### 2019-05-19 README.rmd
adds new badges and switches to README.rmd

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
original_files <- dir()
```

<!-- # ijtiff  <img src="man/figures/logo.png" height="140" align="right"> -->

<!-- Code status -->
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean) 
[![DOI](https://zenodo.org/badge/102645585.svg)](https://zenodo.org/badge/latestdoi/102645585)

<!-- R status -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/Rclean)](https://cran.r-project.org/package=Rclean)
![RStudio CRAN downloads](http://cranlogs.r-pkg.org/badges/grand-total/Rclean)
![RStudio CRAN monthly downloads](http://cranlogs.r-pkg.org/badges/Rclean)
[![Rdocumentation](http://www.rdocumentation.org/badges/version/Rclean)](http://www.rdocumentation.org/packages/Rclean)

<!-- Dev status -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)

<!-- Package Review -->
[![](https://badges.ropensci.org/164_status.svg)](https://github.com/ropensci/onboarding/issues/164)
[![status](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6/status.svg)](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6)

Clean up your code
==================

- Have you ever written a long script in R that conducts oodles of
  analyses and wished that someone would come along and make it all
  clearer to understand and use?
- Well you’re not alone. 
- A recent survey of over 1500 scientists reported a crisis of
  reproducibility with "selective reporting" being the most cited
  contributing factor and 80% saying code availability is playing a
  role
- We created **Rclean** to help scientists more *easily* write "cleaner" code
- [Rclean](https://github.com/ProvTools/Rclean) provides a simple way
  get the code you need to produce a specific result
- **Rclean** uses data provenance tp capture what your code actually
  does when it’s running and then allows you to pull out the essential
  code that produces specific outputs.
- By focusing in on the specific results you want, **Rclean** let’s
  you spend more energy on your science and less time figuring out
  your code.

Install and Setup
=================

You can install
[Rclean](https://cran.r-project.org/web/packages/Rclean/) from *CRAN*:

```R
install.packages("Rclean")
```

You can install the most up to date version easily with
[devtools](https://github.com/hadley/devtools):

```R
install.packages("devtools")
devtools::install_github("ProvTools/cleanR")
```
You will also need to be able to generate data provenance from your
script. This can be done using [provR](https://github.com/ProvTools/):

```R
devtools::install_github("ProvTools/provR")
```

Once installed, per usual R practice, just load the *Rclean* and
*provR* packages:

```R
library(Rclean)
library(provR)
```

Usage
=====

Here's a
[demo video](https://asciinema.org/a/osSGbvH3GKA3r3QMJ2Tlba1pu) for
the following example:

[![demo video](Rclean_demo.png)](https://asciinema.org/a/osSGbvH3GKA3r3QMJ2Tlba1pu)

Once you have your script and workspace setup, you can use
[Rclean](https://github.com/ProvTools/Rclean) to get clean chunks of a
larger script that produce specific results you want. We'll use the
micro.R script, which can be found inside the package repo in the
*exec* directory. The following example assumes that your current
working directory is *exec*.

First, you'll need to record information about the script you would
like to parse. [Rclean](https://github.com/ProvTools/Rclean) uses data
provenance to verify what lines of code depend on each other inside of
the larger script. We can use the
[provR](https://github.com/ProvTools/provR) package to generate
provenance. The next bit of code runs our script and saves the
provenance to memory, which we then pass to the `options` function, so
that [Rclean](https://github.com/ProvTools/Rclean) has access to it:

```R
prov.capture("micro.R")
options(prov.json = prov.json())
```

Or, if you have provenance saved as a text file, you can load it in
like this:

```R
options(prov.json = readLines("prov_micro.json"))
```

Now that we have the provenance loaded, we can start
cleaning. [Rclean](https://github.com/ProvTools/Rclean) will give us a
list of possible values we can get code for:

```R
clean()

```

You can then pick and choose from among these results and get the
essential code to produce the output, like so:

```R
clean(x)

```

Notice that the 'clean' function doesn't require you to quote your
results, it interprets all inputs as names of results.

In many cases, it's handy just to take a look at the isolated code,
but if you can also save the code for later use or sharing.

```R
my.code <- clean(x)
write.code(my.code, file = "x.R")

```

If you would like to copy your code to the clipboard, you can do that
by not specifying a file path.

```R
write.code(my.code)

```

Happy cleaning!

*Contributing*: if you would like to contribute, please read [[CONTRIBUTING.md]].

### 2019-05-19 README.rmd
fixing issue with badges

@@
 <!-- Package Review -->
-[![](https://badges.ropensci.org/164_status.svg)](https://github.com/ropensci/onboarding/issues/164)
+[![](https://badges.ropensci.org/300_status.svg)](https://github.com/ropensci/onboarding/issues/300)
 [![status](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6/status.svg)](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6)

### 2019-05-19 README.rmd
badge fix

@@
 [![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean)
-[![DOI](https://zenodo.org/badge/102645585.svg)](https://zenodo.org/badge/latestdoi/102645585)
 
@@
 [![status](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6/status.svg)](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6)
+
+<!-- Archiving -->
+[![DOI](https://zenodo.org/badge/102645585.svg)](https://zenodo.org/badge/latestdoi/102645585)
 

### 2019-05-19 README.rmd
updating rclean

@@
 
-- Have you ever written a long script in R that conducts oodles of
+- Have you ever written a long script in R that conducts lots of
   analyses and wished that someone would come along and make it all
@@
   contributing factor and 80% saying code availability is playing a
-  role
-- We created **Rclean** to help scientists more *easily* write "cleaner" code
-- [Rclean](https://github.com/ProvTools/Rclean) provides a simple way
-  get the code you need to produce a specific result
-- **Rclean** uses data provenance tp capture what your code actually
-  does when it’s running and then allows you to pull out the essential
-  code that produces specific outputs.
-- By focusing in on the specific results you want, **Rclean** let’s
-  you spend more energy on your science and less time figuring out
-  your code.
+  role.
+- [Rclean](https://github.com/ProvTools/Rclean) was created to help
+  scientists more *easily* write "cleaner" code by providing a simple,
+  rigorous way to isolate the minimal code you need in order to
+  produce a specific result (e.g. object, plot, output written to
+  disk).
+- [Rclean](https://github.com/ProvTools/Rclean) is built on data
+  provenance, a formal representation of a computation, and uses graph
+  analysis to determine the minimal path from inputs to results.
+- The goal is to help facilitate code transparency, reproduciblity,
+  reusability and ultimately help scientists spend more time on
+  research and less time on software.
 
@@
 
-You can install the most up to date version easily with
+You can install the most up to date (beta) version easily with
 [devtools](https://github.com/hadley/devtools):
@@
 install.packages("devtools")
-devtools::install_github("ProvTools/cleanR")
-```
-You will also need to be able to generate data provenance from your
-script. This can be done using [provR](https://github.com/ProvTools/):
-
-```R
-devtools::install_github("ProvTools/provR")
+devtools::install_github("ProvTools/Rclean", ref = "dev")
 ```
 
-Once installed, per usual R practice, just load the *Rclean* and
-*provR* packages:
+Once installed, per usual R practice, just load the *Rclean*:
 
@@
 library(Rclean)
-library(provR)
 ```
@@
 
-Here's a
-[demo video](https://asciinema.org/a/osSGbvH3GKA3r3QMJ2Tlba1pu) for
-the following example:
-
-[![demo video](Rclean_demo.png)](https://asciinema.org/a/osSGbvH3GKA3r3QMJ2Tlba1pu)
+*Rclean* usage is simple. Have a script with code you want to clean
+saved to disk.
 

### 2019-05-19 R/clean.R

@@ -148,7 +148,7 @@ clean <- function(file, var, libs = TRUE, reformat = TRUE, plot = FALSE,
                         node.rank <- as.numeric(gsub("p", "", rownames(lines)))
                         lines <- lines[order(node.rank),]
                     }
-### Extract the minimal code
+                    ## Extract the minimal code
                     min.script <- apply(lines, 1, function(line, src)  
                         src[seq(line[1], line[2])],
                         src = script)
@@ -159,7 +159,7 @@ clean <- function(file, var, libs = TRUE, reformat = TRUE, plot = FALSE,
                     if (any(plot.code)){
                         min.script <- c(min.script, "dev.off()")
                     }
-### Tidying the code using formatR
+                    ## Tidying the code using formatR
                     if (tidy){
                         capture.output(
                             min.script <- 

### 2019-05-19 README.rmd

@@
 *Rclean* usage is simple. Have a script with code you want to clean
-saved to disk.
+saved to disk. Then, just run the `clean` function with the path to
+the script as the input:
 
-Once you have your script and workspace setup, you can use
-[Rclean](https://github.com/ProvTools/Rclean) to get clean chunks of a
-larger script that produce specific results you want. We'll use the
-micro.R script, which can be found inside the package repo in the
-*exec* directory. The following example assumes that your current
-working directory is *exec*.
+```
+clean("./example/simple_script.R")
+```
 
-First, you'll need to record information about the script you would
-like to parse. [Rclean](https://github.com/ProvTools/Rclean) uses data
-provenance to verify what lines of code depend on each other inside of
-the larger script. We can use the
-[provR](https://github.com/ProvTools/provR) package to generate
-provenance. The next bit of code runs our script and saves the
-provenance to memory, which we then pass to the `options` function, so
-that [Rclean](https://github.com/ProvTools/Rclean) has access to it:
+This returns a list of possible results detected in the script,
+including execution lines (not counting lines with no code or that are
+commented). We can now pick the result we want to focus on for
+cleaning:
+
+```
+clean("./example/simple_script.R", "tab.15")
+```
+
+This produces the minimal code detected from the script. It also
+detects the package dependencies as well and provides them in the code
+(`libs = TRUE`).
+
+It can be handy just to take a look at the isolated code, but you can
+save the code for later use or sharing (e.g. creating a reproducible
+example for getting help) with the `write.code` function:
+
+```
+my.code <- clean("./example/simple_script.R", "tab.15")
+write.code(my.code, file = "x.R")
+```
+
+If you would like to copy your code to the clipboard, you can do that
+by not specifying a file path. You can now paste as needed to create a
+simpler script.
 
 ```R
-prov.capture("micro.R")
-options(prov.json = prov.json())
+write.code(my.code)
 ```
 
-Or, if you have provenance saved as a text file, you can load it in
-like this:
+## Retrospective Provenance
+
+So far, we've been using "prosepctive" provenance generated from the
+static code prior to execution. *Rclean* can also be used with
+"retrospective" provenance, which is recorded during execution of a
+script. To do so, we can pass the provenance to the `clean` function
+via `options`:
 
@@
 cleaning. [Rclean](https://github.com/ProvTools/Rclean) will give us a
-list of possible values we can get code for:
+list of possible values we can get code for, notice that the option
+*rp* (i.e. "retrospective provenance") has been set to `TRUE`:
 
 ```R
-clean()
+clean(rp = TRUE)
 
@@
 
-You can then pick and choose from among these results and get the
-essential code to produce the output, like so:
+Similar to before, you can then pick and choose from among these
+results and get the essential code to produce the output, like so:
 
 ```R
-clean(x)
-
-```
-
-Notice that the 'clean' function doesn't require you to quote your
-results, it interprets all inputs as names of results.
-
-In many cases, it's handy just to take a look at the isolated code,
-but if you can also save the code for later use or sharing.
-
-```R
-my.code <- clean(x)
-write.code(my.code, file = "x.R")
-
-```
-
-If you would like to copy your code to the clipboard, you can do that
-by not specifying a file path.
-
-```R
-write.code(my.code)
+clean(x, rp = TRUE)
 

### 2019-05-21 R/clean.R
fixes errors detected by goodpractices and turns off tests temporarily

@@ -44,133 +44,132 @@
 #'@export clean
 #'@author Matthew K. Lau
 
-clean <- function(file, var, libs = TRUE, reformat = TRUE, plot = FALSE,
-                  rp = FALSE){
-    if (!(rp) & missing(file) ){
-        warning("Please provide a script file path.")
+clean <- function(file, var, libs = TRUE, reformat = TRUE, plot = FALSE, rp = FALSE){
+  if (!(rp) & missing(file)){
+    warning("Please provide a script file path.")
+  }else{
+    if (missing(var)){
+      warning("Please supply a variable/object name")
+      rownames(var.lineage(readScript(file))[["g"]])
     }else{
-        if (missing(var)){
-            warning("Please supply a variable/object name")
-            rownames(var.lineage(readScript(file))[["g"]])
+      if (!(rp)){
+        src <- readScript(file)
+        vl <- var.lineage(src)
+        sp <- p.spine(vl, var)
+        min.g <- vl[["g"]][rownames(vl[["g"]]) %in% as.character(sp), 
+                           colnames(vl[["g"]]) %in% as.character(sp)]
+        sp <- sp[sp %in% as.character(unique(vl[["vdf"]][, "step"]))]
+        sp <- sort(as.numeric(sp))
+        min.src <- as.character(src[sp])
+        if (libs){
+          libs <- na.omit(unlist(get.libs(src)[sp]))
+          lib.src <- paste0("library(", libs, ")")
+          out <- c(lib.src, min.src)
         }else{
-            if (!(rp)){
-                src <- readScript(file)
-                vl <- var.lineage(src)
-                sp <- p.spine(vl, var)
-                min.g <- vl[["g"]][rownames(vl[["g"]]) %in% as.character(sp), 
-                                   colnames(vl[["g"]]) %in% as.character(sp)]
-                sp <- sp[sp %in% as.character(unique(vl[["vdf"]][, "step"]))]
-                sp <- sort(as.numeric(sp))
-                min.src <- as.character(src[sp])
-                if (libs){
-                    libs <- na.omit(unlist(get.libs(src)[sp]))
-                    lib.src <- paste0("library(", libs, ")")
-                    out <- c(lib.src, min.src)
-                }else{
-                    out <- min.src
-                }
-                                        # Re-formatting the code using formatR
-                if (reformat){
-                    capture.output(
-                        out <- 
-                            tidy_source(text = out)$text.tidy
-                    )
-                }
-                if (plot){
-                    codeGraph(min.g)
-                }
[…]

### 2019-05-21 R/get.libs.R

@@ -24,6 +24,7 @@
 #'@param src Character vector containing the source script.
 #'@return The libraries used for each step of the script.
 #'@importFrom CodeDepends getInputs
+#'@importFrom methods slot
 #'@export get.libs
 #'@author Matthew K. Lau
 

### 2019-05-21 tests/testthat.R

@@ -3,5 +3,5 @@ library(jsonlite)
 library(igraph)
 library(formatR)
 
-test_check("Rclean")
+# test_check("Rclean")
 

### 2019-05-21 tests/testthat/test_Rclean.R

@@ -23,7 +23,7 @@ context("Code cleaning: initiate")
 micro.test <- clean()
 expect_equal(length(micro.test), 2)
 expect_match(mode(micro.test), "list")
-expect_match(names(micro.test)[1], "Files")
+# expect_match(names(micro.test)[1], "Files")
 expect_match(names(micro.test)[2], "Objects")
 expect_match(micro.test$Files[1], "test.test")
 expect_match(micro.test$Files[2], "test.pdf")

### 2019-06-03 README.rmd
Edits README.Rmd and CONTRIBUTE.md

@@
 This produces the minimal code detected from the script. It also
-detects the package dependencies as well and provides them in the code
-(`libs = TRUE`).
+detects library dependencies and inserts them into the code (`libs =
+TRUE`).
 
@@
 
-If you would like to copy your code to the clipboard, you can do that
+If you would like to copy your code to your clipboard, you can do that
 by not specifying a file path. You can now paste as needed to create a
@@
 
-So far, we've been using "prosepctive" provenance generated from the
+So far, we've been using "prosepective" provenance generated from the
 static code prior to execution. *Rclean* can also be used with
 "retrospective" provenance, which is recorded during execution of a
-script. To do so, we can pass the provenance to the `clean` function
-via `options`:
+script. Using it facilitates more accurate code cleaning, We can pass
+the provenance to the `clean` function via `options`:
 
@@
 
-*Contributing*: if you would like to contribute, please read [[CONTRIBUTING.md]].
+*Contributing*: if you would like to contribute, please read [[CONTRIBUTE.md]].

### 2019-06-03 README.rmd
More random edits and renders

@@
 ---
-output: github_document
+output: md_document
 ---
@@
 
-Clean up your code
-==================
+Clean your code
+===============
 
@@
 - [Rclean](https://github.com/ProvTools/Rclean) is built on data
-  provenance, a formal representation of a computation, and uses graph
-  analysis to determine the minimal path from inputs to results.
+  provenance, a mathematically formal representation of a computation,
+  and uses graph analysis to determine the minimal path from inputs to
+  results in a script.
 - The goal is to help facilitate code transparency, reproduciblity,

### 2019-06-03 README.Rmd
renders README
adds tests for clean

--- 2019-06-03 README.rmd
@@
 
-```R
+```{r}
 install.packages("Rclean")
@@
 
-```R
+```{r}
 install.packages("devtools")
@@
 
-```R
+```{r}
 library(Rclean)
@@
 
-```
+```{r}
 clean("./example/simple_script.R")
@@
 
-```
+```{r}
 clean("./example/simple_script.R", "tab.15")
@@
 
-```
+```{r}
 my.code <- clean("./example/simple_script.R", "tab.15")
@@
 
-```R
+```{r}
 write.code(my.code)
@@
 
-```R
+```{r}
 options(prov.json = readLines("prov_micro.json"))
@@
 
-```R
+```{r}
 clean(rp = TRUE)
@@
 
-```R
+```{r}
 clean(x, rp = TRUE)

### 2019-06-03 tests/testthat.R

@@ -1,7 +1,3 @@
 library(testthat)
-library(jsonlite)
-library(igraph)
-library(formatR)
-
-# test_check("Rclean")
+test_check("Rclean")
 

### 2019-06-03 tests/testthat/test-main.R

@@ -1,0 +1,94 @@
+# Prospective Provenance (i.e. rp = FALSE)
+test_that("clean options prospective", {
+    load("opt.test.rda")
+    opt <- clean("simple_script.R")
+    expect_true(all(opt == opt.test))
+})
+
+test_that("clean prospective data.frame", {
+    load("clean.simple.out.test.rda")
+    clean.simple.out <- clean("simple_script.R", "out")
+    expect_true(all(clean.simple.out == clean.simple.out.test))
+})
+
+
+test_that("clean libs prospective", {
+    load("lib.test.rda")
+    lib <- clean("lib_test.R", "out")
+    expect_true(all(lib[1:2] == lib.test[1:2]))
+})
+
+
+test_that("clean prospective no re-formatting", {
+    load("format.simple.out.test.rda")
+    format.simple.out <- clean("simple_script.R", "out")
+    expect_true(all(format.simple.out == format.simple.out.test))
+})
+
+
+# Retrospective Provenance (i.e. rp = TRUE)
+## provR
+## test_that("check provenance storage", {
+##     options(prov.json = readLines("micro_R.json"))
+##     prov <- read.prov(options()$prov.json)
+##     expect_match(mode(prov), "list")
+##     expect_equal(length(prov), 2)
+## })
+
+## test_that("Provenance graph", {
+##     options(prov.json = readLines("micro_R.json"))
+##     prov <- read.prov(options()$prov.json)
+##     expect_match(mode(prov$graph), "numeric")
+##     expect_match(class(prov$graph), "matrix")
+## })
+
+## test_that("Provenance info", {
+##     options(prov.json = readLines("micro_R.json"))
+##     prov <- read.prov(options()$prov.json)
+##     expect_equal(length(prov$info), 3)
+## })
+
+## test_that("Code cleaning: initiate", {
+##     options(prov.json = readLines("micro_R.json"))
+##     micro.test <- clean(rp = TRUE)
+##     expect_equal(length(micro.test), 2)
+##     expect_match(mode(micro.test), "list")
+##     expect_match(names(micro.test)[2], "Objects")
+##     expect_match(micro.test$Files[1], "test.test")
+##     expect_match(micro.test$Files[2], "test.pdf")
+##     expect_match(micro.test$Objects[1], "x")
+##     expect_match(micro.test$Objects[2], "y")
+## })
+
[…]

### 2019-06-03 tests/testthat/test_Rclean.R

@@ -5,6 +5,10 @@ library(igraph)
 library(formatR)
 library(utils)
 
+
+
+
+# Retrospective Provenance
 ## Loading test data
 test.dat.loc <- system.file("exec", "micro_R.json", package="Rclean")
 options(prov.json = readLines(test.dat.loc))

### 2019-06-03 tests/testthat/test_Rclean.R
debugging clean tests

@@ -1,66 +1,0 @@
-context("Provenance capture")
-library(Rclean)
-library(jsonlite)
-library(igraph)
-library(formatR)
-library(utils)
-
-
-
-
-# Retrospective Provenance
-## Loading test data
-test.dat.loc <- system.file("exec", "micro_R.json", package="Rclean")
-options(prov.json = readLines(test.dat.loc))
-prov <- read.prov(options()$prov.json)
-expect_match(mode(prov), "list")
-expect_equal(length(prov), 2)
-
-context("Provenance graph")
-expect_match(mode(prov$graph), "numeric")
-expect_match(class(prov$graph), "matrix")
-
-context("Provenance info")
-expect_equal(length(prov$info), 3)
-
-context("Code cleaning: initiate")
-micro.test <- clean()
-expect_equal(length(micro.test), 2)
-expect_match(mode(micro.test), "list")
-# expect_match(names(micro.test)[1], "Files")
-expect_match(names(micro.test)[2], "Objects")
-expect_match(micro.test$Files[1], "test.test")
-expect_match(micro.test$Files[2], "test.pdf")
-expect_match(micro.test$Objects[1], "x")
-expect_match(micro.test$Objects[2], "y")
-
-context("Code cleaning: get result")
-micro.result.x.test <- clean(var = "x")
-expect_match(micro.result.x.test[1] , "x <- 1")
-expect_match(micro.result.x.test[2] , "y <- 3")
-expect_match(micro.result.x.test[3] , "x <- x \\+ y")
-micro.result.y.test <- clean(var = "y")
-expect_match(micro.result.y.test[1] , "y <- 3")
-micro.result.test_test.test <- clean(var = "test.test")
-expect_match(micro.result.test_test.test[1], "x <- 1")
-expect_match(micro.result.test_test.test[2], "y <- 3")
-expect_match(micro.result.test_test.test[3], "x <- x \\+ y")
-expect_match(micro.result.test_test.test[4], "write\\.csv\\(x, \"~/test\\.test\"\\)")
-
-micro.result.test_pdf.test <- clean(var = "test.pdf")
-expect_match(micro.result.test_pdf.test[1], "x <- 1")
-expect_match(micro.result.test_pdf.test[2], "y <- 3")
-expect_match(micro.result.test_pdf.test[3], "x <- x \\+ y")
[…]

### 2019-07-03 tests/testthat/test-main.R
adds test for read.prov

@@ -77,8 +77,6 @@ test_that("clean RP y", {
 ##     expect_true(all(rmd.chunks == rmd.chunks.test))
 ## })
 
-
-
 test_that("codeGraph", {
     load("codeGraph.src.rda")
     vl <- var.lineage(src)
@@ -89,7 +87,11 @@ test_that("codeGraph", {
     expect_true(length(output.cap) == 0)
 })
 
-## read.prov
+test_that("read.prov", {
+    load("read.prov.test.rda")
+    prov <- read.prov("micro_R.json")
+    expect_true(all(unlist(prov) == unlist(prov.test)))
+})
 
 
 ## write.code

### 2019-07-03 tests/testthat/clean.simple.test.R
adds write.code test

@@ -1,0 +1,7 @@
+mat <- matrix(rnorm(400), nrow = 100)
+dat <- as.data.frame(mat)
+dat[, "V2"] <- dat[, "V2"] + runif(nrow(dat))
+dat[, "V5"] <- gl(10, 10)
+dat <- 25 + 2
+dat[2] <- 10
+out <- dat * 2

### 2019-07-03 tests/testthat/test-main.R

@@ -94,4 +94,11 @@ test_that("read.prov", {
 })
 
 
-## write.code
+test_that("write.code", {
+    load("write.code.test.rda")    
+    write.code(clean.simple.out, file = "clean.simple.test.R")
+    write.code.test <- readLines("clean.simple.test.R")
+    file.remove("clean.simple.test.R")
+    expect_true(all(clean.simple.out == write.code.test))
+})
+

### 2019-07-04 tests/testthat/clean.simple.test.R
fixes issue with read.prov test

@@ -1,7 +1,0 @@
-mat <- matrix(rnorm(400), nrow = 100)
-dat <- as.data.frame(mat)
-dat[, "V2"] <- dat[, "V2"] + runif(nrow(dat))
-dat[, "V5"] <- gl(10, 10)
-dat <- 25 + 2
-dat[2] <- 10
-out <- dat * 2

### 2019-07-04 tests/testthat/test-main.R

@@ -88,7 +88,7 @@ test_that("codeGraph", {
 })
 
 test_that("read.prov", {
-    load("read.prov.test.rda")
+    load("read.prov.test")
     prov <- read.prov("micro_R.json")
     expect_true(all(unlist(prov) == unlist(prov.test)))
 })

### 2019-07-04 README.rmd
fixed README and re-rendered

--- 2019-06-03 README.rmd
@@
 
-```R
+```{r eval = FALSE}
 options(prov.json = readLines("prov_micro.json"))
@@
 
-```R
+```{r eval = FALSE}
 clean(rp = TRUE)
@@
 
-```R
+```{r eval = FALSE}
 clean(x, rp = TRUE)

### 2019-07-04 x.R

@@ -1,0 +1,10 @@
+mat <- matrix(rnorm(400), nrow = 100)
+dat <- as.data.frame(mat)
+dat[, "V2"] <- dat[, "V2"] + runif(nrow(dat))
+dat[, "V5"] <- gl(10, 10)
+fit14 <- lm(V1 ~ V4, data = dat)
+fit15.aov <- aov(V1 ~ V2 + V5, data = dat)
+tab.14 <- summary(fit14)
+tab.15 <- append(fit15.aov, tab.14)
+dat <- 25 + 2
+dat[2] <- 10

### 2019-07-04 x.R
accidently added x.R, now removed

@@ -1,10 +1,0 @@
-mat <- matrix(rnorm(400), nrow = 100)
-dat <- as.data.frame(mat)
-dat[, "V2"] <- dat[, "V2"] + runif(nrow(dat))
-dat[, "V5"] <- gl(10, 10)
-fit14 <- lm(V1 ~ V4, data = dat)
-fit15.aov <- aov(V1 ~ V2 + V5, data = dat)
-tab.14 <- summary(fit14)
-tab.15 <- append(fit15.aov, tab.14)
-dat <- 25 + 2
-dat[2] <- 10

### 2019-07-04 README.Rmd
adds coverage reporting

@@
 [![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean) 
+[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/tests/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=tests)
 
@@
 
-```{r}
+```{r eval = FALSE}
 options(prov.json = readLines("prov_micro.json"))
@@
 
-```{r}
+```{r eval = FALSE}
 clean(rp = TRUE)
@@
 
-```{r}
+```{r eval = FALSE}
 clean(x, rp = TRUE)

### 2019-07-08 README.rmd
updates README.rmd

@@
 <!-- Code status -->
-[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
-[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean)
+[![Stable: Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
+[![Dev: Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=tests)](https://travis-ci.org/ProvTools/Rclean) 
+[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/tests/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=tests)
 

### 2019-07-08 x.R
updates and renders README

@@ -1,0 +1,11 @@
+library()
+mat <- matrix(rnorm(400), nrow = 100)
+dat <- as.data.frame(mat)
+dat[, "V2"] <- dat[, "V2"] + runif(nrow(dat))
+dat[, "V5"] <- gl(10, 10)
+fit14 <- lm(V1 ~ V4, data = dat)
+fit15.aov <- aov(V1 ~ V2 + V5, data = dat)
+tab.14 <- summary(fit14)
+tab.15 <- append(fit15.aov, tab.14)
+dat <- 25 + 2
+dat[2] <- 10

### 2019-07-08 README.rmd
updates and renders README

--- 2019-07-04 README.rmd
@@
 <!-- Code status -->
-[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
-[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean)
+[![Dev: Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=tests)](https://travis-ci.org/ProvTools/Rclean) 
+[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/tests/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=tests)
 

### 2019-07-08 x.R
updates and renders README

@@ -1,11 +1,0 @@
-library()
-mat <- matrix(rnorm(400), nrow = 100)
-dat <- as.data.frame(mat)
-dat[, "V2"] <- dat[, "V2"] + runif(nrow(dat))
-dat[, "V5"] <- gl(10, 10)
-fit14 <- lm(V1 ~ V4, data = dat)
-fit15.aov <- aov(V1 ~ V2 + V5, data = dat)
-tab.14 <- summary(fit14)
-tab.15 <- append(fit15.aov, tab.14)
-dat <- 25 + 2
-dat[2] <- 10

### 2019-07-08 README.rmd
updates and renders README

--- 2019-07-04 README.rmd
@@
 <!-- Code status -->
-[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
-[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean)
+[![Dev: Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean) 
+[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/dev/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=dev)
 
@@
 
-```{r}
+```{r eval = FALSE}
 my.code <- clean("./example/simple_script.R", "tab.15")
@@
 
-```{r}
+```{r eval = FALSE}
 write.code(my.code)

### 2019-07-08 README.rmd
updates README

@@
 <!-- Code status -->
-[![Dev: Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean) 
-[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/dev/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=dev)
+[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
+[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=master)
 

### 2019-07-09 README.rmd
fixes errors in README

@@
 
-Install and Setup
-=================
+Install
+=======
 
@@
 
-```{r}
+```{r eval = FALSE}
 install.packages("Rclean")
@@
 
-```{r}
+```{r eval = FALSE}
 install.packages("devtools")
@@
 
-```{r}
+```{r eval = TRUE}
 library(Rclean)
@@
 saved to disk. Then, just run the `clean` function with the path to
-the script as the input:
+the script as the input. Here, we can use an example script that is
+included with the package:
 
-```{r}
-clean("./example/simple_script.R")
+```{r eval = TRUE}
+clean("example/simple_script.R")
 ```
@@
 
-```{r}
+```{r eval = TRUE}
 clean("./example/simple_script.R", "tab.15")
@@
 ```{r eval = FALSE}
-my.code <- clean("./example/simple_script.R", "tab.15")
+my.code <- clean("example/simple_script.R", "tab.15")
 write.code(my.code, file = "x.R")
@@
 
-So far, we've been using "prosepective" provenance generated from the
+So far, we've been using "prospective" provenance generated from the
 static code prior to execution. *Rclean* can also be used with
@@
 
-```{r eval = FALSE}
-options(prov.json = readLines("prov_micro.json"))
+```{r eval = TRUE}
+options(prov.json = readLines("example/prov_micro.json"))
 ```
@@
 
-```{r eval = FALSE}
-clean(rp = TRUE)
-
+```{r eval = TRUE}
+clean(file = "example/micro.R", rp = TRUE)
 ```
@@
 ```{r eval = FALSE}
-clean(x, rp = TRUE)
-
+clean(file = "example/micro.R", var = "x", rp = TRUE)
 ```
@@
 Happy cleaning!
-
-*Contributing*: if you would like to contribute, please read [[CONTRIBUTE.md]].

### 2019-07-09 R/clean.R
fixes bug with provenance detection

@@ -90,11 +90,11 @@ clean <- function(file, var, libs = TRUE, reformat = TRUE, plot = FALSE, rp = FA
                 }else{
                     warning("Please add options(prov.json = PROV.JSON)")
                 }
-                ## Check prov matches a file in the current working directory
-                if (!(any(dir() == prov$info$activity[1,1]))){
-                    print("No scripts matching current provenance.")
+                ## Check that specified file matches provenance file before reading
+                if (!(grepl(prov$info$activity[1,1], file))){
+                    print("Specified script does not match provenance.")
                 }else{
-                    script <- readLines(prov$info$activity[1,1][[1]])
+                    script <- readLines(file)
                 }
                 ## Get result options
                 ## Output files

### 2019-07-09 R/get.spine.R
adds noRd to internals and adds export where needed

@@ -33,10 +33,11 @@
 #' @importFrom igraph dfs
 #' @importFrom igraph graph_from_adjacency_matrix
 #' @importFrom stats na.omit
-#'@examples
+#' @export
+#' @examples
 #' data(prov_json)
 #' prov <- read.prov(prov_json)
-#' Rclean:::get.spine("d1", prov$graph)
+#' get.spine("d1", prov$graph)
 
 get.spine <- function(node.id, g){
     ig <- graph_from_adjacency_matrix(g)

### 2019-07-09 R/parse.graph.R

@@ -29,10 +29,11 @@
 #' @param rm.env LOGICAL: should the environment entity be removed?
 #' @return A symmetric matrix of provenance entity relationships.
 #' @author Matthew K. Lau
-#'@examples
+#' @export 
+#' @examples
 #'  data(prov_json)
 #'  prov <- jsonlite::fromJSON(prov_json)
-#'  Rclean:::parse.graph(prov)
+#'  parse.graph(prov)
 
 parse.graph <- function(prov,rm.env = TRUE){
     if (grepl("rdatatracker", prov[[1]][[2]]) | grepl("provR", prov[[1]][[2]])){

### 2019-07-09 R/parse.info.R

@@ -28,10 +28,11 @@
 #' @param prov PROV-JSON formatted provenance.
 #' @return A symmetric matrix of provenance entity relationships.
 #' @author Matthew K. Lau
+#' @export
 #' @examples
 #'  data(prov_json)
 #'  prov <- jsonlite::fromJSON(prov_json)
-#'  Rclean:::parse.info(prov)
+#'  parse.info(prov)
 
 parse.info <- function(prov){
     if (grepl("rdatatracker", prov[[1]][[2]]) | grepl("provR", prov[[1]][[2]])){

### 2019-07-09 R/var.id.R

@@ -24,6 +24,7 @@
 #'@param sep Text separator for the identification tags.
 #'@return A vector of unique identifiers based on the order of creation in the script. 
 #'@author Matthew K. Lau
+#'@noRd
 
 var.id <- function(x, sep = "_"){
   uid <- paste(x[, "var"], cumsum(x[, "defined"]), sep = sep)

### 2019-07-09 vignettes/example/simple_script.R
adds knitr dep and copies example files to vignette

@@ -1,0 +1,20 @@
+## Make a data frame
+mat <- matrix(rnorm(400), nrow = 100)
+dat <- as.data.frame(mat)
+dat[, "V2"] <- dat[, "V2"] + runif(nrow(dat))
+dat[, "V5"] <- gl(10, 10)
+## Conduct some analyses
+fit12 <- lm(V1 ~ V2, data = dat)
+fit13 <- lm(V1 ~ V3, data = dat)
+fit14 <- lm(V1 ~ V4, data = dat)
+fit15.aov <- aov(V1 ~ V2 + V5, data = dat)
+## Summarize analyses
+summary(fit15.aov)
+tab.12 <- summary(fit12)
+tab.13 <- summary(fit13)
+tab.14 <- summary(fit14)
+tab.15 <- append(fit15.aov, tab.14)
+## Conduct an off-hand calculation
+dat <- 25 + 2
+dat[2] <- 10
+out <- dat * 2

### 2019-09-11 inst/README.rmd
changes ROpenSci badge to review in README.rmd

--- 2019-07-09 README.rmd
@@
 <!-- Package Review -->
-[![](https://badges.ropensci.org/300_status.svg)](https://github.com/ropensci/onboarding/issues/300)
+[![](https://badges.ropensci.org/327_status.svg)](https://github.com/ropensci/software-review/issues/327)
 [![status](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6/status.svg)](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6)
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 clean(file = "example/micro.R", var = "x", rp = TRUE)

### 2019-09-11 inst/README.rmd
fixes typos

@@
   analysis to determine the minimal path from inputs to results.
-- The goal is to help facilitate code transparency, reproduciblity,
+- The goal is to help facilitate code transparency, reproducibility,
   reusability and ultimately help scientists spend more time on

### 2019-09-11 R/codeGraph.R

@@ -18,7 +18,7 @@
 
 #'codeGraph --- A network diagram of computational dependencies. 
 #'
-#' Plot the dependencies among funcitons and objects for a given script.
+#' Plot the dependencies among functions and objects for a given script.
 #' 
 #'@param g Matrix representation of the graph.
 #'@return A network plot.

### 2019-09-11 R/get.libs.R

@@ -19,7 +19,7 @@
 
 #'get.libs --- Determine the libraries needed for a given script. 
 #'
-#' Uses code dependency inforrmation to produce a set of necessary libraries.
+#' Uses code dependency information to produce a set of necessary libraries.
 #' 
 #'@param src Character vector containing the source script.
 #'@return The libraries used for each step of the script.

### 2019-09-11 R/p.spine.R

@@ -16,13 +16,13 @@
 #
 # Contact: Matthew Lau <matthewklau@fas.harvard.edu>
 
-#'p.spine --- Parenatage spine for a given object.
+#'p.spine --- Parentage spine for a given object.
 #'
 #' Isolates the line of parentage for an object. This can be either
 #' all steps leading to an object or all steps leading out from an
 #' object.
 #' 
-#'@param g A graph in matrix formate that presents the use and
+#'@param g A graph in matrix format that presents the use and
 #'     creation of variables by steps (i.e. complexes of function and
 #'     operation calls).
 #'@param node.id The name of the node of interest.

### 2019-09-13 inst/README.rmd

@@
 
-You can install the most up to date (beta) version easily with
+You can install the most up to date version easily with
 [devtools](https://github.com/hadley/devtools):
@@
 install.packages("devtools")
-devtools::install_github("ProvTools/Rclean", ref = "dev")
+devtools::install_github("ProvTools/Rclean")
 ```
 
-Once installed, per usual R practice, just load the *Rclean*:
+Once installed, per usual R practice, just load the *Rclean* package with:
 

### 2019-10-10 inst/README.rmd

@@
 ---
-output: md_document
+output: github_document
 ---
@@
   comment = "#>",
-  fig.path = "man/figures/README-"
+  fig.path = "man/figures/README-",
+  out.width = "100%"
 )
@@
 
-## Retrospective Provenance
+Retrospective Provenance
+========================
 
@@
 Happy cleaning!
+
+Contributing
+============
+
+Please note that the 'Rclean' project is released with a
+[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
+By contributing to this project, you agree to abide by its terms.

### 2019-10-28 inst/README.rmd
roxygenize

@@
 
-- Have you ever written a long script in R that conducts lots of
-  analyses and wished that someone would come along and make it all
-  clearer to understand and use?
-- Well you’re not alone. 
-- A recent survey of over 1500 scientists reported a crisis of
-  reproducibility with "selective reporting" being the most cited
-  contributing factor and 80% saying code availability is playing a
-  role.
 - [Rclean](https://github.com/ProvTools/Rclean) was created to help
-  scientists more *easily* write "cleaner" code by providing a simple,
-  rigorous way to isolate the minimal code you need in order to
-  produce a specific result (e.g. object, plot, output written to
-  disk).
-- [Rclean](https://github.com/ProvTools/Rclean) is built on data
-  provenance, a formal representation of a computation, and uses graph
-  analysis to determine the minimal path from inputs to results.
-- The goal is to help facilitate code transparency, reproducibility,
-  reusability and ultimately help scientists spend more time on
-  research and less time on software.
+  scientists more *easily* write "cleaner" code. 
+- Written with research scientists that are results oriented in mind,
+  the package's primary function provides a simple way to isolate the
+  minimal code you need to produce a specific result, such as a
+  statistical table or a figure.
+- By focusing on specific results, large and/or complicated analytical
+  scripts can be paired down to the essentials and easily re-factored
+  to be more robust and easily shared.
 
@@
 install.packages("devtools")
-devtools::install_github("ProvTools/Rclean")
+devtools::install_github("MKLau/Rclean")
 ```
@@
 
+```{r eval = TRUE, echo = FALSE results = "hide"}
+library(CodeDepends)
+script <- system.file(
+    "example", 
+    "simple_script.R", 
+    package = "Rclean")
+
+```
+
 *Rclean* usage is simple. Have a script with code you want to clean
@@
 
-```{r eval = TRUE}
-clean("example/simple_script.R")
+```{r eval = FALSE} 
+script <- "example/simple_script.R"
+
 ```
 
-This returns a list of possible results detected in the script,
-including execution lines (not counting lines with no code or that are
-commented). We can now pick the result we want to focus on for
-cleaning:
+Here's a quick look at the code:
 
 ```{r eval = TRUE}
-clean("./example/simple_script.R", "tab.15")
+readLines(script)
+
 ```
 
-This produces the minimal code detected from the script. It also
-detects library dependencies and inserts them into the code (`libs =
-TRUE`).
+You can get a list of the variables found in an object with
+`get_vars`.
 
-It can be handy just to take a look at the isolated code, but you can
-save the code for later use or sharing (e.g. creating a reproducible
-example for getting help) with the `write.code` function:
+```{r eval = TRUE}
+get_vars(script)
+
+```
+
+Sometimes for more complicated scripts, it can be helpful to see a
+ network graph showing the interdependencies of
+ variables. `code_graph` will produce a network diagram showing which
+ lines of code produce which variables (e.g. 1 -> "out"):
+
+```{r eval = TRUE}
+code_graph(script)
+```
+
+Now, we can now pick the result we want to focus on for cleaning:
+
+```{r eval = TRUE}
+clean(script, "tab.15")
+```
+
+We can also select several variables at the same time:
+
+```{r eval = TRUE}
+my.vars <- c("tab.12", "tab.15")
+clean(script, my.vars)
+```
+
+While just taking a look at the simplified code can be very helpful,
+you can also save the code for later use or sharing (e.g. creating a
+reproducible example for getting help) with `keep`:
 
 ```{r eval = FALSE}
-my.code <- clean("example/simple_script.R", "tab.15")
-write.code(my.code, file = "x.R")
+my.code <- clean(script, my.vars)
+keep(my.code, file = "results_tables.R")
 ```
@@
 If you would like to copy your code to your clipboard, you can do that
-by not specifying a file path. You can now paste as needed to create a
-simpler script.
+by not specifying a file path. You can now paste the simplified as needed.
 
 ```{r eval = FALSE}
-write.code(my.code)
+keep(my.code)
 ```
-
-Retrospective Provenance
-========================
-
-So far, we've been using "prospective" provenance generated from the
-static code prior to execution. *Rclean* can also be used with
-"retrospective" provenance, which is recorded during execution of a
-script. Using it facilitates more accurate code cleaning, We can pass
-the provenance to the `clean` function via `options`:
-
-```{r eval = TRUE}
-options(prov.json = readLines("example/prov_micro.json"))
-```
-
-Now that we have the provenance loaded, we can start
-cleaning. [Rclean](https://github.com/ProvTools/Rclean) will give us a
-list of possible values we can get code for, notice that the option
-*rp* (i.e. "retrospective provenance") has been set to `TRUE`:
-
-```{r eval = TRUE}
-clean(file = "example/micro.R", rp = TRUE)
-```
-
-Similar to before, you can then pick and choose from among these
-results and get the essential code to produce the output, like so:
-
-```{r eval = TRUE}
-clean(file = "example/micro.R", var = "x", rp = TRUE)
-```
-
-Happy cleaning!
 

### 2019-10-31 tests/testthat/test-deps.R
removed old scripts from tests

@@ -1,77 +1,0 @@
-## get.libs 
-test_that("Check get.libs", {
-    load("libs.test.rda")
-    libs <- clean("./lib_test.R", "out")
-    expect_true(all(libs == libs.test))
-})
-
-## read.prov
-test_that("Check read.prov", {
-    load("prov.test.rda")
-    prov <- read.prov("micro_R.json")
-    expect_true(all(unlist(prov) == unlist(prov.test)))
-})
-
-
-## parse.graph
-test_that("Check parse.graph", {
-    load("prov.g.test.rda")
-    prov.json <- fromJSON("micro_R.json")
-    prov.g <- parse.graph(prov.json)
-    expect_true(all(prov.g == prov.g.test))
-})
-
-## var.lineage
-test_that("Check variable lineage", {
-    load("vl.test.rda")
-    src <- readScript("simple_script.R")
-    vl <- var.lineage(src)
-    expect_true(all(unlist(vl) == unlist(vl.test)))
-})
-
-
-## p.spine
-test_that("Check parentage sub-graph", {
-    load("sp.test.rda")
-    src <- readScript("simple_script.R")
-    vl <- var.lineage(src)
-    sp <- p.spine(vl, "out")
-    expect_true(all(sp == sp.test))
-})
-
-test_that("Check parentage sub-graph length", {
-    load("sp.test.rda")
-    src <- readScript("simple_script.R")
-    vl <- var.lineage(src)
-    sp <- p.spine(vl, "out")
-    expect_true(length(sp) == length(sp.test))
-})
-
-
-## get.spine
-test_that("Check get.spine", {
-    load("s.test.rda")
-    var <- "x"
-    prov <- read.prov("micro_R.json")
-    node.id <- tail(n = 1,
-                    rownames(prov$info$entity)[
-                        prov$info$entity[,1] == var]
-                    )
-    s <- get.spine(node.id, prov$g)
-    expect_true(all(s == s.test))
-})
-
-## ## parse.info
-test_that("Check parse.info", {
-    load("pi.test.rda")
-    prov <- fromJSON("micro_R.json")
-    pi <- parse.info(prov)
-    expect_true(all(unlist(pi) == unlist(pi.test)))
-})
-
-## ## var.id
-## test_that("Check var.id", {
-##     load("vid.test.rda")
-##     vid <- 
-##     expect_true(all( == .test))
-## })

### 2019-10-31 inst/README.rmd
adds new README example and text

@@
 
-```{r eval = TRUE, echo = FALSE results = "hide"}
+```{r eval = TRUE, echo = FALSE, results = "hide"}
 library(CodeDepends)
@@
  variables. `code_graph` will produce a network diagram showing which
- lines of code produce which variables (e.g. 1 -> "out"):
+ lines of code produce or use which variables (e.g. 1 -> "out"):
 
@@
 
-Now, we can now pick the result we want to focus on for cleaning:
+Now, we can pick the result we want to focus on for cleaning:
 
@@
 
+This is an open-source project. If you would like to contribute to the
+project, please check out [CONTRIBUTING.md](CONTRIBUTING.md).
+
 Please note that the 'Rclean' project is released with a

### 2019-11-01 inst/README.rmd
adds make.R, renders and moves README.md

@@
   statistical table or a figure.
-- By focusing on specific results, large and/or complicated analytical
-  scripts can be paired down to the essentials and easily re-factored
-  to be more robust and easily shared.
+- By focusing on specific results (aka. variables), large and/or
+  complicated analytical scripts can be paired down to the essentials
+  and easily re-factored to be more robust and easily shared.
 

### 2019-11-01 make.R

@@ -1,0 +1,3 @@
+### Render and migrate README.md
+rmarkdown::render("inst/README.rmd")
+file.rename("inst/README.md", "README.md")

### 2019-11-06 make.R
adds rclean-package

@@ -1,3 +1,4 @@
 ### Render and migrate README.md
 rmarkdown::render("inst/README.rmd")
 file.rename("inst/README.md", "README.md")
+

### 2019-11-07 inst/README.rmd
README now contains Rgraphviz install instructions

@@
 
-Once installed, per usual R practice, just load the *Rclean* package with:
+You will also likely need to install the
+[RGraphViz](bioconductor.org/packages/release/bioc/html/Rgraphviz.html):
+
+```{R rgraphviz}
+
+if (!requireNamespace("BiocManager", quietly = TRUE))
+    install.packages("BiocManager")
+
+BiocManager::install("Rgraphviz")
+
+```
+
+Once installed, per usual R practice just load the *Rclean* package
+with:
 

### 2019-11-08 inst/README.rmd
Changes provtools to MKLau in all docs

@@
 <!-- Code status -->
-[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
-[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=master)
+[![Build Status](https://travis-ci.org/MKLau/Rclean.svg?branch=master)](https://travis-ci.org/MKLau/Rclean) 
+[![Coverage status](https://codecov.io/gh/MKLau/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/MKLau/Rclean?branch=master)
 
@@
 
-- [Rclean](https://github.com/ProvTools/Rclean) was created to help
+- [Rclean](https://github.com/MKLau/Rclean) was created to help
   scientists more *easily* write "cleaner" code. 

### 2019-11-09 R/get_libs.R
Hacking at get_libs

@@ -22,16 +22,31 @@
 #' Uses code dependency information to produce a set of necessary
 #' libraries.
 #' 
-#'@param src 
-#'@return The libraries used for each step of the script.
+#'@param file 
+#'@return Returns the libraries references in the script.
 #'@importFrom CodeDepends getInputs
+#'@importFrom CodeDepends readScript
 #'@importFrom methods slot
 #'@export get_libs
 #'@author Matthew K. Lau
 
-get_libs <- function(src){
-  cd <- getInputs(src)
-  libs <- unlist(lapply(cd, slot, name = "libraries"))
-  out <- unique(libs)
-  return(out)
+get_libs <- function(file){
+    src <- readScript(file)
+    cd <- getInputs(src)
+    libs <- unlist(lapply(cd, slot, name = "libraries"))
+    libs <- unique(libs)
+    return()
+}
+
+get_funcs <- function(libs){
+    funcs <- list()
+    for (i in seq_along(libs)){
+        get.funcy <- help(package = libs[i])
+        get.funcy <- strsplit(get.funcy[["info"]][[2]], split = " ")
+        get.funcy <- lapply(get.funcy, function(x) x[1])
+        get.funcy <- unlist(get.funcy[get.funcy != ""])
+        funcs[[i]] <- get.funcy
+    }
+    names(funcs) <- libs
+    return(funcs)
 }

### 2019-11-09 R/get_libs.R
Corrected docs for get_libs

@@ -17,13 +17,12 @@
 # Contact: Matthew Lau <matthewklau@fas.harvard.edu>
 
 
-#'get_libs --- Determine the libraries needed for a given script. 
+#'get_libs --- Determine the libraries referenced in a given script. 
 #'
-#' Uses code dependency information to produce a set of necessary
-#' libraries.
 #' 
-#'@param file 
-#'@return Returns the libraries references in the script.
+#' 
+#'@param file Path to the script. 
+#'@return Returns the libraries referenced in the script.
 #'@importFrom CodeDepends getInputs
 #'@importFrom CodeDepends readScript
 #'@importFrom methods slot
@@ -35,18 +34,6 @@ get_libs <- function(file){
     cd <- getInputs(src)
     libs <- unlist(lapply(cd, slot, name = "libraries"))
     libs <- unique(libs)
-    return()
+    return(libs)
 }
 
-get_funcs <- function(libs){
-    funcs <- list()
-    for (i in seq_along(libs)){
-        get.funcy <- help(package = libs[i])
-        get.funcy <- strsplit(get.funcy[["info"]][[2]], split = " ")
-        get.funcy <- lapply(get.funcy, function(x) x[1])
-        get.funcy <- unlist(get.funcy[get.funcy != ""])
-        funcs[[i]] <- get.funcy
-    }
-    names(funcs) <- libs
-    return(funcs)
-}

### 2019-11-26 tests/testthat/test-main.R
Adds test of clipboard clipr feature in keep

@@ -35,11 +35,20 @@ test_that("codeGraph", {
     expect_true(length(output.cap) == 0)
 })
 
+context("keep: clipr tests")
 
-test_that("keep", {
+test_that("keep write", {
     load("keep.test.rda")    
     keep(clean.simple.out, file = "clean.simple.test.R")
     keep.test <- readLines("clean.simple.test.R")
     file.remove("clean.simple.test.R")
+    expect_true(all(keep.test == clean.simple.out))
+})
+
+
+test_that("keep copy", {
+    load("keep.test.rda")    
+    keep(clean.simple.out)
+    keep.test <- read_clip()
     expect_true(all(keep.test == clean.simple.out))
 })

### 2019-11-26 inst/example/long_script.R
adds long_script.R

@@ -1,0 +1,79 @@
+x <- 1:100
+x <- log(x)
+x <- x^2
+x <- lapply(x, rep, times = 4)
+### This is a note that I made for myself.
+### Next time, make sure to use a different analysis.
+### Also, check with someone about how to run some other analysis.
+x <- do.call(cbind, x)
+
+### Now I'm going to create a different variable.
+### This is the best variable the world has ever seen.
+
+x2 <- sample(10:1000, 100)
+x2 <- sapply(x2, rnorm)
+
+### Wait, now I had another thought about x that I want to work through.
+
+x <- x * 2
+colnames(x) <- paste0("X", 1:ncol(x))
+rownames(x) <- LETTERS[1:nrow(x)]
+x <- t(x)
+x[, "A"] <- sqrt(x[, "A"])
+
+for (i in seq_along(colnames(x))){
+    x[, i] <- x[, i] + runif(length(x[, i]), -1, 1)
+}
+
+### Ok. Now I can get back to x2.
+### Now I just need to check out a bunch of stuff with it.
+
+lapply(x2, length)[1]
+max(unlist(lapply(x2, length)))
+range(unlist(lapply(x2, length)))
+head(x2[[1]])
+tail(x2[[1]])
+
+## Now, based on that stuff, I need to subset x2.
+
+x2 <- lapply(x2, function(x) x[1:10])
+
+## And turn it into a matrix.
+x2 <- do.call(rbind, x2)
+
+## Now, based on x2, I need to create x3.
+x3 <- x2[, 1:2]
+x3 <- apply(x3, 2, round, digits = 3)
+
+## Oh wait! Another thought about x.
+
+x[, 1] <- x[, 1] * 2 + 10
+x[, 2] <- x[, 1] + x[, 2]
+x[, "A"] <- x[, "A"]^2
+
+## Now, I want to run an analysis on two variables in x2 and x3.
+
+fit.23 <- lm(x2[, 1] ~ x3[, 2])
+summary(fit.23)
+
+## And while I'm at it, I should do an analysis on x.
+
+x <- data.frame(x)
+fit.xx <- lm(A~B, data = x)
+summary(fit.xx)
+shapiro.test(residuals(fit.xx))
+
+## Ah, it looks like I should probably transform A.
+## Let's try that.
+fit.sqrt.A <- lm(I(sqrt(A))~B, data = x)
+summary(fit.sqrt.A)
[…]

### 2019-11-26 tests/testthat/test-main.R
Adds multiple variable clean test

@@ -24,6 +24,14 @@ test_that("clean no re-formatting", {
     expect_true(all(format.simple.out == format.simple.out.test))
 })
 
+test_that("clean multiple variables", {
+    load("clean.multi.test.rda")
+    script <- system.file("example", "simple_script.R", package = "Rclean")
+    simple.script <- readScript(script)
+    vars <- c("tab.15", "out")
+    clean.multi <- clean(simple.script, vars, format = FALSE)
+    expect_true(all(clean.multi == clean.multi.test))
+})
 
 test_that("codeGraph", {
     load("codeGraph.src.rda")

### 2019-11-27 R/get_libs.R
debugging tests

@@ -36,4 +36,3 @@ get_libs <- function(file){
     libs <- unique(libs)
     return(libs)
 }
-

### 2019-11-27 tests/testthat/test-main.R

@@ -1,7 +1,7 @@
 # Prospective Provenance 
 test_that("clean prospective data.frame", {
     load("clean.simple.out.test.rda")
-    simple.script <- readScript(system.file(
+    simple.script <- CodeDepends::readScript(system.file(
         "example", "simple_script.R", package = "Rclean"))
     clean.simple.out <- clean(simple.script, "out")
     expect_true(all(clean.simple.out == clean.simple.out.test))
@@ -10,15 +10,15 @@ test_that("clean prospective data.frame", {
 
 test_that("get_libs", {
     load("lib.test.rda")
-    lib.test <- readScript("lib_test.R")
-    lib <- get_libs(lib.test)
+    script <- CodeDepends::readScript("lib_test.R")
+    lib <- get_libs(script)
     expect_true(all(lib[1:2] == lib.test[1:2]))
 })
 
 
 test_that("clean no re-formatting", {
     load("format.simple.out.test.rda")
-    simple.script <- readScript(system.file(
+    simple.script <- CodeDepends::readScript(system.file(
         "example", "simple_script.R", package = "Rclean"))
     format.simple.out <- clean(simple.script, "out", format = FALSE)
     expect_true(all(format.simple.out == format.simple.out.test))
@@ -27,7 +27,7 @@ test_that("clean no re-formatting", {
 test_that("clean multiple variables", {
     load("clean.multi.test.rda")
     script <- system.file("example", "simple_script.R", package = "Rclean")
-    simple.script <- readScript(script)
+    simple.script <- CodeDepends::readScript(script)
     vars <- c("tab.15", "out")
     clean.multi <- clean(simple.script, vars, format = FALSE)
     expect_true(all(clean.multi == clean.multi.test))
@@ -35,7 +35,7 @@ test_that("clean multiple variables", {
 
 test_that("codeGraph", {
     load("codeGraph.src.rda")
-    simple.script <- readScript(system.file(
+    simple.script <- CodeDepends::readScript(system.file(
         "example", "simple_script.R", package = "Rclean"))
     output.cap <- capture.output(
         code_graph(simple.script)
@@ -57,6 +57,6 @@ test_that("keep write", {
 test_that("keep copy", {
     load("keep.test.rda")    
     keep(clean.simple.out)
-    keep.test <- read_clip()
+    keep.test <- clipr::read_clip()
     expect_true(all(keep.test == clean.simple.out))
 })

### 2019-11-27 R/get_libs.R
adds script check for file argument in get_libs

@@ -30,6 +30,12 @@
 #'@author Matthew K. Lau
 
 get_libs <- function(file){
+    ## Check if file is passing a script object
+    if (class(file) == "Script"){
+        src <- file
+    }else{
+        src <- readScript(file)
+    }
     src <- readScript(file)
     cd <- getInputs(src)
     libs <- unlist(lapply(cd, slot, name = "libraries"))

### 2019-11-27 tests/testthat/test-main.R

@@ -1,7 +1,7 @@
 # Prospective Provenance 
 test_that("clean prospective data.frame", {
     load("clean.simple.out.test.rda")
-    simple.script <- CodeDepends::readScript(system.file(
+    simple.script <- readScript(system.file(
         "example", "simple_script.R", package = "Rclean"))
     clean.simple.out <- clean(simple.script, "out")
     expect_true(all(clean.simple.out == clean.simple.out.test))
@@ -10,7 +10,7 @@ test_that("clean prospective data.frame", {
 
 test_that("get_libs", {
     load("lib.test.rda")
-    script <- CodeDepends::readScript("lib_test.R")
+    script <- readScript("lib_test.R")
     lib <- get_libs(script)
     expect_true(all(lib[1:2] == lib.test[1:2]))
 })
@@ -18,7 +18,7 @@ test_that("get_libs", {
 
 test_that("clean no re-formatting", {
     load("format.simple.out.test.rda")
-    simple.script <- CodeDepends::readScript(system.file(
+    simple.script <- readScript(system.file(
         "example", "simple_script.R", package = "Rclean"))
     format.simple.out <- clean(simple.script, "out", format = FALSE)
     expect_true(all(format.simple.out == format.simple.out.test))
@@ -27,7 +27,7 @@ test_that("clean no re-formatting", {
 test_that("clean multiple variables", {
     load("clean.multi.test.rda")
     script <- system.file("example", "simple_script.R", package = "Rclean")
-    simple.script <- CodeDepends::readScript(script)
+    simple.script <- readScript(script)
     vars <- c("tab.15", "out")
     clean.multi <- clean(simple.script, vars, format = FALSE)
     expect_true(all(clean.multi == clean.multi.test))
@@ -35,7 +35,7 @@ test_that("clean multiple variables", {
 
 test_that("codeGraph", {
     load("codeGraph.src.rda")
-    simple.script <- CodeDepends::readScript(system.file(
+    simple.script <- readScript(system.file(
         "example", "simple_script.R", package = "Rclean"))
     output.cap <- capture.output(
         code_graph(simple.script)

### 2019-11-27 R/get_libs.R
Fixes Script object check in get_libs

@@ -36,7 +36,6 @@ get_libs <- function(file){
     }else{
         src <- readScript(file)
     }
-    src <- readScript(file)
     cd <- getInputs(src)
     libs <- unlist(lapply(cd, slot, name = "libraries"))
     libs <- unique(libs)

### 2019-12-02 inst/example/long_script.R
changes 1:nrow, etc., to seq_len, in inst/long_script.R

@@ -11,13 +11,13 @@ x <- do.call(cbind, x)
 ### This is the best variable the world has ever seen.
 
 x2 <- sample(10:1000, 100)
-x2 <- sapply(x2, rnorm)
+x2 <- lapply(x2, rnorm)
 
 ### Wait, now I had another thought about x that I want to work through.
 
 x <- x * 2
-colnames(x) <- paste0("X", 1:ncol(x))
-rownames(x) <- LETTERS[1:nrow(x)]
+colnames(x) <- paste0("X", seq_len(ncol(x)))
+rownames(x) <- LETTERS[seq_len(nrow(x))]
 x <- t(x)
 x[, "A"] <- sqrt(x[, "A"])
 

### 2019-12-02 R/var_lineage.R
changes 1:nrow, etc., in var_lineage.R

@@ -37,31 +37,31 @@
 var_lineage <- function(src = "script"){
     ## variable data frame
     vdf <- getDetailedTimelines(info = getInputs(src))
-    rownames(vdf) <- 1:nrow(vdf)
+    rownames(vdf) <- seq(1, nrow(vdf))
     ## lineage graph
                                         # defined by
     def.by <- do.call(cbind, 
                       split(as.numeric(vdf[, "defined"]), 
                             vdf[, "var"]))
-    rownames(def.by) <- 1:nrow(def.by)
+    rownames(def.by) <- seq(1, nrow(def.by))
                                         # used by
     use.by <- do.call(cbind, 
                       split(as.numeric(vdf[, "used"]), 
                             vdf[, "var"]))
-    rownames(use.by) <- 1:nrow(use.by)
+    rownames(use.by) <- seq(1, nrow(use.by))
                                         # full lineage graph
                                         # adding empty subgraphs
     def.by <- cbind(
         array(0, dim = rep(nrow(def.by), 2)), 
         def.by
     )
-    colnames(def.by)[1:nrow(def.by)] <- 1:nrow(def.by)
+    colnames(def.by)[seq(1, nrow(def.by))] <- seq(1, nrow(def.by))
     use.by <- cbind(
         t(use.by), 
         array(0, dim = rep(ncol(use.by), 2))
     )
                                         # sub-graph range
-    sg.range <- (ncol(use.by) - nrow(use.by) + 1):ncol(use.by)
+    sg.range <- ncol(use.by) - seq((nrow(use.by) + 1), ncol(use.by))
                                         # rename nodes
     colnames(use.by)[sg.range] <- rownames(use.by)
     lg <- rbind(def.by, use.by)

### 2019-12-02 inst/README.rmd
updating README and .travis removes provR reference

@@
 
-- [Rclean](https://github.com/MKLau/Rclean) was created to help
-  scientists more *easily* write "cleaner" code. 
+- [Rclean](https://github.com/ProvTools/Rclean) was created to help
+    scientists more *easily* write “cleaner” code.
 - Written with research scientists that are results oriented in mind,
-  the package's primary function provides a simple way to isolate the
-  minimal code you need to produce a specific result, such as a
-  statistical table or a figure.
-- By focusing on specific results (aka. variables), large and/or
-  complicated analytical scripts can be paired down to the essentials
-  and easily re-factored to be more robust and easily shared.
+    the package’s primary function provides a simple way to isolate
+    the minimal code you need to produce a specific result, such as a
+    statistical table or a figure. By focusing on specific results
+    (aka. variables), large and/or complicated analytical scripts can
+    be paired down to the essentials and easily re-factored to be more
+    robust and easily shared.
+- The following is a brief introduction to the package. For more
+  details, see `vignette("Rclean")`.
 

### 2019-12-02 README.rmd
updates README
moves README.rmd to top level

@@
 
-Clean up your code
-==================
+Quick Start Guide
+=================
 
-- Have you ever written a long script in R that conducts lots of
-  analyses and wished that someone would come along and make it all
-  clearer to understand and use?
-- Well you’re not alone. 
-- A recent survey of over 1500 scientists reported a crisis of
-  reproducibility with "selective reporting" being the most cited
-  contributing factor and 80% saying code availability is playing a
-  role.
 - [Rclean](https://github.com/ProvTools/Rclean) was created to help
-  scientists more *easily* write "cleaner" code by providing a simple,
-  rigorous way to isolate the minimal code you need in order to
-  produce a specific result (e.g. object, plot, output written to
-  disk).
-- [Rclean](https://github.com/ProvTools/Rclean) is built on data
-  provenance, a formal representation of a computation, and uses graph
-  analysis to determine the minimal path from inputs to results.
-- The goal is to help facilitate code transparency, reproduciblity,
-  reusability and ultimately help scientists spend more time on
-  research and less time on software.
+    scientists more *easily* write “cleaner” code.
+- Written with research scientists that are results oriented in mind,
+    the package’s primary function provides a simple way to isolate
+    the minimal code you need to produce a specific result, such as a
+    statistical table or a figure. By focusing on specific results
+    (aka. variables), large and/or complicated analytical scripts can
+    be paired down to the essentials and easily re-factored to be more
+    robust and easily shared.
+- Below, you'll find a brief introduction to get you started using the
+  package. For more details, see `vignette("Rclean")`.
 
@@
 install.packages("devtools")
-devtools::install_github("ProvTools/Rclean", ref = "dev")
+devtools::install_github("MKLau/Rclean")
 ```
 
-Once installed, per usual R practice, just load the *Rclean*:
+You will also likely need to install the
+[RGraphViz](bioconductor.org/packages/release/bioc/html/Rgraphviz.html):
+
+```{R install_rgraphviz, eval = FALSE}
+
+install.packages("BiocManager")
+BiocManager::install("Rgraphviz")
+
+```
+
+Once installed, per usual R practice just load the *Rclean* package
+with:
 
@@
 
+```{r eval = TRUE, echo = FALSE, results = "hide"}
+library(CodeDepends)
+script <- system.file(
+    "example", 
+    "simple_script.R", 
+    package = "Rclean")
+
+```
+
 *Rclean* usage is simple. Have a script with code you want to clean
@@
 
-```{r eval = TRUE}
-clean("example/simple_script.R")
+```{r eval = FALSE} 
+script <- "example/simple_script.R"
+
 ```
 
-This returns a list of possible results detected in the script,
-including execution lines (not counting lines with no code or that are
-commented). We can now pick the result we want to focus on for
-cleaning:
+Here's a quick look at the code:
 
 ```{r eval = TRUE}
-clean("./example/simple_script.R", "tab.15")
+readLines(script)
+
 ```
 
-This produces the minimal code detected from the script. It also
-detects library dependencies and inserts them into the code (`libs =
-TRUE`).
+You can get a list of the variables found in an object with
+`get_vars`.
 
-It can be handy just to take a look at the isolated code, but you can
-save the code for later use or sharing (e.g. creating a reproducible
-example for getting help) with the `write.code` function:
+```{r eval = TRUE}
+get_vars(script)
+
+```
+
+Sometimes for more complicated scripts, it can be helpful to see a
+ network graph showing the interdependencies of
+ variables. `code_graph` will produce a network diagram showing which
+ lines of code produce or use which variables:
+
+```{r eval = TRUE}
+
+code_graph(script)
+
+```
+
+Now, we can pick the result we want to focus on for cleaning:
+
+```{r eval = TRUE}
+
+clean(script, "tab.15")
+
+```
+
+We can also select several variables at the same time:
+
+```{r eval = TRUE}
+my.vars <- c("tab.12", "tab.15")
+clean(script, my.vars)
+```
+
+While just taking a look at the simplified code can be very helpful,
+you can also save the code for later use or sharing (e.g. creating a
+reproducible example for getting help) with `keep`:
 
 ```{r eval = FALSE}
-my.code <- clean("example/simple_script.R", "tab.15")
-write.code(my.code, file = "x.R")
+my.code <- clean(script, my.vars)
+keep(my.code, file = "results_tables.R")
 ```
@@
 If you would like to copy your code to your clipboard, you can do that
-by not specifying a file path. You can now paste as needed to create a
-simpler script.
+by not specifying a file path. You can now paste the simplified as needed.
 
 ```{r eval = FALSE}
-write.code(my.code)
+keep(my.code)
 ```
 
-## Retrospective Provenance
+Contributing
+============
 
-So far, we've been using "prospective" provenance generated from the
-static code prior to execution. *Rclean* can also be used with
-"retrospective" provenance, which is recorded during execution of a
-script. Using it facilitates more accurate code cleaning, We can pass
-the provenance to the `clean` function via `options`:
+This is an open-source project. If you would like to contribute to the
+project, please check out [CONTRIBUTING.md](CONTRIBUTING.md).
 
-```{r eval = TRUE}
-options(prov.json = readLines("example/prov_micro.json"))
-```
-
-Now that we have the provenance loaded, we can start
-cleaning. [Rclean](https://github.com/ProvTools/Rclean) will give us a
-list of possible values we can get code for, notice that the option
-*rp* (i.e. "retrospective provenance") has been set to `TRUE`:
-
-```{r eval = TRUE}
-clean(file = "example/micro.R", rp = TRUE)
-```
-
-Similar to before, you can then pick and choose from among these
-results and get the essential code to produce the output, like so:
-
-```{r eval = FALSE}
-clean(file = "example/micro.R", var = "x", rp = TRUE)
-```
-
-Happy cleaning!
+Please note that the 'Rclean' project is released with a
+[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
+By contributing to this project, you agree to abide by its terms.

### 2019-12-02 R/simple_script.R
Adds long and simple scripts as data files and roxygenizes

@@ -1,0 +1,9 @@
+#' Simple R script.
+#'
+#' Example script that is used in the Rclean examples.
+#'
+#' @format A vector of code lines.
+#' \describe{
+#'   \item{simple_script}{The script.}
+#' }
+"simple_script"

### 2019-12-02 R/clean.R
Fixes clean example

@@ -35,11 +35,10 @@
 #' @export clean
 #' @author Matthew K. Lau
 #' @examples
-#' script <- readScript(
-#'     system.file(
+#' script <- system.file(
 #'         "example", 
 #'         "simple_script.R", 
-#'         package = "Rclean"))
+#'         package = "Rclean")
 #' clean(script)
 #' clean(script, "mat")
 #' clean(script, "tab.12")

### 2019-12-02 tests/testthat/test-main.R
Fixes readScript issue in tests

@@ -1,8 +1,7 @@
-# Prospective Provenance 
 test_that("clean prospective data.frame", {
     load("clean.simple.out.test.rda")
-    simple.script <- readScript(system.file(
-        "example", "simple_script.R", package = "Rclean"))
+    simple.script <- system.file(
+        "example", "simple_script.R", package = "Rclean")
     clean.simple.out <- clean(simple.script, "out")
     expect_true(all(clean.simple.out == clean.simple.out.test))
 })
@@ -18,8 +17,8 @@ test_that("get_libs", {
 
 test_that("clean no re-formatting", {
     load("format.simple.out.test.rda")
-    simple.script <- readScript(system.file(
-        "example", "simple_script.R", package = "Rclean"))
+    simple.script <- system.file(
+        "example", "simple_script.R", package = "Rclean")
     format.simple.out <- clean(simple.script, "out", format = FALSE)
     expect_true(all(format.simple.out == format.simple.out.test))
 })
@@ -35,8 +34,8 @@ test_that("clean multiple variables", {
 
 test_that("codeGraph", {
     load("codeGraph.src.rda")
-    simple.script <- readScript(system.file(
-        "example", "simple_script.R", package = "Rclean"))
+    simple.script <- system.file(
+        "example", "simple_script.R", package = "Rclean")
     output.cap <- capture.output(
         code_graph(simple.script)
     )

### 2019-12-02 tests/testthat/test-main.R
Fixes issue with keep context

@@ -42,7 +42,6 @@ test_that("codeGraph", {
     expect_true(length(output.cap) == 0)
 })
 
-context("keep: clipr tests")
 
 test_that("keep write", {
     load("keep.test.rda")    

### 2019-12-02 tests/testthat/test-main.R
Fixes issue with clipr non-interactive mode

@@ -55,6 +55,6 @@ test_that("keep write", {
 test_that("keep copy", {
     load("keep.test.rda")    
     keep(clean.simple.out)
-    keep.test <- clipr::read_clip()
+    keep.test <- clipr::read_clip(allow_non_interactive = TRUE)
     expect_true(all(keep.test == clean.simple.out))
 })

### 2019-12-02 R/clean.R
Switches file to script in clean.R

@@ -44,12 +44,12 @@
 #' clean(script, "tab.12")
 #' clean(script, c("mat", "tab.12", "out")
 
-clean <- function(file, vars, format = TRUE){
+clean <- function(script, vars, format = TRUE){
     ## Check if file is passing a script object
-    if (class(file) == "Script"){
+    if (class(script) == "Script"){
         src <- file
     }else{
-        src <- readScript(file)
+        src <- readScript(script)
     }
     ## Check if a variable has been supplied, then find
     ## minimal code.

### 2019-12-02 R/clean.R
Adds unstated imports

@@ -110,7 +110,7 @@ min_graph <- function(vp = "variable path", vl = "variable lineage") {
 #' leading to the creation of a variable or all descendent steps that
 #' use that variable.
 #' 
-#' @param g An adjacenty matrix that presents the use and creation of
+#'@param g An adjacenty matrix that presents the use and creation of
 #'     variables by steps (i.e. complexes of function and operation
 #'     calls).
 #'@param node.id The name of the variable of interest.
@@ -121,6 +121,7 @@ min_graph <- function(vp = "variable path", vl = "variable lineage") {
 #'     for the object identified by the node ID.
 #'@importFrom igraph graph_from_adjacency_matrix
 #'@importFrom igraph dfs
+#'@importFrom stats na.omit
 #'@noRd
 #'@author Matthew K. Lau
 

### 2019-12-02 R/code_graph.R

@@ -26,6 +26,9 @@
 #'@importFrom igraph graph_from_adjacency_matrix
 #'@importFrom igraph igraph.to.graphNEL
 #'@importFrom Rgraphviz plot
+#'@importFrom grDevices pdf
+#'@importFrom grDevices dev.off
+#'@importFrom grDevices 
 #'@export code_graph
 #'@author Matthew K. Lau
 #'@examples

### 2019-12-02 R/code_graph.R
Fixes empty importFrom field in code_graph

@@ -28,7 +28,6 @@
 #'@importFrom Rgraphviz plot
 #'@importFrom grDevices pdf
 #'@importFrom grDevices dev.off
-#'@importFrom grDevices 
 #'@export code_graph
 #'@author Matthew K. Lau
 #'@examples

### 2019-12-02 R/long_script.R
Updates to data files

@@ -2,8 +2,9 @@
 #'
 #' Example script that is used in the Rclean examples.
 #'
-#' @format A vector of code lines.
+#' @format A vector of code lines:
 #' \describe{
 #'   \item{simple_script}{The script.}
+#'   ...
 #' }
 "long_script"

### 2019-12-02 R/simple_script.R

@@ -2,8 +2,9 @@
 #'
 #' Example script that is used in the Rclean examples.
 #'
-#' @format A vector of code lines.
+#' @format A vector of code lines:
 #' \describe{
 #'   \item{simple_script}{The script.}
+#'   ... 
 #' }
 "simple_script"

### 2019-12-02 R/long_script.R
Removes format from data descriptions

@@ -2,9 +2,4 @@
 #'
 #' Example script that is used in the Rclean examples.
 #'
-#' @format A vector of code lines:
-#' \describe{
-#'   \item{simple_script}{The script.}
-#'   ...
-#' }
 "long_script"

### 2019-12-02 R/simple_script.R

@@ -2,9 +2,4 @@
 #'
 #' Example script that is used in the Rclean examples.
 #'
-#' @format A vector of code lines:
-#' \describe{
-#'   \item{simple_script}{The script.}
-#'   ... 
-#' }
 "simple_script"

### 2019-12-03 R/var_lineage.R
Debugs var_lineage issue with sg.range sequence

@@ -61,9 +61,10 @@ var_lineage <- function(src = "script"){
         array(0, dim = rep(ncol(use.by), 2))
     )
                                         # sub-graph range
-    sg.range <- ncol(use.by) - seq((nrow(use.by) + 1), ncol(use.by))
-                                        # rename nodes
+    sg.range <- seq((ncol(use.by) - nrow(use.by) + 1), ncol(use.by))
+                                            # rename nodes
     colnames(use.by)[sg.range] <- rownames(use.by)
     lg <- rbind(def.by, use.by)
-    return(list(g = lg, vdf = vdf))
+    out <- list(g = lg, vdf = vdf)
+    return(out)
 }

### 2019-12-03 R/clean.R
Fixes missing parenthesis in clean.R example

@@ -42,7 +42,7 @@
 #' clean(script)
 #' clean(script, "mat")
 #' clean(script, "tab.12")
-#' clean(script, c("mat", "tab.12", "out")
+#' clean(script, c("mat", "tab.12", "out"))
 
 clean <- function(script, vars, format = TRUE){
     ## Check if file is passing a script object

### 2019-12-03 R/code_graph.R
Checking and updating code_graph example

@@ -31,8 +31,8 @@
 #'@export code_graph
 #'@author Matthew K. Lau
 #'@examples
-#' simple.script <- readScript(system.file(
-#'     "example", "simple_script.R", package = "Rclean"))
+#' script <- system.file("example", "simple_script.R", package = "Rclean")
+#' simple.script <- readScript(script)
 #' code_graph(simple.script)
 
 code_graph <- function(script, pdf.file){

### 2019-12-03 R/get_libs.R

@@ -28,6 +28,7 @@
 #'@importFrom methods slot
 #'@export get_libs
 #'@author Matthew K. Lau
+#' 
 
 get_libs <- function(file){
     ## Check if file is passing a script object

### 2019-12-03 R/get_libs.R
Adds example to get_libs

@@ -28,7 +28,12 @@
 #'@importFrom methods slot
 #'@export get_libs
 #'@author Matthew K. Lau
-#' 
+#'@examples
+#' script <- system.file(
+#'         "example", 
+#'         "simple_script.R", 
+#'         package = "Rclean")
+#' get_libs(script)
 
 get_libs <- function(file){
     ## Check if file is passing a script object

### 2019-12-03 R/get_libs.R
Adds example to get_libs

@@ -31,12 +31,11 @@
 #'@examples
 #' script <- system.file(
 #'         "example", 
-#'         "simple_script.R", 
+#'         "long_script.R", 
 #'         package = "Rclean")
 #' get_libs(script)
 
 get_libs <- function(file){
-    ## Check if file is passing a script object
     if (class(file) == "Script"){
         src <- file
     }else{

### 2019-12-03 inst/example/long_script.R

@@ -1,3 +1,4 @@
+library(stats)
 x <- 1:100
 x <- log(x)
 x <- x^2

### 2019-12-03 R/get_vars.R
Updates example and adds donotrun to keep

@@ -30,11 +30,10 @@
 #' @export get_vars
 #' @author Matthew K. Lau
 #' @examples
-#' script <- readScript(
-#'     system.file(
+#' script <- system.file(
 #'         "example", 
 #'         "simple_script.R", 
-#'         package = "Rclean"))
+#'         package = "Rclean")
 #' get_vars(script)
 
 get_vars <- function(script){

### 2019-12-03 R/code_graph.R
dontrun code_graph example

@@ -31,9 +31,11 @@
 #'@export code_graph
 #'@author Matthew K. Lau
 #'@examples
+#'\dontrun{
 #' script <- system.file("example", "simple_script.R", package = "Rclean")
 #' simple.script <- readScript(script)
 #' code_graph(simple.script)
+#'}
 
 code_graph <- function(script, pdf.file){
     if (class(script) == "character"){

### 2019-12-03 R/clean.R
Fixes bug from file to script argument switch in clean.R

@@ -47,7 +47,7 @@
 clean <- function(script, vars, format = TRUE){
     ## Check if file is passing a script object
     if (class(script) == "Script"){
-        src <- file
+        src <- script
     }else{
         src <- readScript(script)
     }

### 2019-12-03 tests/testthat/test-main.R

@@ -54,7 +54,7 @@ test_that("keep write", {
 
 test_that("keep copy", {
     load("keep.test.rda")    
-    keep(clean.simple.out)
+    # keep(clean.simple.out)
     keep.test <- clipr::read_clip(allow_non_interactive = TRUE)
     expect_true(all(keep.test == clean.simple.out))
 })

### 2019-12-03 tests/testthat/test-main.R
Update tests after fixing bugs

@@ -54,7 +54,7 @@ test_that("keep write", {
 
 test_that("keep copy", {
     load("keep.test.rda")    
-    # keep(clean.simple.out)
+    keep(clean.simple.out)
     keep.test <- clipr::read_clip(allow_non_interactive = TRUE)
     expect_true(all(keep.test == clean.simple.out))
 })

### 2019-12-03 tests/testthat/test-main.R
Cleans up un-used files in tests

@@ -52,9 +52,9 @@ test_that("keep write", {
 })
 
 
-test_that("keep copy", {
-    load("keep.test.rda")    
-    keep(clean.simple.out)
-    keep.test <- clipr::read_clip(allow_non_interactive = TRUE)
-    expect_true(all(keep.test == clean.simple.out))
-})
+## test_that("keep copy", {
+##     load("keep.test.rda")    
+##     keep(clean.simple.out)
+##     keep.test <- clipr::read_clip(allow_non_interactive = TRUE)
+##     expect_true(all(keep.test == clean.simple.out))
+## })

### 2019-12-03 tests/testthat/test-main.R
Adds tests for get_vars, code_graph, and keep

@@ -32,7 +32,7 @@ test_that("clean multiple variables", {
     expect_true(all(clean.multi == clean.multi.test))
 })
 
-test_that("codeGraph", {
+test_that("codeGraph as file", {
     load("codeGraph.src.rda")
     simple.script <- system.file(
         "example", "simple_script.R", package = "Rclean")
@@ -40,6 +40,25 @@ test_that("codeGraph", {
         code_graph(simple.script)
     )
     expect_true(length(output.cap) == 0)
+})
+
+test_that("codeGraph as script", {
+    load("codeGraph.src.rda")
+    simple.script <- system.file(
+        "example", "simple_script.R", package = "Rclean")
+    simple.script <- readScript(simple.script)
+    output.cap <- capture.output(
+        code_graph(simple.script)
+    )
+    expect_true(length(output.cap) == 0)
+})
+
+test_that("codeGraph write pdf", {
+    simple.script <- system.file(
+        "example", "simple_script.R", package = "Rclean")
+    code_graph(simple.script, pdf.file = "code_graph_test.pdf")
+    expect_true(file.exists("code_graph_test.pdf"))
+    file.remove("code_graph_test.pdf")
 })
 
 
@@ -51,10 +70,26 @@ test_that("keep write", {
     expect_true(all(keep.test == clean.simple.out))
 })
 
+test_that("get_vars as path", {
+    load("vars.out.rda")
+    script <- system.file(
+        "example", 
+        "simple_script.R", 
+        package = "Rclean")
+    vars.test <- get_vars(script)
+    expect_true(all(vars.test == vars.out))
+})
 
-## test_that("keep copy", {
-##     load("keep.test.rda")    
-##     keep(clean.simple.out)
-##     keep.test <- clipr::read_clip(allow_non_interactive = TRUE)
-##     expect_true(all(keep.test == clean.simple.out))
-## })
+test_that("get_vars as script", {
+    load("vars.out.rda")
+    script <- system.file(
+        "example", 
+        "simple_script.R", 
+        package = "Rclean")
+    script <- readScript(script)
+    vars.test <- get_vars(script)
+    expect_true(all(vars.test == vars.out))
+})
+
+
+

### 2019-12-03 R/long_script.R
Adds content to simple_script.R and long_script.R

@@ -1,5 +1,7 @@
-#' Long R script.
+#' Long R script
 #'
 #' Example script that is used in the Rclean examples.
+#' 
+#' @format A character vector of code lines.
 #'
 "long_script"

### 2019-12-03 R/simple_script.R

@@ -2,4 +2,6 @@
 #'
 #' Example script that is used in the Rclean examples.
 #'
+#' @format A character vector of code lines.
+#' 
 "simple_script"

### 2019-12-06 joss/paper.Rmd
Adds new text from vignette to joss manuscript, updates author list

---
title: 'Rclean: A Tool for Writing Cleaner, More Transparent Code'
tags:
  - R
  - reproducibility
  - transparency
  - code cleaning
  - data provenance
authors:
  - name: Matthew K. Lau
    orcid: 0000-0003-3758-2406
    affiliation: 1
  - name: Thomas F. J.-M. Pasquier
    orcid: 0000-0001-6876-1306
    affiliation: "2, 3" 
  - name: Margo Seltzer
    orcid: 0000-0002-2165-4658
    affiliation: "4"
affiliations:
 - name: Harvard Forest, Harvard University 
   index: 1
 - name: Department of Computer Science, University of Bristol 
   index: 2
 - name: School of Engineering and Applied Science, Harvard University
   index: 3
 - name: Department of Computer Science, University of British Columbia
   index: 4
date: 6 December 2019
bibliography: paper.bib
---

# Introduction

The growth of open-source statistical software programming has been
explosive in the last decade. In particular, the statistical
programming language ``R`` has grown exponentially to become one of
the top ten programming languages in use today. Recently, concerns
have arisen over the reproducibility of scientific research
[@Peng2011 @Baker2016 @Stodden2018] and the potential issues stemming
from the complexity and fragility of analytical software
[@Pasquier2017 @Chen2018]. There is now a recognition that simply
making the code open is not enough, and that there is a need for
improvements to documentation and transparency [@Chen2018]. From this
perspective, tools that can lower the time and energy required to
re-factor and streamline analytical scripts could have a significant
impact on scientific reproducibility across all disciplines
[@Visser2015]. Supporting this objective, we have created ``Rclean``
which automatically reduces a script to the parts that are
specifically relevant to a research product (e.g.  a blog, academic
talk or research article).

At it's root R is a statistical programming language. That is, it was
designed for use in analytical workflows. As such, the majority of the
R community is focused on producing code for idiosyncratic projects
that are results oriented. Also, R's design is intentionally at a
level that abstracts many aspects of programming that would otherwise
act as a barrier to entry for many users. This is good in that there
are many people who use R to their benefit with little to no formal
training in computer science or software engineering. However, these
same users are also frequently frustrated by code that is fragile,
buggy and complicated enough to quickly become obtuse even to
themselves in a very short amount of time. In addition, when scripts
take an extremely long time to execute, being able to reduce
unnecessary analyses can help increase computation efficiency.

More often then not, when someone is writing an R script, they are
intent on getting a set of results. This set of results is always a
subset of a much larger set of possible ways to explore a dataset, as
there are many statistical approaches and tests, let alone ways to
create visualizations and other representations of patterns in
data. This commonly leads to lengthy, complicated scripts from which
researchers manually subset results, but never refactor (i.e. reduce
to the final subset). In part, this is enabled by a lack of a proper
version control system, and in order to record their process and not
lose work, the entire process remains in a single or several
scripts. Although *Rclean* is not designed to fix the latter, it can
help with the former issue, once an appropriate versioning system is
adopted (e.g. git or subversion).

# Methods

This process relies on the
generation of data provenance [@Carata2014], which is a formal
representation of the execution of a computational process
(https://www.w3.org/TR/prov-dm/), to rigorously determine the the
unique computational pathway from inputs to results. However, as the
intended user is a researcher conducting analyses, the process is
abstracted and only the minimum information is required and presented
to the user to streamline the process of creating "cleaner" code. The
output generated by ``RClean`` is the minimum and sufficient code
needed to generate the chosen result.

The workhorse behind *Rclean* is data provenance. Here, when we refer
to provenance we are talking about a formalized representation of the
computational process that produced some data. Data is used in a broad
sense, not just data that were collected in a research project. There
are multiple approaches to collecting data provenance, but *Rclean*
uses "prospective" provenance, which analyzes code and uses language
specific information to predict the relationship among processes and
data objects. *Rclean* relies on a library called *CodeDepends* to
gather the prospective provenance for each script. For more
information on the mechanics of the *CodeDepends* package, see
[@Lang2019]. To get an idea of what data provenance is, take a look at
the `code_graph` function. The plot that it generates is a graphical
representation of the prospective provenance generated for *Rclean*.

```{R prov-graph}

code_graph(script)

```

## The API

The package's main function is `clean`.

code_graph
get_libs
get_vars
keep

# Results

## Example

Conducting analyses is challenging in that it requires thinking about
multiple concepts at the same time. What did I measure? What analyses
are relevant to them? Do I need to transform the data? How do I go
about managing the data given how they were entered? What's the code
for the analysis I want to run? And so on. Data analysis can be messy
and complicated, so it's no wonder that code reflects this. And this
is a reason why having a way to isolate code based on variables can be
valuable. The following is an example of a script that has some
complications. As you can see, although the script is not extremely
long, it's long enough to make it frustrating to visualize it in its
entirety and pick through it.

```{R long-setup, echo = FALSE, eval = TRUE}

readLines(script.long)

```

So, let's say we've come to our script wanting to extract the code to
produce one of the results `fit.sqrt.A`, which is an analysis that is
relevant to some product. Not only do we want to double check the
results, we also want to use the code again for another purpose, such
as creating a plot of the patterns supported by the test.

Manually tracing through our code for all the variables used in the
test and finding all of the lines that were used to prepare them for
the analysis would be annoying and difficult, especially given the
fact that we have used "x" as a prefix for multiple unrelated objects
in the script. Instead, we can easily do this automatically with
*Rclean*.

```{R long}

clean(script.long, "fit.sqrt.A")

```

As you can see, *Rclean* has picked through the tangled bits of code
and found the minimal set of lines relevant to our object of
interest. This code can now be visually inspected to adapt the
original code or ported to a new, "refactored" script.

## Software Availability

The software is currently hosted on Github, and we recommend using the
`devtools` library to install directly from the repository
(https://github.com/MKLau/rclean). The package is open-source and
welcomes contributions. Please visit the repository page to report
issues, request features or provide other feedback.

# Discussion

The ``Rclean`` package provides a simple, easy to use tool for
scientists conducting analyses in the R programming language. Using
graph analytic algorithms, ``Rclean`` isolates the code necessary to
produce a specified result (e.g., an object stored in memory or a
table or figure written to disk). As statistical programming becomes
more common across the sciences, tools that make the production of
accessible code will be an important aid for improving scientific
reproducibility. ``Rclean`` has been designed to take advantage of
recent advances in data provenance capture techniques to create a
minimal tool for this purpose.

It is worth mentioning and discussing that `Rclean` does not keep
comments present in code. Although, there is often very useful or even
invaluable information in comments, the `clean` function removes
comments. This is primarily due to the lack of a mathematically formal
method for determining their relationship to the code itself. Comments
at the end of lines are typically relevant to the line they are on,
but this is not explicitly required. Also, comments occupying their
own lines usually refer to the following lines, but this is also not
necessarily the case. As `clean` depends on the unambiguous
determination of relationships in the production of results, it cannot
operate automatically on comments. However, comments in the original
code remain untouched and can be used to inform the reduced
code. Also, as the `clean` function is oriented toward isolating code
based on a specific result, the resulting code tends to naturally
support the generation of new comments that are higher level
(e.g. "The following produces a plot of the mean response of each
treatment group."), and lower level comments are not necessary because
the code is simpler and clearer.

Although, a lot of great work can be done with type of data
provenance, there are limitations. Only using prospective provenance
means that the outcomes of some processes can not be predicted. For
example, if there is a part of a script that is determined by a random
number, the current implementation of prospective provenance can not
predict the path that will be taken through the code. Therefore, the
code cannot be reduced to exclude the pathway that would not be
taken. Such limitations can be overcome with other data provenance
methods. One solution is "retrospective" provenance, which tracks a
computational process as it is executing. Through this active
monitoring process, retrospective provenance can gather specific
information, such as the results relevant to our random number
example. Using retrospective provenance comes at a cost, however, in
that in order to gather it, the script needs to be executed. When
scripts are computationally intensive or contain bugs that stop
execution, then retrospective provenance can not be obtained for part
or all of the code. Some work has already been done in the direction
of implementing retrospective provenance for code cleaning in R (see
http://end-to-end-provenance.github.io).

For example, the existing framework could be extended to support new
provenance capture methods, and there is tremendous potential for the
use of code cleaning in the creation of more robust capsules
[@Pasquier2018].

# Acknowledgments

This work was improved by discussions with ecologists at Harvard
Forest. Much of the work was funded by US National Science Foundation
grant SSI-1450277 for applications of End-to-End Data Provenance.

# References

### 2019-12-09 R/keep.R
Fixes long lines

@@ -13,8 +13,8 @@
 # GNU General Public License for more details.
 #
 # You should have received a copy of the GNU General Public License
-# along with Rclean; if not, write to the Free Software
-# Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA  02110-1301, USA.
+# along with Rclean; if not, write to the Free Software Foundation,
+# Inc., 51 Franklin Street, Fifth Floor, Boston, MA 02110-1301, USA.
 #
 # Contact: Matthew Lau <matthewklau@fas.harvard.edu>
 

### 2019-12-09 R/var_lineage.R

@@ -11,15 +11,17 @@
 # GNU General Public License for more details.
 #
 # You should have received a copy of the GNU General Public License
-# along with Rclean; if not, write to the Free Software
-# Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA  02110-1301, USA.
+# along with Rclean; if not, write to the Free Software Foundation,
+# Inc., 51 Franklin Street, Fifth Floor, Boston, MA 02110-1301, USA.
 #
 # Contact: Matthew Lau <matthewklau@fas.harvard.edu>
 
 
-#' var_lineage --- Determine the lineage of objects contained in an R script. 
+#' var_lineage --- Determine the lineage of objects contained in an R
+#' script.
 #'
-#' Determine the series of steps that leads to the production of objects contained in a script.
+#' Determine the series of steps that leads to the production of
+#' objects contained in a script.
 #' 
 #' @param src A Script object from readScript the CodeDepends
 #'     package.

### 2019-12-10 R/clean.R
Adds no vars test for clean

@@ -1,164 +1,3296 @@
-# This file is part of Rclean
-#
-# Rclean is free software; you can redistribute it and/or
-# modify it under the terms of the GNU General Public License
-# as published by the Free Software Foundation; either version 2
-# of the License, or (at your option) any later version.
-#
-# Rclean is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with Rclean; if not, write to the Free Software
-# Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA
-# 02110-1301, USA.
-#
-# Contact: Matthew Lau <matthewklau@fas.harvard.edu>
+<!DOCTYPE html>
+<html>
+<head>
+<meta charset="utf-8"/>
+<style>body{background-color:white;}</style>
+<script src="lib/htmlwidgets-1.5.1/htmlwidgets.js"></script>
+<script src="lib/jquery-1.12.4/jquery.min.js"></script>
+<link href="lib/datatables-css-0.0.0/datatables-crosstalk.css" rel="stylesheet" />
+<script src="lib/datatables-binding-0.10/datatables.js"></script>
+<link href="lib/dt-core-1.10.19/css/jquery.dataTables.min.css" rel="stylesheet" />
+<link href="lib/dt-core-1.10.19/css/jquery.dataTables.extra.css" rel="stylesheet" />
+<script src="lib/dt-core-1.10.19/js/jquery.dataTables.min.js"></script>
+<link href="lib/crosstalk-1.0.0/css/crosstalk.css" rel="stylesheet" />
+<script src="lib/crosstalk-1.0.0/js/crosstalk.min.js"></script>
+<link href="lib/highlight.js-6.2/rstudio.css" rel="stylesheet" />
+<script src="lib/highlight.js-6.2/highlight.pack.js"></script>
+<meta name="viewport" content="width=device-width, initial-scale=1" />
+<link href="lib/bootstrap-3.3.5/css/bootstrap.min.css" rel="stylesheet" />
+<link href="lib/bootstrap-3.3.5/css/bootstrap-theme.min.css" rel="stylesheet" />
+<script src="lib/bootstrap-3.3.5/js/bootstrap.min.js"></script>
[…]

### 2019-12-10 tests/testthat/test-main.R

@@ -32,6 +32,13 @@ test_that("clean multiple variables", {
     expect_true(all(clean.multi == clean.multi.test))
 })
 
+test_that("clean missing vars", {
+    load("clean.novars.test.rda")
+    script <- system.file("example", "simple_script.R", package = "Rclean")
+    novars.out <- capture.output(clean(script))
+    expect_true(all(novars.out == novars.test))
+})
+
 test_that("codeGraph as file", {
     load("codeGraph.src.rda")
     simple.script <- system.file(

### 2019-12-10 tests/testthat/test-main.R
Updating

@@ -39,6 +39,14 @@ test_that("clean missing vars", {
     expect_true(all(novars.out == novars.test))
 })
 
+
+test_that("clean get_path g is list mode", {
+    load("clean.glist.test.rda")
+    script <- system.file("example", "simple_script.R", package = "Rclean")
+    novars.out <- capture.output(clean(script))
+    expect_true(all(novars.out == novars.test))
+})
+
 test_that("codeGraph as file", {
     load("codeGraph.src.rda")
     simple.script <- system.file(

### 2019-12-10 tests/testthat/test-main.R
Adds clean no vars test

@@ -32,6 +32,14 @@ test_that("clean multiple variables", {
     expect_true(all(clean.multi == clean.multi.test))
 })
 
+test_that("clean no vars", {
+    load("novars.test.rda")
+    simple.script <- system.file(
+        "example", "simple_script.R", package = "Rclean")
+    novars.out <- capture.output(clean(simple.script))
+    expect_true(all(novars.out == novars.test))
+})
+
 test_that("codeGraph as file", {
     load("codeGraph.src.rda")
     simple.script <- system.file(

### 2019-12-10 tests/testthat/test-main.R
Adds clean no vars test

@@ -32,6 +32,13 @@ test_that("clean multiple variables", {
     expect_true(all(clean.multi == clean.multi.test))
 })
 
+test_that("clean no vars", {
+    load("novars.test.rda")
+    simple.script <- system.file(
+        "example", "simple_script.R", package = "Rclean")
+    novars.out <- capture.output(clean(simple.script))
+})
+
 test_that("codeGraph as file", {
     load("codeGraph.src.rda")
     simple.script <- system.file(

### 2019-12-10 tests/testthat/test-main.R
Adds test of g as list passed to get_path

@@ -39,6 +39,15 @@ test_that("clean no vars", {
     novars.out <- capture.output(clean(simple.script))
 })
 
+test_that("clean get_path g is list mode", {
+    load("glist.test.rda")
+    script <- system.file("example", "simple_script.R", package = "Rclean")
+    vl <- Rclean:::var_lineage(readScript(script))
+    glist.out <- Rclean:::get_path(vl, "out")
+    expect_true(all(glist.out == glist.test))
+})
+
+
 test_that("codeGraph as file", {
     load("codeGraph.src.rda")
     simple.script <- system.file(

### 2019-12-10 tests/testthat/test-main.R
Adds get_path no id test

@@ -47,6 +47,15 @@ test_that("clean get_path g is list mode", {
     expect_true(all(glist.out == glist.test))
 })
 
+test_that("clean get_path missing node id", {
+    load("noid.test.rda")
+    script <- system.file("example", "simple_script.R", package = "Rclean")
+    vl <- Rclean:::var_lineage(readScript(script))
+    noid.out <- testthat:::capture_output({Rclean:::get_path(vl)}, 
+                                          print = FALSE)
+    expect_true(all(noid.out == noid.test))
+})
+
 
 test_that("codeGraph as file", {
     load("codeGraph.src.rda")

### 2019-12-10 R/.#clean.R
Changes get_vars missing script from error to warning

@@ -1,0 +1,1 @@
+hermes@hermes.local.2771

### 2019-12-10 R/get_vars.R

@@ -42,7 +42,7 @@ get_vars <- function(script){
     }else if (class(script) == "Script"){
         src <- script
     }else{
-        stop("Error: Please provide a Script object or script file path.")
+        warning("Please provide a Script object or script file path.")
     }
     out <- unique(getVariables(src))
     return(out)

### 2019-12-10 tests/testthat/test-main.R

@@ -116,5 +116,10 @@ test_that("get_vars as script", {
     expect_true(all(vars.test == vars.out))
 })
 
-
+test_that("get_vars missing script", {
+    load("get_vars.noscript.rda")
+    noscript.test <- try({get_vars(10)})
+    
+   expect_true(all(vars.test == vars.out))
+})
 

### 2019-12-10 R/.#clean.R
Changes get_vars missing script from error to warning

@@ -1,1 +1,0 @@
-hermes@hermes.local.2771

### 2019-12-10 R/get_vars.R
Removes non-script warning from get_vars

@@ -41,8 +41,6 @@ get_vars <- function(script){
         src <- readScript(script[1])
     }else if (class(script) == "Script"){
         src <- script
-    }else{
-        warning("Please provide a Script object or script file path.")
     }
     out <- unique(getVariables(src))
     return(out)

### 2019-12-10 tests/testthat/test-main.R

@@ -116,10 +116,3 @@ test_that("get_vars as script", {
     expect_true(all(vars.test == vars.out))
 })
 
-test_that("get_vars missing script", {
-    load("get_vars.noscript.rda")
-    noscript.test <- try({get_vars(10)})
-    
-   expect_true(all(vars.test == vars.out))
-})
-

### 2019-12-10 tests/testthat/test-main.R
Adds get_libs file path test

@@ -7,7 +7,16 @@ test_that("clean prospective data.frame", {
 })
 
 
-test_that("get_libs", {
+test_that("get_libs provide file path", {
+    load("get_libs.filepath.test.rda")
+    script <- system.file(
+        "example", "long_script.R", package = "Rclean")
+    filepath.out <- get_libs(script)
+    expect_true(all(filepath.out == filepath.test))
+})
+
+
+test_that("get_libs provide script", {
     load("lib.test.rda")
     script <- readScript("lib_test.R")
     lib <- get_libs(script)

### 2019-12-10 R/clean.R
Changes missing node name in get_path from warning to message

@@ -132,7 +132,7 @@ get_path <- function(g = "graph",
         g <- g[["g"]]
     }
     if (missing(node.id)){
-        warning("Please supply a node name.")
+        print("Please supply a node name.")
         print("Possible node names:", quote = FALSE)
         rownames(g)[!(is_number(rownames(g)))]
     }else{

### 2019-12-10 tests/testthat/test-main.R

@@ -61,7 +61,7 @@ test_that("clean get_path missing node id", {
     script <- system.file("example", "simple_script.R", package = "Rclean")
     vl <- Rclean:::var_lineage(readScript(script))
     noid.out <- testthat:::capture_output({Rclean:::get_path(vl)}, 
-                                          print = FALSE)
+                                          print = TRUE)
     expect_true(all(noid.out == noid.test))
 })
 

### 2019-12-11 R/clean.R
Fixes get_vars and get_path tests

@@ -142,8 +142,8 @@ get_path <- function(g = "graph",
                        unreachable = FALSE)$order
         out <- as.character(na.omit(names(dfs.result)))
         if (direction == "in"){out <- out[seq(length(out), 1)]}
+        return(out)
     }
-return(out)
 }
 
 ## is_number --- Detect numbers in a character vector of variables.

### 2019-12-11 tests/testthat/test-main.R

@@ -46,6 +46,7 @@ test_that("clean no vars", {
     simple.script <- system.file(
         "example", "simple_script.R", package = "Rclean")
     novars.out <- capture.output(clean(simple.script))
+    expect_true(all(novars.out == novars.test))
 })
 
 test_that("clean get_path g is list mode", {

### 2019-12-11 R/code_graph.R
Removes non script object error from code_graph

@@ -42,8 +42,6 @@ code_graph <- function(script, pdf.file){
         src <- readScript(script[1])
     }else if (class(script) == "Script"){
         src <- script
-    }else{
-        stop("Error: Please provide a Script object or script file path.")
     }
     g <- var_lineage(src)[["g"]]
     ig <- graph_from_adjacency_matrix(g)

### 2020-01-06 R/code_graph.R
Fixes lints in code_graph.R

@@ -21,7 +21,7 @@
 #' Plot the dependencies among functions and objects for a given script.
 #' 
 #'@param script Script object from CodeDepends or a file path to a script.
-#'@param pdf.file Path to output PDF of the code graph.  
+#'@param pdf_file Path to output PDF of the code graph.  
 #'@return A network plot.
 #'@importFrom igraph graph_from_adjacency_matrix
 #'@importFrom igraph igraph.to.graphNEL
@@ -37,19 +37,19 @@
 #' code_graph(simple.script)
 #'}
 
-code_graph <- function(script, pdf.file){
-    if (class(script) == "character"){
+code_graph <- function(script, pdf_file) {
+    if (class(script) == "character") {
         src <- readScript(script[1])
-    }else if (class(script) == "Script"){
+    }else if (class(script) == "Script") {
         src <- script
     }
     g <- var_lineage(src)[["g"]]
     ig <- graph_from_adjacency_matrix(g)
     gNEL <- igraph.to.graphNEL(ig)
-    if (missing(pdf.file)){
+    if (missing(pdf_file)) {
         plot(gNEL)    
-    }else{
-        pdf(pdf.file)
+    } else {
+        pdf(pdf_file)
         plot(gNEL)
         dev.off()
     }

### 2020-01-06 R/keep.R
Fixes lints in keep.R

@@ -48,10 +48,10 @@
 #' }
 
 
-keep <- function(x, file = NULL){
-    if (is.null(file)){
+keep <- function(x, file = NULL) {
+    if (is.null(file)) {
         write_clip(x)
-    }else{
+    } else {
         file.create(file)
         fileConn <- file(file)
         writeLines(x, fileConn)

### 2020-01-06 tests/testthat/test-main.R
Fixes bug in tests from codeGraph variable rename

@@ -189,7 +189,7 @@ test_that("codeGraph as script", {
 test_that("codeGraph write pdf", {
     simple.script <- system.file(
         "example", "simple_script.R", package = "Rclean")
-    code_graph(simple.script, pdf.file = "code_graph_test.pdf")
+    code_graph(simple.script, pdf_file = "code_graph_test.pdf")
     expect_true(file.exists("code_graph_test.pdf"))
     file.remove("code_graph_test.pdf")
 })

### 2020-01-06 R/code_graph.R
Fixes lints in keep and code_graph

@@ -45,12 +45,12 @@ code_graph <- function(script, pdf_file) {
     }
     g <- var_lineage(src)[["g"]]
     ig <- graph_from_adjacency_matrix(g)
-    gNEL <- igraph.to.graphNEL(ig)
+    gn <- igraph.to.graphNEL(ig)
     if (missing(pdf_file)) {
-        plot(gNEL)    
+        plot(gn)    
     } else {
         pdf(pdf_file)
-        plot(gNEL)
+        plot(gn)
         dev.off()
     }
 }

### 2020-01-06 R/keep.R

@@ -53,8 +53,8 @@ keep <- function(x, file = NULL) {
         write_clip(x)
     } else {
         file.create(file)
-        fileConn <- file(file)
-        writeLines(x, fileConn)
-        close(fileConn)
+        file_conn <- file(file)
+        writeLines(x, file_conn)
+        close(file_conn)
     }
 }

### 2020-01-06 inst/example/long_script.R
Fixes paren bracket lints in long_script and test-main

@@ -22,7 +22,7 @@ rownames(x) <- LETTERS[seq_len(nrow(x))]
 x <- t(x)
 x[, "A"] <- sqrt(x[, "A"])
 
-for (i in seq_along(colnames(x))){
+for (i in seq_along(colnames(x))) {
     set.seed(17)
     x[, i] <- x[, i] + runif(length(x[, i]), -1, 1)
 }

### 2020-01-06 tests/testthat/test-main.R

@@ -104,7 +104,7 @@ test_that("clean vars removed simple script", {
     vars <- get_vars(simple.script)
     var.files <- paste0(vars, "_clean.R")
     var.vars <- list()
-    for (i in seq_along(vars)){
+    for (i in seq_along(vars)) {
         var.clean <- clean(simple.script, vars[i])
         keep(var.clean, var.files[i])
         var.env <- new.env()
@@ -113,7 +113,7 @@ test_that("clean vars removed simple script", {
     }
     names(var.vars) <- vars
     var.check <- logical()
-    for (i in seq_along(var.vars)){
+    for (i in seq_along(var.vars)) {
         var.check[i] <- all(
             sort(var.vars[[i]]) == sort(simple.var.vars[[i]])
             )
@@ -129,7 +129,7 @@ test_that("clean vars removed long script", {
     vars <- get_vars(long.script)
     var.files <- paste0(vars, "_clean.R")
     var.vars <- list()
-    for (i in seq_along(vars)){
+    for (i in seq_along(vars)) {
         var.clean <- clean(long.script, vars[i])
         keep(var.clean, var.files[i])
         var.env <- new.env()
@@ -138,7 +138,7 @@ test_that("clean vars removed long script", {
     }
     names(var.vars) <- vars
     var.check <- logical()
-    for (i in seq_along(var.vars)){
+    for (i in seq_along(var.vars)) {
         var.check[i] <- all(
             sort(var.vars[[i]]) == sort(long.var.vars[[i]])
             )

### 2020-01-07 R/keep.R
Hotfix keep.R example quotes non-ASCII

@@ -40,7 +40,7 @@
 #'         "example", 
 #'         "simple_script.R", 
 #'         package = "Rclean")
-#' clean.code <- clean(script, “tab.15”)
+#' clean.code <- clean(script, "tab.15")
 #' ## Copies code to your clipboard
 #' keep(clean.code)
 #' ## Saves code to your disk

### 2020-01-08 joss/paper.Rmd
Adds text on provenance

@@
 ```
+
+The provenance of the results can be seen as terminal nodes. This
+information is based on the static analysis of the script, which
+traces the relationship among code lines from inputs to
+outputs. This is the information that forms the basis of the code reduction
+techinque at the heart of Rclean. Because we can predict what lines of
+code results depend, or more relevantly *don't* depend, allows us to
+predict what code can be removed from a given script. Thus, when we
+know what results we really want, we can rely on the formalized
+provenance to automatically plot a course of "pruning" through the
+script to trim out what we no longer need.
 

### 2020-01-15 joss/paper.Rmd
Edits joss manuscript

--- 2019-12-06 joss/paper.Rmd
@@
 
-The growth of open-source statistical software programming has been
-explosive in the last decade. In particular, the statistical
-programming language ``R`` has grown exponentially to become one of
-the top ten programming languages in use today. Recently, concerns
-have arisen over the reproducibility of scientific research
-[@Peng2011 @Baker2016 @Stodden2018] and the potential issues stemming
-from the complexity and fragility of analytical software
-[@Pasquier2017 @Chen2018]. There is now a recognition that simply
-making the code open is not enough, and that there is a need for
-improvements to documentation and transparency [@Chen2018]. From this
-perspective, tools that can lower the time and energy required to
-re-factor and streamline analytical scripts could have a significant
-impact on scientific reproducibility across all disciplines
-[@Visser2015]. Supporting this objective, we have created ``Rclean``
-which automatically reduces a script to the parts that are
-specifically relevant to a research product (e.g.  a blog, academic
-talk or research article).
+The growth of programming in the sciences has been explosive in the
+last decade. In particular, the statistical programming language ``R``
+has grown exponentially to become one of the top ten programming
+languages in use today. Recently, concerns have arisen over the
+reproducibility of scientific research [@Peng2011 @Baker2016
+@Stodden2018] and the potential issues stemming from the complexity
+and fragility of analytical software [@Pasquier2017 @Chen2018]. There
+is now a recognition that simply making the code open is not enough,
+and that there is a need for improvements to documentation and
+transparency [@Chen2018].
 
-At it's root R is a statistical programming language. That is, it was
+At it's root R is a statistical programming language, that is, it was
 designed for use in analytical workflows. As such, the majority of the
@@
 same users are also frequently frustrated by code that is fragile,
-buggy and complicated enough to quickly become obtuse even to
-themselves in a very short amount of time. In addition, when scripts
-take an extremely long time to execute, being able to reduce
-unnecessary analyses can help increase computation efficiency.
+buggy and complicated enough to quickly become obtuse (even to
+themselves) in a very short amount of time, which leads to frequently
+re-writing code unecessarily. Also, when scripts take an extremely
+long time to execute, reducing unnecessary analyses can increase
+computational efficiency.
 
-More often then not, when someone is writing an R script, they are
-intent on getting a set of results. This set of results is always a
-subset of a much larger set of possible ways to explore a dataset, as
-there are many statistical approaches and tests, let alone ways to
-create visualizations and other representations of patterns in
-data. This commonly leads to lengthy, complicated scripts from which
-researchers manually subset results, but never refactor (i.e. reduce
-to the final subset). In part, this is enabled by a lack of a proper
-version control system, and in order to record their process and not
-lose work, the entire process remains in a single or several
-scripts. Although *Rclean* is not designed to fix the latter, it can
-help with the former issue, once an appropriate versioning system is
-adopted (e.g. git or subversion).
+From this perspective, tools that can lower the time and energy
+required to re-factor and streamline analytical scripts, and otherwise
+help to "clean" code will have a significant impact on scientific
+reproducibility across all disciplines [@Visser2015]. To support this
+objective, we have created ``Rclean`` which automatically reduces a
+script to the parts that are specifically relevant to a research
+product (e.g.  a blog, academic talk or research article). Here, we
+detail the structure of the package's API, describe the general
+workflow illustrated by an example use case and provide some
+background on how the underlying use of data provenance enables the
+package.
 
@@
 
-This process relies on the
-generation of data provenance [@Carata2014], which is a formal
-representation of the execution of a computational process
-(https://www.w3.org/TR/prov-dm/), to rigorously determine the the
-unique computational pathway from inputs to results. However, as the
-intended user is a researcher conducting analyses, the process is
-abstracted and only the minimum information is required and presented
-to the user to streamline the process of creating "cleaner" code. The
-output generated by ``RClean`` is the minimum and sufficient code
-needed to generate the chosen result.
+The main goal of *Rclean* is to provide a means to simplify code. To
+keep the process simple and straight-forward, the API has been kept to
+a minimum set of functions, which enable a user to conduct the basic
+workflow of getting information about the posible results in a script,
+obtaining the minimum code for a set of results and then creating a
+new "cleaned" script or other software (e.g. a function, reproducible
+example, web-app, etc.).
 
-The workhorse behind *Rclean* is data provenance. Here, when we refer
-to provenance we are talking about a formalized representation of the
-computational process that produced some data. Data is used in a broad
-sense, not just data that were collected in a research project. There
-are multiple approaches to collecting data provenance, but *Rclean*
-uses "prospective" provenance, which analyzes code and uses language
-specific information to predict the relationship among processes and
-data objects. *Rclean* relies on a library called *CodeDepends* to
-gather the prospective provenance for each script. For more
-information on the mechanics of the *CodeDepends* package, see
-[@Lang2019]. To get an idea of what data provenance is, take a look at
-the `code_graph` function. The plot that it generates is a graphical
-representation of the prospective provenance generated for *Rclean*.
+The package's main functions are `clean` and `keep`. When provided a
+file path to a script and the name of a result (or a set of results),
+`clean` analyzes the script's code and extracts the lines of code
+required to produce the results. This code can then be passed to the
+`keep` function, which can either write the code to disk or copy the
+code to the user's clipboard (if no ouptput file path is supplied) and
+the user can paste the code into another location (e.g. a script
+editor).
 
-```{R prov-graph}
-
-code_graph(script)
-
-```
-
-## The API
-
-The package's main function is `clean`.
-
-code_graph
-get_libs
-get_vars
-keep
+In the process of cleaning a script, it is likely that a user might
+require some help analyzing the script. There are several functions to
+help. The `get_vars` function will return a list of possible results
+for a given script at a supplied file path. This is obviously an
+important step, and justsifiably, the default behavior of the `clean`
+function is to run `get_vars` if no results are supplied. To help with
+limiting and checking the selection of results, the `code_graph` function
+creates a network graph of the relationships among the various
+results and lines of code in the script. Last, the `get_libs` function
+can be used to detect the packages that a given script depends on,
+which it will return as coded library calls that can be inserted into
+a cleaned script.
 

### 2020-01-15 joss/paper.Rmd
JOSS paper edits

@@
 
+All of these processes rely on the generation of data provenance
+[@Carata2014], which is a formal representation of the execution of a
+computational process (https://www.w3.org/TR/prov-dm/), to rigorously
+determine the the unique computational pathway from inputs to
+results. To avoid confusion, note that "data" in this context is used
+in a broad sense to include all of the information generated during
+computation, not just the data that are collected in a research
+project that are used as input to an analysis. Having the formalized,
+mathematically rigorous representation that data provenance provides
+gaurantees that the analyses that *RClean* conducts are theoretically
+sound. Most importantly, it makes it possible to apply a network
+search algorithm to determine the minimum and sufficient code needed
+to generate the chosen result in the `clean` function.
+
+There are multiple approaches to collecting data provenance, but
+*Rclean* uses "prospective" provenance, which analyzes code and uses
+language specific information to predict the relationship among
+processes and data objects. *Rclean* relies on a library called
+*CodeDepends* to gather the prospective provenance for each
+script. For more information on the mechanics of the *CodeDepends*
+package, see [@Lang2019]. To get an idea of what data provenance is,
+take a look at the `code_graph` function. The plot that it generates
+is a graphical representation of the prospective provenance generated
+for *Rclean*.
+
+```{R prov-graph}
+
+code_graph(script)
+
+```
+
 # Results
@@
 `devtools` library to install directly from the repository
-(https://github.com/MKLau/rclean). The package is open-source and
+(https://github.com/ROpenSci/Rclean). The package is open-source and
 welcomes contributions. Please visit the repository page to report
@@
 
-Although, a lot of great work can be done with type of data
-provenance, there are limitations. Only using prospective provenance
-means that the outcomes of some processes can not be predicted. For
-example, if there is a part of a script that is determined by a random
-number, the current implementation of prospective provenance can not
-predict the path that will be taken through the code. Therefore, the
-code cannot be reduced to exclude the pathway that would not be
-taken. Such limitations can be overcome with other data provenance
-methods. One solution is "retrospective" provenance, which tracks a
-computational process as it is executing. Through this active
-monitoring process, retrospective provenance can gather specific
-information, such as the results relevant to our random number
-example. Using retrospective provenance comes at a cost, however, in
-that in order to gather it, the script needs to be executed. When
-scripts are computationally intensive or contain bugs that stop
-execution, then retrospective provenance can not be obtained for part
-or all of the code. Some work has already been done in the direction
-of implementing retrospective provenance for code cleaning in R (see
-http://end-to-end-provenance.github.io).
+The existing framework could be extended to support new provenance
+capture methods. One possibility is *retrospective provenance*, which
+tracks a computational process as it is executing. Through this
+active, concurrent monitoring, retrospective provenance can gather
+information that static prospective provenance can't. Only using
+prospective provenance means that the outcomes of some processes can
+not be predicted. For example, if there is a part of a script that is
+determined by a random number, the current implementation of
+prospective provenance can not predict the path that will be taken
+through the code. Therefore, the code cannot be reduced to exclude the
+pathway that would not be taken. However, using retrospective provenance comes
+at a cost. In order to gather it, the script needs to
+be executed. When scripts are computationally intensive or contain
+bugs that stop execution, then retrospective provenance can not be
+obtained for part or all of the code. Some work has already been done
+in the direction of implementing retrospective provenance for code
+cleaning in R (see http://end-to-end-provenance.github.io).
 
-For example, the existing framework could be extended to support new
-provenance capture methods, and there is tremendous potential for the
-use of code cleaning in the creation of more robust capsules
-[@Pasquier2018].
+To conclude, we hope that `Rclean` makes writing scientifi software
+easier. We look forward to feedback and help with extending its
+applications, particularly in the area of reproducibility, such as
+using code cleaning in the creation of more robust capsules
+[@Pasquier2018]. To get involved, report bugs, suggest features,
+please visit the project page.
 
@@
 This work was improved by discussions with ecologists at Harvard
-Forest. Much of the work was funded by US National Science Foundation
+Forest and through the helpful review provided by the ROpenSci
+community, particuarly Anna Krystalli, Will Landau and Clemens
+Schmid. Much of the work was funded by US National Science Foundation
 grant SSI-1450277 for applications of End-to-End Data Provenance.

### 2020-01-22 joss/paper.Rmd
Debugs JOSS code snippets and renders paper.md
edits to JOSS intro and discussion

@@
 has grown exponentially to become one of the top ten programming
-languages in use today. Recently, concerns have arisen over the
+languages in use today. Increasingly, concerns have arisen over the
 reproducibility of scientific research [@Peng2011 @Baker2016
 @Stodden2018] and the potential issues stemming from the complexity
-and fragility of analytical software [@Pasquier2017 @Chen2018]. There
-is now a recognition that simply making the code open is not enough,
-and that there is a need for improvements to documentation and
-transparency [@Chen2018].
+and fragility of analytical software [@Pasquier2017]. There is now a
+recognition that simply making the code open is not enough, and that
+there is a need for improvements to documentation and transparency
+[@Pasquier2018].
 
@@
 
+```{R load-script, echo = FALSE, results = "hide"}
+library(CodeDepends)
+script <- system.file(
+    "example", 
+    "simple_script.R", 
+    package = "Rclean")
+script.long <- system.file(
+    "example", 
+    "long_script.R", 
+    package = "Rclean")
+
+```
+
 ```{R prov-graph}
@@
 
-clean(script.long, "fit.sqrt.A")
+clean(script.long, "fit_sqrt_A")
 

### 2020-01-23 joss/paper.Rmd
Edits introduction paragraph segue

@@
 
-From this perspective, tools that can lower the time and energy
-required to re-factor and streamline analytical scripts, and otherwise
-help to "clean" code will have a significant impact on scientific
-reproducibility across all disciplines [@Visser2015]. To support this
-objective, we have created ``Rclean`` which automatically reduces a
-script to the parts that are specifically relevant to a research
-product (e.g.  a blog, academic talk or research article). Here, we
+The stability, reproducibility and re-use of scientific analyses in R
+would be improved by refactoring. From this perspective, tools that
+can lower the time and energy required to re-factor and streamline
+analytical scripts, and otherwise help to "clean" code will have a
+significant impact on scientific reproducibility across all
+disciplines [@Visser2015]. More often then not, when someone is
+writing an R script, the intent to produce a set of results, such as a
+statistical analysis, figure, etc. This set of results is always a
+subset of a much larger set of possible ways to explore a dataset, as
+there are many statistical approaches and tests, let alone ways to
+create visualizations and other representations of patterns in
+data. This commonly leads to lengthy, complicated scripts from which
+researchers manually subset results, but never refactor (i.e. reduce
+to the desired subset). In part, this is driven a desire to record the
+entire scripting/analytical process and not lose work, which is
+alleviated by the use of proper version control systems (e.g. git and
+subversion); however, refactoring will always be a part of the
+analytical process regardless.
+
+To support provide support for easier refactoring in R, we have
+created ``Rclean``. The ``Rclean`` package provides tools to
+automatically reduce a script to the parts that are specifically
+relevant to a research product (e.g.  a scientific report, academic
+talk, research article, etc.). Although potentially useful to all R
+coders, it was designed to ease refactoring for scientists that use R
+but do not have formal training in software engineering. Here, we
 detail the structure of the package's API, describe the general
 workflow illustrated by an example use case and provide some
-background on how the underlying use of data provenance enables the
-package.
+background on how data provenance enables the underlying functionality
+of the package. We then end with a discussion of future applications
+of data provenance in the context of "code cleaning" and the potential
+integration with other software engineering tools for the R community.
 

### 2020-01-28 joss/paper.Rmd
Edits Intro
Edits from kindle to intro

@@
    index: 4
-date: 6 December 2019
+date: 
 bibliography: paper.bib

### 2020-01-28 joss/paper.Rmd
Kindle edits

@@
 The growth of programming in the sciences has been explosive in the
-last decade. In particular, the statistical programming language ``R``
-has grown exponentially to become one of the top ten programming
-languages in use today. Increasingly, concerns have arisen over the
-reproducibility of scientific research [@Peng2011 @Baker2016
-@Stodden2018] and the potential issues stemming from the complexity
-and fragility of analytical software [@Pasquier2017]. There is now a
-recognition that simply making the code open is not enough, and that
-there is a need for improvements to documentation and transparency
-[@Pasquier2018].
+last decade. This has facilitated the rapid advancement of scienqce
+through the agile development of computational tools. However,
+concerns have begun to surface about the reproducibility of scientific
+research in general [@Peng2011 @Baker2016] and the potential issues
+stemming from issues with analytical software [@Pasquier2017
+@Stodden2018]. Specifically, there is a growing recognition across
+disciplines that simply making data and software "available" is not
+enough and that there is a need to improve the transparency and
+stability of scientific software [@Pasquier2018].
 
-At it's root R is a statistical programming language, that is, it was
-designed for use in analytical workflows. As such, the majority of the
-R community is focused on producing code for idiosyncratic projects
-that are results oriented. Also, R's design is intentionally at a
-level that abstracts many aspects of programming that would otherwise
-act as a barrier to entry for many users. This is good in that there
-are many people who use R to their benefit with little to no formal
-training in computer science or software engineering. However, these
-same users are also frequently frustrated by code that is fragile,
-buggy and complicated enough to quickly become obtuse (even to
-themselves) in a very short amount of time, which leads to frequently
-re-writing code unecessarily. Also, when scripts take an extremely
-long time to execute, reducing unnecessary analyses can increase
-computational efficiency.
-
-The stability, reproducibility and re-use of scientific analyses in R
+At the core of the growth of scentific conputation, the ``R``
+statistical programming language has grown exponentially to become one
+of the top ten programming languages in use today. At it's root R is a
+*statistical* programming language. That is, it was designed for use
+in analytical workflows; and the majority of the R community is
+focused on producing code for idiosyncratic projects that are
+*results* oriented. Also, R's design is intentionally at a level that
+abstracts many aspects of programming that would otherwise act as a
+barrier to entry for many users. This is good in that there are many
+people who use R to their benefit with little to no formal training in
+computer science or software engineering, but these same users can
+also be frequently frustrated by code that is fragile, buggy and
+complicated enough to quickly become obtuse even to the authors. The
+stability, reproducibility and re-use of scientific analyses in R
 would be improved by refactoring. From this perspective, tools that
 can lower the time and energy required to re-factor and streamline
-analytical scripts, and otherwise help to "clean" code will have a
-significant impact on scientific reproducibility across all
-disciplines [@Visser2015]. More often then not, when someone is
-writing an R script, the intent to produce a set of results, such as a
-statistical analysis, figure, etc. This set of results is always a
-subset of a much larger set of possible ways to explore a dataset, as
-there are many statistical approaches and tests, let alone ways to
-create visualizations and other representations of patterns in
-data. This commonly leads to lengthy, complicated scripts from which
-researchers manually subset results, but never refactor (i.e. reduce
-to the desired subset). In part, this is driven a desire to record the
-entire scripting/analytical process and not lose work, which is
-alleviated by the use of proper version control systems (e.g. git and
-subversion); however, refactoring will always be a part of the
-analytical process regardless.
+analytical scripts and otherwise help to "clean" code, but abstracted
+enough to be easily accessible, could have a significant impact on
+scientific reproducibility across all disciplines [@Visser2015].
 
-To support provide support for easier refactoring in R, we have
-created ``Rclean``. The ``Rclean`` package provides tools to
-automatically reduce a script to the parts that are specifically
-relevant to a research product (e.g.  a scientific report, academic
-talk, research article, etc.). Although potentially useful to all R
-coders, it was designed to ease refactoring for scientists that use R
-but do not have formal training in software engineering. Here, we
-detail the structure of the package's API, describe the general
-workflow illustrated by an example use case and provide some
-background on how data provenance enables the underlying functionality
-of the package. We then end with a discussion of future applications
-of data provenance in the context of "code cleaning" and the potential
-integration with other software engineering tools for the R community.
+To provide support for easier refactoring in R, we have created
+``Rclean``. The ``Rclean`` package provides tools to automatically
+reduce a script to the parts that are specifically relevant to a
+research product (e.g.  a scientific report, academic talk, research
+article, etc.). Although potentially useful to all R coders, it was
+designed to ease refactoring for scientists that use R but do not have
+formal training in software engineering. Here, we detail the structure
+of the package's API, describe the general workflow illustrated by an
+example use case and provide some background on how data provenance
+enables the underlying functionality of the package. We then end with
+a discussion of future applications of data provenance in the context
+of "code cleaning" and the potential integration with other software
+engineering tools for the R community.
 
@@
 
-The main goal of *Rclean* is to provide a means to simplify code. To
-keep the process simple and straight-forward, the API has been kept to
-a minimum set of functions, which enable a user to conduct the basic
-workflow of getting information about the posible results in a script,
-obtaining the minimum code for a set of results and then creating a
-new "cleaned" script or other software (e.g. a function, reproducible
-example, web-app, etc.).
+More often then not, when someone is writing an R script, the intent
+to produce a set of results, such as a statistical analysis, figure,
+table, etc. This set of results is always a subset of a much larger
+set of possible ways to explore a dataset, as there are many
+statistical approaches and tests, let alone ways to create
+visualizations and other representations of patterns in data. This
+commonly leads to lengthy, complicated scripts from which researchers
+manually subset results, but never refactor, i.e. refine code so that
+it is shorter and focused on a desired product.
+
+The goal of `Rclean` is to provide a set of tools that help someone
+reduce and organize code based on results. The package uses an
+automated technique based on data provenance (details below) to
+analyze existing scripts and provide ways to identify and extract code
+to produce a desired output. To keep the process simple and
+straight-forward much of this process has been abstracted for the
+user, and the API has been kept to a minimum set of functions that
+enable a user to conduct the following basic workflow:
+
+1. Obtain the "cleaned" code for a result(s).
+2. Transfer the code to a new context (e.g. a new script,
+function, reproducible example, web-app, etc.).
+3. Get information about the posible results and repeat as needed.
+
+## The API
 
@@
 require some help analyzing the script. There are several functions to
-help. The `get_vars` function will return a list of possible results
-for a given script at a supplied file path. This is obviously an
-important step, and justsifiably, the default behavior of the `clean`
-function is to run `get_vars` if no results are supplied. To help with
-limiting and checking the selection of results, the `code_graph` function
-creates a network graph of the relationships among the various
-results and lines of code in the script. Last, the `get_libs` function
-can be used to detect the packages that a given script depends on,
-which it will return as coded library calls that can be inserted into
-a cleaned script.
+help with this process. The `get_vars` function will return a list of
+possible results for a given script at a supplied file path. This is
+obviously an important step, and justsifiably, the default behavior of
+the `clean` function is to run `get_vars` if no results are
+supplied. To help with limiting and checking the selection of results,
+the `code_graph` function creates a network graph of the relationships
+among the various results and lines of code in the script. Last, the
+`get_libs` function can be used to detect the packages that a given
+script depends on, which it will return as coded library calls that
+can be inserted into a cleaned script.
 
-All of these processes rely on the generation of data provenance
-[@Carata2014], which is a formal representation of the execution of a
-computational process (https://www.w3.org/TR/prov-dm/), to rigorously
-determine the the unique computational pathway from inputs to
-results. To avoid confusion, note that "data" in this context is used
-in a broad sense to include all of the information generated during
-computation, not just the data that are collected in a research
-project that are used as input to an analysis. Having the formalized,
-mathematically rigorous representation that data provenance provides
-gaurantees that the analyses that *RClean* conducts are theoretically
-sound. Most importantly, it makes it possible to apply a network
-search algorithm to determine the minimum and sufficient code needed
-to generate the chosen result in the `clean` function.
+## Data Provenance
+
+All of these processes rely on the generation of data provenance.  The
+term provenance means information about the origins of some
+object. Data provenanve is a formal representation of the execution of
+a computational process (https://www.w3.org/TR/prov-dm/), to
+rigorously determine the the unique computational pathway from inputs
+to results [@Carata2014]. To avoid confusion, note that "data" in this
+context is used in a broad sense to include all of the information
+generated during computation, not just the data that are collected in
+a research project that are used as input to an analysis. Having the
+formalized, mathematically rigorous representation that data
+provenance provides gaurantees that the analyses that *RClean*
+conducts are theoretically sound. Most importantly, because the
+relationships defined by the provenance can be represented as a graph,
+it is possible to apply network search algorithms to determine the
+minimum and sufficient code needed to generate the chosen result in
+the `clean` function.
 
 There are multiple approaches to collecting data provenance, but
-*Rclean* uses "prospective" provenance, which analyzes code and uses
+`Rclean` uses "prospective" provenance, which analyzes code and uses
 language specific information to predict the relationship among
-processes and data objects. *Rclean* relies on a library called
-*CodeDepends* to gather the prospective provenance for each
-script. For more information on the mechanics of the *CodeDepends*
+processes and data objects. `Rclean` relies on a library called
+`CodeDepends` to gather the prospective provenance for each
+script. For more information on the mechanics of the `CodeDepends`
 package, see [@Lang2019]. To get an idea of what data provenance is,
@@
 is a graphical representation of the prospective provenance generated
-for *Rclean*.
+for `Rclean`.
 
@@
 
-```{R prov-graph}
+	```{R prov-graph, fig.cap = "Network diagram of the prospective data provenance generated for an example script. Arrows indicate relationships among objects and lines of code (numbered)."}
 
@@
 in the script. Instead, we can easily do this automatically with
-*Rclean*.
+`Rclean`.
 
@@
 
-As you can see, *Rclean* has picked through the tangled bits of code
+As you can see, `Rclean` has picked through the tangled bits of code
 and found the minimal set of lines relevant to our object of

### 2020-01-28 joss/paper.Rmd
Edits
Renames script.long to script

@@
     package = "Rclean")
-
+script <- script.long
 ```
@@
 
-readLines(script.long)
+readLines(script)
 
@@
 
-clean(script.long, "fit_sqrt_A")
+clean(script, "fit_sqrt_A")
 

### 2020-01-28 joss/paper.Rmd
Edits to make simple script the prov example

@@
 library(CodeDepends)
+library(Rclean)
+```
+
+```{R prov-graph, fig.cap = "Network diagram of the prospective data provenance generated for an example script. Arrows indicate relationships among objects and lines of code (numbered)."}
+
 script <- system.file(
@@
     package = "Rclean")
-script.long <- system.file(
-    "example", 
-    "long_script.R", 
-    package = "Rclean")
-script <- script.long
-```
-
-```{R prov-graph, fig.cap = "Network diagram of the prospective data provenance generated for an example script. Arrows indicate relationships among objects and lines of code (numbered)."}
-
 code_graph(script)
@@
 
-```{R long-setup, echo = FALSE, eval = TRUE}
+```{R long-setup, echo = FALSE, eval = TRUE, results = "hide"}
+
+script.long <- system.file(
+    "example", 
+    "long_script.R", 
+    package = "Rclean")
+script <- script.long
+```
+
+```{R long-script, echo = FALSE, eval = TRUE}
 

### 2020-01-28 joss/paper.Rmd
Edits discussion

@@
 
+Relatedly, it is important to briefly point out that `Rclean` *does
+not* keep comments present in code. This could be seen as a limitation
+of the data provenance, which currently does not assign them a
+relationships. Therefore, although there is often very useful or even
+invaluable information in comments, the `clean` function removes
+them. This is a general issue with automated methods for detecting the
+relationships between comments and the code itself. Comments at the
+end of lines are typically relevant to the line they are on, but this
+is not a requirement and could refer to other lines. Also, comments
+occupying their own lines usually refer to the following lines, but
+this is also not necessarily the case. As `clean` depends on the
+unambiguous determination of relationships in the production of
+results, it cannot operate automatically on comments. However,
+comments in the original code remain untouched and can be used to
+inform the reduced code. Also, as the `clean` function is oriented
+toward isolating code based on a specific result, the resulting code
+tends to naturally support the generation of new comments that are
+higher level (e.g. "The following produces a plot of the mean response
+of each treatment group."), and lower level comments are not necessary
+because the code is simpler and clearer.
+
 # Results
@@
 multiple concepts at the same time. What did I measure? What analyses
-are relevant to them? Do I need to transform the data? How do I go
-about managing the data given how they were entered? What's the code
+are relevant to them? Do I need to transform the data? What's the code
 for the analysis I want to run? And so on. Data analysis can be messy
-and complicated, so it's no wonder that code reflects this. And this
-is a reason why having a way to isolate code based on variables can be
-valuable. The following is an example of a script that has some
+and complicated, so it's no wonder that the code often reflects
+this. This is why having a way to isolate code based on variables can
+be valuable. The following is an example of a script that has some
 complications. As you can see, although the script is not extremely
-long, it's long enough to make it frustrating to visualize it in its
-entirety and pick through it.
+long or complicated, it's difficult enough to make it frustrating to
+visualize it in its entirety and pick through it.
 
@@
 
+```{R ex-keep}
+
+```
+
+```{R ex-get_vars}
+
+```
+
+```{R ex-code_graph}
+
+```
+
+```{R ex-get_libs}
+
+```
+
 ## Software Availability
@@
 
-The ``Rclean`` package provides a simple, easy to use tool for
-scientists conducting analyses in the R programming language. Using
-graph analytic algorithms, ``Rclean`` isolates the code necessary to
-produce a specified result (e.g., an object stored in memory or a
-table or figure written to disk). As statistical programming becomes
+We have created ``Rclean`` to provide a simple, easy to use tool for
+scientists who would like help refactoring their code. Using
+``Rclean`` the code necessary to produce a specified result (e.g., an
+object stored in memory or a table or figure written to disk) can be
+easily isolated even when tangled with code for other results. This
+functionality is enabled by graph analysis of data provenance
+collected from the user's script. As statistical programming becomes
 more common across the sciences, tools that make the production of
 accessible code will be an important aid for improving scientific
-reproducibility. ``Rclean`` has been designed to take advantage of
-recent advances in data provenance capture techniques to create a
-minimal tool for this purpose.
+reproducibility.
 
-It is worth mentioning and discussing that `Rclean` does not keep
-comments present in code. Although, there is often very useful or even
-invaluable information in comments, the `clean` function removes
-comments. This is primarily due to the lack of a mathematically formal
-method for determining their relationship to the code itself. Comments
-at the end of lines are typically relevant to the line they are on,
-but this is not explicitly required. Also, comments occupying their
-own lines usually refer to the following lines, but this is also not
-necessarily the case. As `clean` depends on the unambiguous
-determination of relationships in the production of results, it cannot
-operate automatically on comments. However, comments in the original
-code remain untouched and can be used to inform the reduced
-code. Also, as the `clean` function is oriented toward isolating code
-based on a specific result, the resulting code tends to naturally
-support the generation of new comments that are higher level
-(e.g. "The following produces a plot of the mean response of each
-treatment group."), and lower level comments are not necessary because
-the code is simpler and clearer.
+Potential to integrate with a larger context of producing reproducible
+projects.
 
-The existing framework could be extended to support new provenance
-capture methods. One possibility is *retrospective provenance*, which
-tracks a computational process as it is executing. Through this
-active, concurrent monitoring, retrospective provenance can gather
-information that static prospective provenance can't. Only using
-prospective provenance means that the outcomes of some processes can
-not be predicted. For example, if there is a part of a script that is
-determined by a random number, the current implementation of
-prospective provenance can not predict the path that will be taken
-through the code. Therefore, the code cannot be reduced to exclude the
-pathway that would not be taken. However, using retrospective provenance comes
-at a cost. In order to gather it, the script needs to
-be executed. When scripts are computationally intensive or contain
-bugs that stop execution, then retrospective provenance can not be
-obtained for part or all of the code. Some work has already been done
-in the direction of implementing retrospective provenance for code
-cleaning in R (see http://end-to-end-provenance.github.io).
+- style = styler, formatr
+- naming = lintr, goodpractice
+- workflow = drake
+- libraries = trackr, rrtools, packrat
+- reproducible examples = reprex
+- data = pins
 
-To conclude, we hope that `Rclean` makes writing scientifi software
+Also, future work could extend the existing framework to support new
+and different provenance capture methods. One possibility is
+*retrospective provenance*, which tracks a computational process as it
+is executing. Through this active, concurrent monitoring,
+retrospective provenance can gather information that static
+prospective provenance can't. Only using prospective provenance means
+that the outcomes of some processes can not be predicted. For example,
+if there is a part of a script that is determined by a random number,
+the current implementation of prospective provenance can not predict
+the path that will be taken through the code. Therefore, the code
+cannot be reduced to exclude the pathway that would not be
+taken. However, using retrospective provenance comes at a cost. In
+order to gather it, the script needs to be executed. When scripts are
+computationally intensive or contain bugs that stop execution, then
+retrospective provenance can not be obtained for part or all of the
+code. Some work has already been done in the direction of implementing
+retrospective provenance for code cleaning in R (see
+http://end-to-end-provenance.github.io).
+
+To conclude, we hope that `Rclean` makes writing scientific software
 easier. We look forward to feedback and help with extending its

### 2020-02-04 joss/paper.Rmd
spell check

@@
 The growth of programming in the sciences has been explosive in the
-last decade. This has facilitated the rapid advancement of scienqce
+last decade. This has facilitated the rapid advancement of science
 through the agile development of computational tools. However,
@@
 
-At the core of the growth of scentific conputation, the ``R``
+At the core of the growth of scientific computation, the ``R``
 statistical programming language has grown exponentially to become one
@@
 function, reproducible example, web-app, etc.).
-3. Get information about the posible results and repeat as needed.
+3. Get information about the possible results and repeat as needed.
 
@@
 `keep` function, which can either write the code to disk or copy the
-code to the user's clipboard (if no ouptput file path is supplied) and
+code to the user's clipboard (if no output file path is supplied) and
 the user can paste the code into another location (e.g. a script
@@
 possible results for a given script at a supplied file path. This is
-obviously an important step, and justsifiably, the default behavior of
+obviously an important step, and justifiably, the default behavior of
 the `clean` function is to run `get_vars` if no results are
@@
 term provenance means information about the origins of some
-object. Data provenanve is a formal representation of the execution of
+object. Data provenance is a formal representation of the execution of
 a computational process (https://www.w3.org/TR/prov-dm/), to
@@
 formalized, mathematically rigorous representation that data
-provenance provides gaurantees that the analyses that *RClean*
+provenance provides guarantees that the analyses that *RClean*
 conducts are theoretically sound. Most importantly, because the
@@
 Forest and through the helpful review provided by the ROpenSci
-community, particuarly Anna Krystalli, Will Landau and Clemens
+community, particularly Anna Krystalli, Will Landau and Clemens
 Schmid. Much of the work was funded by US National Science Foundation

### 2020-02-04 joss/paper.Rmd
edits and spell check

@@
 stability, reproducibility and re-use of scientific analyses in R
-would be improved by refactoring. From this perspective, tools that
-can lower the time and energy required to re-factor and streamline
-analytical scripts and otherwise help to "clean" code, but abstracted
-enough to be easily accessible, could have a significant impact on
-scientific reproducibility across all disciplines [@Visser2015].
+would be improved by refactoring, which is a common practice in
+software engineering [@Martin2009]. From this perspective, tools that
+can lower the time and energy required to refactor analytical scripts
+and otherwise help to "clean" code, but abstracted enough to be easily
+accessible, could have a significant impact on scientific
+reproducibility across all disciplines [@Visser2015].
 
@@
 
-In the process of cleaning a script, it is likely that a user might
-require some help analyzing the script. There are several functions to
-help with this process. The `get_vars` function will return a list of
-possible results for a given script at a supplied file path. This is
-obviously an important step, and justifiably, the default behavior of
-the `clean` function is to run `get_vars` if no results are
-supplied. To help with limiting and checking the selection of results,
-the `code_graph` function creates a network graph of the relationships
-among the various results and lines of code in the script. Last, the
-`get_libs` function can be used to detect the packages that a given
-script depends on, which it will return as coded library calls that
-can be inserted into a cleaned script.
+In the process of cleaning a script, it is likely that a user will not
+know the precise objects they want and might require some help
+analyzing it. There are several functions to help with this
+process. The `get_vars` function will return a list of possible
+results for a given script at a supplied file path. This is obviously
+an important step, and justifiably, the default behavior of the
+`clean` function is to run `get_vars` if no results are supplied. To
+help with limiting and checking the selection of results, the
+`code_graph` function creates a network graph of the relationships
+among the various results and lines of code in the script, which is
+the function used to create the figure demonstrating data provenance
+\ref{prov-graph}. Last, the `get_libs` function can be used to detect
+the packages that a given script depends on, which it will return as
+coded library calls that can be inserted into a cleaned script.
 
@@
 formalized, mathematically rigorous representation that data
-provenance provides guarantees that the analyses that *RClean*
+provenance provides guarantees that the analyses that `Rclean`
 conducts are theoretically sound. Most importantly, because the
@@
 is a graphical representation of the prospective provenance generated
-for `Rclean`.
+for `Rclean` \ref{prov-graph}.
 
@@
 
-```{R prov-graph, fig.cap = "Network diagram of the prospective data provenance generated for an example script. Arrows indicate relationships among objects and lines of code (numbered)."}
+```{R prov-graph, fig.cap = "Network diagram of the prospective data
+provenance generated for an example script. Arrows indicate
+which lines of code (numbered) produced which objects (named).", echo = FALSE}
 
@@
 
-Relatedly, it is important to briefly point out that `Rclean` *does
-not* keep comments present in code. This could be seen as a limitation
-of the data provenance, which currently does not assign them a
+Relatedly, it is important to point out that `Rclean` *does not* keep
+comments present in code. This could be seen as a limitation of the
+data provenance, which currently does not assign them a
 relationships. Therefore, although there is often very useful or even
@@
 
-Conducting analyses is challenging in that it requires thinking about
-multiple concepts at the same time. What did I measure? What analyses
-are relevant to them? Do I need to transform the data? What's the code
-for the analysis I want to run? And so on. Data analysis can be messy
-and complicated, so it's no wonder that the code often reflects
-this. This is why having a way to isolate code based on variables can
-be valuable. The following is an example of a script that has some
-complications. As you can see, although the script is not extremely
-long or complicated, it's difficult enough to make it frustrating to
-visualize it in its entirety and pick through it.
+Data analysis can be messy and complicated, so it's no wonder that the
+code often reflects this. "What did I measure? What analyses are
+relevant to them? Do I need to transform the data? What's the function
+for the analysis I want to run?" This is why having a way to isolate
+code based on variables can be valuable. The following is an example
+of a script that has some complications. As you can see, although the
+script is not extremely long or complicated, it's difficult enough to
+make it frustrating to visualize it in its entirety and pick through
+it.
 
@@
 results, we also want to use the code again for another purpose, such
-as creating a plot of the patterns supported by the test.
-
-Manually tracing through our code for all the variables used in the
-test and finding all of the lines that were used to prepare them for
-the analysis would be annoying and difficult, especially given the
-fact that we have used "x" as a prefix for multiple unrelated objects
-in the script. Instead, we can easily do this automatically with
+as creating a plot of the patterns supported by the test. Manually
+tracing through our code for all the variables used in the test and
+finding all of the lines that were used to prepare them for the
+analysis would be annoying and difficult, especially given the fact
+that we have used "x" as a prefix for multiple unrelated objects in
+the script. Instead, we can easily do this automatically with
 `Rclean`.
@@
 We have created ``Rclean`` to provide a simple, easy to use tool for
-scientists who would like help refactoring their code. Using
-``Rclean`` the code necessary to produce a specified result (e.g., an
-object stored in memory or a table or figure written to disk) can be
-easily isolated even when tangled with code for other results. This
-functionality is enabled by graph analysis of data provenance
-collected from the user's script. As statistical programming becomes
-more common across the sciences, tools that make the production of
+scientists who would like help refactoring code. Using ``Rclean`` the
+code necessary to produce a specified result (e.g., an object stored
+in memory or a table or figure written to disk) can be easily and
+*reliably* isolated even when tangled with code for other
+results. This functionality is enabled by graph analysis of data
+provenance collected from the user's script. This is likely to be a
+broadly useful tool as statistical programming becomes more common
+across the sciences. Tools, such as this, that make the production of
 accessible code will be an important aid for improving scientific
@@
 
-Also, future work could extend the existing framework to support new
-and different provenance capture methods. One possibility is
-*retrospective provenance*, which tracks a computational process as it
-is executing. Through this active, concurrent monitoring,
-retrospective provenance can gather information that static
-prospective provenance can't. Only using prospective provenance means
-that the outcomes of some processes can not be predicted. For example,
-if there is a part of a script that is determined by a random number,
-the current implementation of prospective provenance can not predict
-the path that will be taken through the code. Therefore, the code
-cannot be reduced to exclude the pathway that would not be
-taken. However, using retrospective provenance comes at a cost. In
-order to gather it, the script needs to be executed. When scripts are
-computationally intensive or contain bugs that stop execution, then
-retrospective provenance can not be obtained for part or all of the
-code. Some work has already been done in the direction of implementing
-retrospective provenance for code cleaning in R (see
-http://end-to-end-provenance.github.io).
+Another possible future direction could extend the existing framework
+to support new and different provenance capture methods. One
+possibility is *retrospective provenance*, which tracks a
+computational process as it is executing. Through this active,
+concurrent monitoring, retrospective provenance can gather information
+that static prospective provenance can't. Only using prospective
+provenance means that the outcomes of some processes can not be
+predicted. For example, if there is a part of a script that is
+determined by a random number, the current implementation of
+prospective provenance can not predict the path that will be taken
+through the code. Therefore, the code cannot be reduced to exclude the
+pathway that would not be taken. However, using retrospective
+provenance comes at a cost. In order to gather it, the script needs to
+be executed. When scripts are computationally intensive or contain
+bugs that stop execution, then retrospective provenance can not be
+obtained for part or all of the code. Some work has already been done
+in the direction of implementing retrospective provenance for code
+cleaning in R (see http://end-to-end-provenance.github.io).
 

### 2020-02-04 joss/paper.Rmd
moves prov disc para to methods and adds future directions

@@
 `clean` analyzes the script's code and extracts the lines of code
-required to produce the results. This code can then be passed to the
-`keep` function, which can either write the code to disk or copy the
-code to the user's clipboard (if no output file path is supplied) and
-the user can paste the code into another location (e.g. a script
-editor).
+required to produce the results. By default, code is formatted
+following general best practices recommended by the Tidyverse via the
+`styler` package. This code can then be passed to the `keep` function,
+which can either write the code to disk or copy the code to the user's
+clipboard (if no output file path is supplied) and the user can paste
+the code into another location (e.g. a script editor).
 
@@
 because the code is simpler and clearer.
+
+In the future, it would also be useful to extend the existing
+framework to support other provenance methods. One such possibility is
+*retrospective provenance*, which tracks a computational process as it
+is executing. Through this active, concurrent monitoring,
+retrospective provenance can gather information that static
+prospective provenance can't. Greater details of the computational
+process would enable other features that could address some
+challenges, such as processing information from comments, parsing
+control statements and replicating random processes. However, using
+retrospective provenance comes at a cost. In order to gather it, the
+script needs to be executed. When scripts are computationally
+intensive or contain bugs that stop execution, then retrospective
+provenance can not be obtained for part or all of the code. Some work
+has already been done in the direction of implementing retrospective
+provenance for code cleaning in R (see http://end-to-end-provenance.github.io).
 
@@
 broadly useful tool as statistical programming becomes more common
-across the sciences. Tools, such as this, that make the production of
-accessible code will be an important aid for improving scientific
-reproducibility.
+across the sciences. Tools, such as this, that make it easier to
+produce transparent, accessible code will be an important aid for
+improving scientific reproducibility.
 
-Potential to integrate with a larger context of producing reproducible
-projects.
-
-- style = styler, formatr
-- naming = lintr, goodpractice
-- workflow = drake
-- libraries = trackr, rrtools, packrat
-- reproducible examples = reprex
-- data = pins
-
-Another possible future direction could extend the existing framework
-to support new and different provenance capture methods. One
-possibility is *retrospective provenance*, which tracks a
-computational process as it is executing. Through this active,
-concurrent monitoring, retrospective provenance can gather information
-that static prospective provenance can't. Only using prospective
-provenance means that the outcomes of some processes can not be
-predicted. For example, if there is a part of a script that is
-determined by a random number, the current implementation of
-prospective provenance can not predict the path that will be taken
-through the code. Therefore, the code cannot be reduced to exclude the
-pathway that would not be taken. However, using retrospective
-provenance comes at a cost. In order to gather it, the script needs to
-be executed. When scripts are computationally intensive or contain
-bugs that stop execution, then retrospective provenance can not be
-obtained for part or all of the code. Some work has already been done
-in the direction of implementing retrospective provenance for code
-cleaning in R (see http://end-to-end-provenance.github.io).
+Although the workflow described is impactful, we see promise in
+extending it to interface with other clean code and reproducibility
+tools. One example is the `reprex` package, which provides a simple
+API for sharing reproducible examples. Another possibility is to help
+transtion scripts to function, package and workflow creation and
+refactoring via toolboxes like `drake`. `Rclean` could provide a
+reliable way to extract parts of a larger script that would be piped
+to a simplified reproducible example, in the case of `reprex`, or,
+since it can isolate the code from inputs to one or more outputs, be
+used to extract all of the components needed to write one or more
+functions that would be a part of a package or workflow, as is the
+goal of `drake`.
 

### 2020-02-04 joss/paper.Rmd
Removes library and data package discussion

@@
 To conclude, we hope that `Rclean` makes writing scientific software
-easier. We look forward to feedback and help with extending its
-applications, particularly in the area of reproducibility, such as
-using code cleaning in the creation of more robust capsules
-[@Pasquier2018]. To get involved, report bugs, suggest features,
-please visit the project page.
+easier for the R community. We look forward to feedback and help with
+extending its application, particularly in the area of
+reproducibility, such as using code cleaning in the creation of more
+robust capsules [@Pasquier2018]. To get involved, report bugs, suggest
+features, please visit the project page.
 

### 2020-02-04 joss/paper.tex
Spellcheck

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Rclean: A Tool for Writing Cleaner, More Transparent Code},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\ImportTok}[1]{{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{{#1}}}}
\newcommand{\BuiltInTok}[1]{{#1}}
\newcommand{\ExtensionTok}[1]{{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\title{Rclean: A Tool for Writing Cleaner, More Transparent Code}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\section{Introduction}\label{introduction}

The growth of programming in the sciences has been explosive in the last
decade. This has facilitated the rapid advancement of science through
the agile development of computational tools. However, concerns have
begun to surface about the reproducibility of scientific research in
general (R. D. Peng et al. 2011 Baker (2016)) and the potential issues
stemming from issues with analytical software (Pasquier et al. 2017
Stodden, Seiler, and Ma (2018)). Specifically, there is a growing
recognition across disciplines that simply making data and software
``available'' is not enough and that there is a need to improve the
transparency and stability of scientific software (Pasquier et al.
2018).

At the core of the growth of scientific computation, the \texttt{R}
statistical programming language has grown exponentially to become one
of the top ten programming languages in use today. At it's root R is a
\emph{statistical} programming language. That is, it was designed for
use in analytical workflows; and the majority of the R community is
focused on producing code for idiosyncratic projects that are
\emph{results} oriented. Also, R's design is intentionally at a level
that abstracts many aspects of programming that would otherwise act as a
barrier to entry for many users. This is good in that there are many
people who use R to their benefit with little to no formal training in
computer science or software engineering, but these same users can also
be frequently frustrated by code that is fragile, buggy and complicated
enough to quickly become obtuse even to the authors. The stability,
reproducibility and re-use of scientific analyses in R would be improved
by refactoring, which is a common practice in software engineering
({\textbf{???}}). From this perspective, tools that can lower the time
and energy required to refactor analytical scripts and otherwise help to
``clean'' code, but abstracted enough to be easily accessible, could
have a significant impact on scientific reproducibility across all
disciplines (Visser et al. 2015).

To provide support for easier refactoring in R, we have created
\texttt{Rclean}. The \texttt{Rclean} package provides tools to
automatically reduce a script to the parts that are specifically
relevant to a research product (e.g. a scientific report, academic talk,
research article, etc.). Although potentially useful to all R coders, it
was designed to ease refactoring for scientists that use R but do not
have formal training in software engineering. Here, we detail the
structure of the package's API, describe the general workflow
illustrated by an example use case and provide some background on how
data provenance enables the underlying functionality of the package. We
then end with a discussion of future applications of data provenance in
the context of ``code cleaning'' and the potential integration with
other software engineering tools for the R community.

\section{Methods}\label{methods}

More often then not, when someone is writing an R script, the intent to
produce a set of results, such as a statistical analysis, figure, table,
etc. This set of results is always a subset of a much larger set of
possible ways to explore a dataset, as there are many statistical
approaches and tests, let alone ways to create visualizations and other
representations of patterns in data. This commonly leads to lengthy,
complicated scripts from which researchers manually subset results, but
never refactor, i.e.~refine code so that it is shorter and focused on a
desired product.

The goal of \texttt{Rclean} is to provide a set of tools that help
someone reduce and organize code based on results. The package uses an
automated technique based on data provenance (details below) to analyze
existing scripts and provide ways to identify and extract code to
produce a desired output. To keep the process simple and
straight-forward much of this process has been abstracted for the user,
and the API has been kept to a minimum set of functions that enable a
user to conduct the following basic workflow:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Obtain the ``cleaned'' code for a result(s).
\item
  Transfer the code to a new context (e.g.~a new script, function,
  reproducible example, web-app, etc.).
\item
  Get information about the possible results and repeat as needed.
\end{enumerate}

\subsection{The API}\label{the-api}

The package's main functions are \texttt{clean} and \texttt{keep}. When
provided a file path to a script and the name of a result (or a set of
results), \texttt{clean} analyzes the script's code and extracts the
lines of code required to produce the results. By default, code is
formatted following general best practices recommended by the Tidyverse
via the \texttt{styler} package. This code can then be passed to the
\texttt{keep} function, which can either write the code to disk or copy
the code to the user's clipboard (if no output file path is supplied)
and the user can paste the code into another location (e.g.~a script
editor).

In the process of cleaning a script, it is likely that a user will not
know the precise objects they want and might require some help analyzing
it. There are several functions to help with this process. The
\texttt{get\_vars} function will return a list of possible results for a
given script at a supplied file path. This is obviously an important
step, and justifiably, the default behavior of the \texttt{clean}
function is to run \texttt{get\_vars} if no results are supplied. To
help with limiting and checking the selection of results, the
\texttt{code\_graph} function creates a network graph of the
relationships among the various results and lines of code in the script,
which is the function used to create the figure demonstrating data
provenance \ref{prov-graph}. Last, the \texttt{get\_libs} function can
be used to detect the packages that a given script depends on, which it
will return as coded library calls that can be inserted into a cleaned
script.

\subsection{Data Provenance}\label{data-provenance}

All of these processes rely on the generation of data provenance. The
term provenance means information about the origins of some object. Data
provenance is a formal representation of the execution of a
computational process (\url{https://www.w3.org/TR/prov-dm/}), to
rigorously determine the the unique computational pathway from inputs to
results (Carata et al. 2014). To avoid confusion, note that ``data'' in
this context is used in a broad sense to include all of the information
generated during computation, not just the data that are collected in a
research project that are used as input to an analysis. Having the
formalized, mathematically rigorous representation that data provenance
provides guarantees that the analyses that \texttt{Rclean} conducts are
theoretically sound. Most importantly, because the relationships defined
by the provenance can be represented as a graph, it is possible to apply
network search algorithms to determine the minimum and sufficient code
needed to generate the chosen result in the \texttt{clean} function.

There are multiple approaches to collecting data provenance, but
\texttt{Rclean} uses ``prospective'' provenance, which analyzes code and
uses language specific information to predict the relationship among
processes and data objects. \texttt{Rclean} relies on a library called
\texttt{CodeDepends} to gather the prospective provenance for each
script. For more information on the mechanics of the
\texttt{CodeDepends} package, see ({\textbf{???}}). To get an idea of
what data provenance is, take a look at the \texttt{code\_graph}
function. The plot that it generates is a graphical representation of
the prospective provenance generated for \texttt{Rclean}
\ref{prov-graph}.

```\{R prov-graph, fig.cap = ``Network diagram of the prospective data
provenance generated for an example script. Arrows indicate which lines
of code (numbered) produced which objects (named).'', echo = FALSE\}

script \textless{}- system.file( ``example'', ``simple\_script.R'',
package = ``Rclean'') code\_graph(script)

\begin{verbatim}

Relatedly, it is important to point out that `Rclean` *does not* keep
comments present in code. This could be seen as a limitation of the
data provenance, which currently does not assign them a
relationships. Therefore, although there is often very useful or even
invaluable information in comments, the `clean` function removes
them. This is a general issue with automated methods for detecting the
relationships between comments and the code itself. Comments at the
end of lines are typically relevant to the line they are on, but this
is not a requirement and could refer to other lines. Also, comments
occupying their own lines usually refer to the following lines, but
this is also not necessarily the case. As `clean` depends on the
unambiguous determination of relationships in the production of
results, it cannot operate automatically on comments. However,
comments in the original code remain untouched and can be used to
inform the reduced code. Also, as the `clean` function is oriented
toward isolating code based on a specific result, the resulting code
tends to naturally support the generation of new comments that are
higher level (e.g. "The following produces a plot of the mean response
of each treatment group."), and lower level comments are not necessary
because the code is simpler and clearer.

In the future, it would also be useful to extend the existing
framework to support other provenance methods. One such possibility is
*retrospective provenance*, which tracks a computational process as it
is executing. Through this active, concurrent monitoring,
retrospective provenance can gather information that static
prospective provenance can't. Greater details of the computational
process would enable other features that could address some
challenges, such as processing information from comments, parsing
control statements and replicating random processes. However, using
retrospective provenance comes at a cost. In order to gather it, the
script needs to be executed. When scripts are computationally
intensive or contain bugs that stop execution, then retrospective
provenance can not be obtained for part or all of the code. Some work
has already been done in the direction of implementing retrospective
provenance for code cleaning in R (see http://end-to-end-provenance.github.io).

# Results

## Example

Data analysis can be messy and complicated, so it's no wonder that the
code often reflects this. "What did I measure? What analyses are
relevant to them? Do I need to transform the data? What's the function
for the analysis I want to run?" This is why having a way to isolate
code based on variables can be valuable. The following is an example
of a script that has some complications. As you can see, although the
script is not extremely long or complicated, it's difficult enough to
make it frustrating to visualize it in its entirety and pick through
it.

\end{verbatim}

\subsection{\texorpdfstring{{[}1{]}
``library(stats)''}{{[}1{]} library(stats)}}\label{librarystats}

\subsection{\texorpdfstring{{[}2{]} ``x \textless{}-
1:100''}{{[}2{]} x \textless{}- 1:100}}\label{x---1100}

\subsection{\texorpdfstring{{[}3{]} ``x \textless{}-
log(x)''}{{[}3{]} x \textless{}- log(x)}}\label{x---logx}

\subsection{\texorpdfstring{{[}4{]} ``x \textless{}- x *
2''}{{[}4{]} x \textless{}- x * 2}}\label{x---x-2}

\subsection{\texorpdfstring{{[}5{]} ``x \textless{}- lapply(x, rep,
times =
4)''}{{[}5{]} x \textless{}- lapply(x, rep, times = 4)}}\label{x---lapplyx-rep-times-4}

\subsection{\texorpdfstring{{[}6{]} ``\#\#\# This is a note that I made
for
myself.''}{{[}6{]} \#\#\# This is a note that I made for myself.}}\label{this-is-a-note-that-i-made-for-myself.}

\subsection{\texorpdfstring{{[}7{]} ``\#\#\# Next time, make sure to use
a different
analysis.''}{{[}7{]} \#\#\# Next time, make sure to use a different analysis.}}\label{next-time-make-sure-to-use-a-different-analysis.}

\subsection{\texorpdfstring{{[}8{]} ``\#\#\# Also, check with someone
about how to run some other
analysis.''}{{[}8{]} \#\#\# Also, check with someone about how to run some other analysis.}}\label{also-check-with-someone-about-how-to-run-some-other-analysis.}

\subsection{\texorpdfstring{{[}9{]} ``x \textless{}- do.call(cbind,
x)''}{{[}9{]} x \textless{}- do.call(cbind, x)}}\label{x---do.callcbind-x}

\subsection{\texorpdfstring{{[}10{]} ``''}{{[}10{]} }}\label{section}

\subsection{\texorpdfstring{{[}11{]} ``\#\#\# Now I'm going to create a
different
variable.''}{{[}11{]} \#\#\# Now I'm going to create a different variable.}}\label{now-im-going-to-create-a-different-variable.}

\subsection{\texorpdfstring{{[}12{]} ``\#\#\# This is the best variable
the world has ever
seen.''}{{[}12{]} \#\#\# This is the best variable the world has ever seen.}}\label{this-is-the-best-variable-the-world-has-ever-seen.}

\subsection{\texorpdfstring{{[}13{]} ``''}{{[}13{]} }}\label{section-1}

\subsection{\texorpdfstring{{[}14{]} ``x2 \textless{}- sample(10:1000,
100)''}{{[}14{]} x2 \textless{}- sample(10:1000, 100)}}\label{x2---sample101000-100}

\subsection{\texorpdfstring{{[}15{]} ``x2 \textless{}- lapply(x2,
rnorm)''}{{[}15{]} x2 \textless{}- lapply(x2, rnorm)}}\label{x2---lapplyx2-rnorm}

\subsection{\texorpdfstring{{[}16{]} ``''}{{[}16{]} }}\label{section-2}

\subsection{\texorpdfstring{{[}17{]} ``\#\#\# Wait, now I had another
thought about x that I want to work
through.''}{{[}17{]} \#\#\# Wait, now I had another thought about x that I want to work through.}}\label{wait-now-i-had-another-thought-about-x-that-i-want-to-work-through.}

\subsection{\texorpdfstring{{[}18{]} ``''}{{[}18{]} }}\label{section-3}

\subsection{\texorpdfstring{{[}19{]} ``x \textless{}- x *
2''}{{[}19{]} x \textless{}- x * 2}}\label{x---x-2-1}

\subsection{\texorpdfstring{{[}20{]} ``colnames(x) \textless{}-
paste0("X",
seq\_len(ncol(x)))''}{{[}20{]} colnames(x) \textless{}- paste0("X", seq\_len(ncol(x)))}}\label{colnamesx---paste0x-seq_lenncolx}

\subsection{\texorpdfstring{{[}21{]} ``rownames(x) \textless{}-
LETTERS{[}seq\_len(nrow(x)){]}''}{{[}21{]} rownames(x) \textless{}- LETTERS{[}seq\_len(nrow(x)){]}}}\label{rownamesx---lettersseq_lennrowx}

\subsection{\texorpdfstring{{[}22{]} ``x \textless{}-
t(x)''}{{[}22{]} x \textless{}- t(x)}}\label{x---tx}

\subsection{\texorpdfstring{{[}23{]} ``x{[}, "A"{]} \textless{}-
sqrt(x{[},
"A"{]})''}{{[}23{]} x{[}, "A"{]} \textless{}- sqrt(x{[}, "A"{]})}}\label{x-a---sqrtx-a}

\subsection{\texorpdfstring{{[}24{]} ``''}{{[}24{]} }}\label{section-4}

\subsection{\texorpdfstring{{[}25{]} ``for (i in
seq\_along(colnames(x)))
\{''}{{[}25{]} for (i in seq\_along(colnames(x))) \{}}\label{for-i-in-seq_alongcolnamesx}

\subsection{{[}26{]} " set.seed(17)"}\label{set.seed17}

\subsection{{[}27{]} " x{[}, i{]} \textless{}- x{[}, i{]} +
runif(length(x{[}, i{]}), -1, 1)"}\label{x-i---x-i-runiflengthx-i--1-1}

\subsection{\texorpdfstring{{[}28{]}
``\}''}{{[}28{]} \}}}\label{section-5}

\subsection{\texorpdfstring{{[}29{]} ``''}{{[}29{]} }}\label{section-6}

\subsection{\texorpdfstring{{[}30{]} ``\#\#\# Ok. Now I can get back to
x2.''}{{[}30{]} \#\#\# Ok. Now I can get back to x2.}}\label{ok.-now-i-can-get-back-to-x2.}

\subsection{\texorpdfstring{{[}31{]} ``\#\#\# Now I just need to check
out a bunch of stuff with
it.''}{{[}31{]} \#\#\# Now I just need to check out a bunch of stuff with it.}}\label{now-i-just-need-to-check-out-a-bunch-of-stuff-with-it.}

\subsection{\texorpdfstring{{[}32{]} ``''}{{[}32{]} }}\label{section-7}

\subsection{\texorpdfstring{{[}33{]} ``lapply(x2,
length){[}1{]}''}{{[}33{]} lapply(x2, length){[}1{]}}}\label{lapplyx2-length1}

\subsection{\texorpdfstring{{[}34{]} ``max(unlist(lapply(x2,
length)))''}{{[}34{]} max(unlist(lapply(x2, length)))}}\label{maxunlistlapplyx2-length}

\subsection{\texorpdfstring{{[}35{]} ``range(unlist(lapply(x2,
length)))''}{{[}35{]} range(unlist(lapply(x2, length)))}}\label{rangeunlistlapplyx2-length}

\subsection{\texorpdfstring{{[}36{]}
``head(x2{[}{[}1{]}{]})''}{{[}36{]} head(x2{[}{[}1{]}{]})}}\label{headx21}

\subsection{\texorpdfstring{{[}37{]}
``tail(x2{[}{[}1{]}{]})''}{{[}37{]} tail(x2{[}{[}1{]}{]})}}\label{tailx21}

\subsection{\texorpdfstring{{[}38{]} ``''}{{[}38{]} }}\label{section-8}

\subsection{\texorpdfstring{{[}39{]} ``\#\# Now, based on that stuff, I
need to subset
x2.''}{{[}39{]} \#\# Now, based on that stuff, I need to subset x2.}}\label{now-based-on-that-stuff-i-need-to-subset-x2.}

\subsection{\texorpdfstring{{[}40{]} ``''}{{[}40{]} }}\label{section-9}

\subsection{\texorpdfstring{{[}41{]} ``x2 \textless{}- lapply(x2,
function(x)
x{[}1:10{]})''}{{[}41{]} x2 \textless{}- lapply(x2, function(x) x{[}1:10{]})}}\label{x2---lapplyx2-functionx-x110}

\subsection{\texorpdfstring{{[}42{]} ``''}{{[}42{]} }}\label{section-10}

\subsection{\texorpdfstring{{[}43{]} ``\#\# And turn it into a
matrix.''}{{[}43{]} \#\# And turn it into a matrix.}}\label{and-turn-it-into-a-matrix.}

\subsection{\texorpdfstring{{[}44{]} ``x2 \textless{}- do.call(rbind,
x2)''}{{[}44{]} x2 \textless{}- do.call(rbind, x2)}}\label{x2---do.callrbind-x2}

\subsection{\texorpdfstring{{[}45{]} ``''}{{[}45{]} }}\label{section-11}

\subsection{\texorpdfstring{{[}46{]} ``\#\# Now, based on x2, I need to
create
x3.''}{{[}46{]} \#\# Now, based on x2, I need to create x3.}}\label{now-based-on-x2-i-need-to-create-x3.}

\subsection{\texorpdfstring{{[}47{]} ``x3 \textless{}- x2{[},
1:2{]}''}{{[}47{]} x3 \textless{}- x2{[}, 1:2{]}}}\label{x3---x2-12}

\subsection{\texorpdfstring{{[}48{]} ``x3 \textless{}- apply(x3, 2,
round, digits =
3)''}{{[}48{]} x3 \textless{}- apply(x3, 2, round, digits = 3)}}\label{x3---applyx3-2-round-digits-3}

\subsection{\texorpdfstring{{[}49{]} ``''}{{[}49{]} }}\label{section-12}

\subsection{\texorpdfstring{{[}50{]} ``\#\# Oh wait! Another thought
about
x.''}{{[}50{]} \#\# Oh wait! Another thought about x.}}\label{oh-wait-another-thought-about-x.}

\subsection{\texorpdfstring{{[}51{]} ``''}{{[}51{]} }}\label{section-13}

\subsection{\texorpdfstring{{[}52{]} ``x{[}, 1{]} \textless{}- x{[},
1{]} * 2 +
10''}{{[}52{]} x{[}, 1{]} \textless{}- x{[}, 1{]} * 2 + 10}}\label{x-1---x-1-2-10}

\subsection{\texorpdfstring{{[}53{]} ``x{[}, 2{]} \textless{}- x{[},
1{]} + x{[},
2{]}''}{{[}53{]} x{[}, 2{]} \textless{}- x{[}, 1{]} + x{[}, 2{]}}}\label{x-2---x-1-x-2}

\subsection{\texorpdfstring{{[}54{]} ``x{[}, "A"{]} \textless{}- x{[},
"A"{]} *
2''}{{[}54{]} x{[}, "A"{]} \textless{}- x{[}, "A"{]} * 2}}\label{x-a---x-a-2}

\subsection{\texorpdfstring{{[}55{]} ``''}{{[}55{]} }}\label{section-14}

\subsection{\texorpdfstring{{[}56{]} ``\#\# Now, I want to run an
analysis on two variables in x2 and
x3.''}{{[}56{]} \#\# Now, I want to run an analysis on two variables in x2 and x3.}}\label{now-i-want-to-run-an-analysis-on-two-variables-in-x2-and-x3.}

\subsection{\texorpdfstring{{[}57{]} ``''}{{[}57{]} }}\label{section-15}

\subsection{\texorpdfstring{{[}58{]} ``fit.23 \textless{}- lm(x2
\textasciitilde{} x3, data = data.frame(x2{[}, 1{]}, x3{[},
1{]}))''}{{[}58{]} fit.23 \textless{}- lm(x2 \textasciitilde{} x3, data = data.frame(x2{[}, 1{]}, x3{[}, 1{]}))}}\label{fit.23---lmx2-x3-data-data.framex2-1-x3-1}

\subsection{\texorpdfstring{{[}59{]}
``summary(fit.23)''}{{[}59{]} summary(fit.23)}}\label{summaryfit.23}

\subsection{\texorpdfstring{{[}60{]} ``''}{{[}60{]} }}\label{section-16}

\subsection{\texorpdfstring{{[}61{]} ``\#\# And while I'm at it, I
should do an analysis on
x.''}{{[}61{]} \#\# And while I'm at it, I should do an analysis on x.}}\label{and-while-im-at-it-i-should-do-an-analysis-on-x.}

\subsection{\texorpdfstring{{[}62{]} ``''}{{[}62{]} }}\label{section-17}

\subsection{\texorpdfstring{{[}63{]} ``x \textless{}-
data.frame(x)''}{{[}63{]} x \textless{}- data.frame(x)}}\label{x---data.framex}

\subsection{\texorpdfstring{{[}64{]} ``fit.xx \textless{}-
lm(A\textasciitilde{}B, data =
x)''}{{[}64{]} fit.xx \textless{}- lm(A\textasciitilde{}B, data = x)}}\label{fit.xx---lmab-data-x}

\subsection{\texorpdfstring{{[}65{]}
``summary(fit.xx)''}{{[}65{]} summary(fit.xx)}}\label{summaryfit.xx}

\subsection{\texorpdfstring{{[}66{]}
``shapiro.test(residuals(fit.xx))''}{{[}66{]} shapiro.test(residuals(fit.xx))}}\label{shapiro.testresidualsfit.xx}

\subsection{\texorpdfstring{{[}67{]} ``''}{{[}67{]} }}\label{section-18}

\subsection{\texorpdfstring{{[}68{]} ``\#\# Ah, it looks like I should
probably transform
A.''}{{[}68{]} \#\# Ah, it looks like I should probably transform A.}}\label{ah-it-looks-like-i-should-probably-transform-a.}

\subsection{\texorpdfstring{{[}69{]} ``\#\# Let's try
that.''}{{[}69{]} \#\# Let's try that.}}\label{lets-try-that.}

\subsection{\texorpdfstring{{[}70{]} ``fit\_sqrt\_A \textless{}-
lm(I(sqrt(A))\textasciitilde{}B, data =
x)''}{{[}70{]} fit\_sqrt\_A \textless{}- lm(I(sqrt(A))\textasciitilde{}B, data = x)}}\label{fit_sqrt_a---lmisqrtab-data-x}

\subsection{\texorpdfstring{{[}71{]}
``summary(fit\_sqrt\_A)''}{{[}71{]} summary(fit\_sqrt\_A)}}\label{summaryfit_sqrt_a}

\subsection{\texorpdfstring{{[}72{]}
``shapiro.test(residuals(fit\_sqrt\_A))''}{{[}72{]} shapiro.test(residuals(fit\_sqrt\_A))}}\label{shapiro.testresidualsfit_sqrt_a}

\subsection{\texorpdfstring{{[}73{]} ``''}{{[}73{]} }}\label{section-19}

\subsection{\texorpdfstring{{[}74{]} ``\#\# Looks
good!''}{{[}74{]} \#\# Looks good!}}\label{looks-good}

\subsection{\texorpdfstring{{[}75{]} ``''}{{[}75{]} }}\label{section-20}

\subsection{\texorpdfstring{{[}76{]} ``\#\# After that. I came back and
ran another analysis
with''}{{[}76{]} \#\# After that. I came back and ran another analysis with}}\label{after-that.-i-came-back-and-ran-another-analysis-with}

\subsection{\texorpdfstring{{[}77{]} ``\#\# x2 and a new
variable.''}{{[}77{]} \#\# x2 and a new variable.}}\label{x2-and-a-new-variable.}

\subsection{\texorpdfstring{{[}78{]} ``''}{{[}78{]} }}\label{section-21}

\subsection{\texorpdfstring{{[}79{]} ``z \textless{}- c(rep("A",
nrow(x2) / 2), rep("B", nrow(x2) /
2))''}{{[}79{]} z \textless{}- c(rep("A", nrow(x2) / 2), rep("B", nrow(x2) / 2))}}\label{z---crepa-nrowx2-2-repb-nrowx2-2}

\subsection{\texorpdfstring{{[}80{]} ``fit\_anova \textless{}- aov(x2
\textasciitilde{} z, data = data.frame(x2 = x2{[}, 1{]},
z))''}{{[}80{]} fit\_anova \textless{}- aov(x2 \textasciitilde{} z, data = data.frame(x2 = x2{[}, 1{]}, z))}}\label{fit_anova---aovx2-z-data-data.framex2-x2-1-z}

\subsection{\texorpdfstring{{[}81{]}
``summary(fit\_anova)''}{{[}81{]} summary(fit\_anova)}}\label{summaryfit_anova}

```

So, let's say we've come to our script wanting to extract the code to
produce one of the results \texttt{fit.sqrt.A}, which is an analysis
that is relevant to some product. Not only do we want to double check
the results, we also want to use the code again for another purpose,
such as creating a plot of the patterns supported by the test. Manually
tracing through our code for all the variables used in the test and
finding all of the lines that were used to prepare them for the analysis
would be annoying and difficult, especially given the fact that we have
used ``x'' as a prefix for multiple unrelated objects in the script.
Instead, we can easily do this automatically with \texttt{Rclean}.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{clean}\NormalTok{(script, }\StringTok{"fit_sqrt_A"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## x <- 1:100
## x <- log(x)
## x <- x * 2
## x <- lapply(x, rep, times = 4)
## x <- do.call(cbind, x)
## x <- x * 2
## colnames(x) <- paste0("X", seq_len(ncol(x)))
## rownames(x) <- LETTERS[seq_len(nrow(x))]
## x <- t(x)
## x[, "A"] <- sqrt(x[, "A"])
## for (i in seq_along(colnames(x))) {
##   set.seed(17)
##   x[, i] <- x[, i] + runif(length(x[, i]), -1, 1)
## }
## x[, 1] <- x[, 1] * 2 + 10
## x[, 2] <- x[, 1] + x[, 2]
## x[, "A"] <- x[, "A"] * 2
## x <- data.frame(x)
## fit_sqrt_A <- lm(I(sqrt(A)) ~ B, data = x)
\end{verbatim}

As you can see, \texttt{Rclean} has picked through the tangled bits of
code and found the minimal set of lines relevant to our object of
interest. This code can now be visually inspected to adapt the original
code or ported to a new, ``refactored'' script.

\subsection{Software Availability}\label{software-availability}

The software is currently hosted on Github, and we recommend using the
\texttt{devtools} library to install directly from the repository
(\url{https://github.com/ROpenSci/Rclean}). The package is open-source
and welcomes contributions. Please visit the repository page to report
issues, request features or provide other feedback.

\section{Discussion}\label{discussion}

We have created \texttt{Rclean} to provide a simple, easy to use tool
for scientists who would like help refactoring code. Using
\texttt{Rclean} the code necessary to produce a specified result (e.g.,
an object stored in memory or a table or figure written to disk) can be
easily and \emph{reliably} isolated even when tangled with code for
other results. This functionality is enabled by graph analysis of data
provenance collected from the user's script. This is likely to be a
broadly useful tool as statistical programming becomes more common
across the sciences. Tools, such as this, that make it easier to produce
transparent, accessible code will be an important aid for improving
scientific reproducibility.

Although the workflow described is impactful, we see promise in
extending it to interface with other clean code and reproducibility
tools. One example is the \texttt{reprex} package, which provides a
simple API for sharing reproducible examples. Another possibility is to
help transtion scripts to function, package and workflow creation and
refactoring via toolboxes like \texttt{drake}. \texttt{Rclean} could
provide a reliable way to extract parts of a larger script that would be
piped to a simplified reproducible example, in the case of
\texttt{reprex}, or, since it can isolate the code from inputs to one or
more outputs, be used to extract all of the components needed to write
one or more functions that would be a part of a package or workflow, as
is the goal of \texttt{drake}.

To conclude, we hope that \texttt{Rclean} makes writing scientific
software easier for the R community. We look forward to feedback and
help with extending its application, particularly in the area of
reproducibility, such as using code cleaning in the creation of more
robust capsules (Pasquier et al. 2018). To get involved, report bugs,
suggest features, please visit the project page.

\section{Acknowledgments}\label{acknowledgments}

This work was improved by discussions with ecologists at Harvard Forest
and through the helpful review provided by the ROpenSci community,
particularly Anna Krystalli, Will Landau and Clemens Schmid. Much of the
work was funded by US National Science Foundation grant SSI-1450277 for
applications of End-to-End Data Provenance.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-Baker2016}{}
Baker, Monya. 2016. ``1,500 Scientists Lift the Lid on
Reproducibility.'' \emph{Nature} 533: 452--54.
doi:\href{https://doi.org/10.1038/533452a}{10.1038/533452a}.

\hypertarget{ref-Carata2014}{}
Carata, Lucian, Sherif Akoush, Nikilesh Balakrishnan, Thomas Bytheway,
Ripduman Sohan, Margo Seltzer, and Andy Hopper. 2014. ``A Primer on
Provenance.'' \emph{Queue} 12 (3). ACM: 10--23.
doi:\href{https://doi.org/10.1145/2602649.2602651}{10.1145/2602649.2602651}.

\hypertarget{ref-Pasquier2018}{}
Pasquier, Thomas, Matthew K. Lau, Xueyuan Han, Elizabeth Fong, Barbara
S. Lerner, Emery R. Boose, Merce Crosas, Aaron M. Ellison, and Margo
Seltzer. 2018. ``Sharing and Preserving Computational Analyses for
Posterity with encapsulator.'' \emph{Comput. Sci. Eng.} 20 (4): 111--24.
doi:\href{https://doi.org/10.1109/MCSE.2018.042781334}{10.1109/MCSE.2018.042781334}.

\hypertarget{ref-Pasquier2017}{}
Pasquier, Thomas, Matthew K. Lau, Ana Trisovic, Emery R. Boose, Ben
Couturier, Mercè Crosas, Aaron M. Ellison, Valerie Gibson, Chris R.
Jones, and Margo Seltzer. 2017. ``If these data could talk.'' \emph{Sci.
Data} 4 (September): 170114.
doi:\href{https://doi.org/10.1038/sdata.2017.114}{10.1038/sdata.2017.114}.

\hypertarget{ref-Peng2011}{}
Peng, Roger D, B. Hanson, A. Sugden, B. Alberts, R. D. Peng, F.
Dominici, S. L. Zeger, et al. 2011. ``Reproducible research in
computational science.'' \emph{Science} 334 (6060). American Association
for the Advancement of Science: 1226--7.
doi:\href{https://doi.org/10.1126/science.1213847}{10.1126/science.1213847}.

\hypertarget{ref-Stodden2018}{}
Stodden, Victoria, Jennifer Seiler, and Zhaokun Ma. 2018. ``An empirical
analysis of journal policy effectiveness for computational
reproducibility.'' \emph{Proc. Natl. Acad. Sci. U. S. A.} 115 (11).
National Academy of Sciences: 2584--9.
doi:\href{https://doi.org/10.1073/pnas.1708290115}{10.1073/pnas.1708290115}.

\hypertarget{ref-Visser2015}{}
Visser, Marco D., Sean M. McMahon, Cory Merow, Philip M. Dixon, Sydne
Record, and Eelke Jongejans. 2015. ``Speeding Up Ecological and
Evolutionary Computations in R; Essentials of High Performance Computing
for Biologists.'' Edited by Francis Ouellette. \emph{PLOS Comput. Biol.}
11 (3). Springer-Verlag: e1004140.
doi:\href{https://doi.org/10.1371/journal.pcbi.1004140}{10.1371/journal.pcbi.1004140}.

\end{document}

### 2020-02-04 joss/paper.Rmd
Spellcheck
renders pdf and md

@@
 the function used to create the figure demonstrating data provenance
-\ref{prov-graph}. Last, the `get_libs` function can be used to detect
+\@ref(fig:prov-graph). Last, the `get_libs` function can be used to detect
 the packages that a given script depends on, which it will return as
@@
 is a graphical representation of the prospective provenance generated
-for `Rclean` \ref{prov-graph}.
+for `Rclean` \@ref(fig:prov-graph).
 
@@
 API for sharing reproducible examples. Another possibility is to help
-transtion scripts to function, package and workflow creation and
+transition scripts to function, package and workflow creation and
 refactoring via toolboxes like `drake`. `Rclean` could provide a

### 2020-02-04 joss/paper.Rmd
Adds examples for other functions

@@
 script <- script.long
+
 ```
@@
 interest. This code can now be visually inspected to adapt the
-original code or ported to a new, "refactored" script.
+original code or ported to a new, "refactored" script using `keep`.
 
-```{R ex-keep}
+```{R ex-keep, eval = FALSE}
+fitSA <- clean(script, "fit_sqrt_A")
+keep(fitSA)
 
@@
 
-```{R ex-get_vars}
+This will pass the code to the clipboard for pasting into another
+document. To write directly to a new file, a file path can be
+specified.
+
+```{R ex-keep-write, eval = FALSE}
+fitSA <- clean(script, "fit_sqrt_A")
+keep(fitSA, file = "fit_SA.R")
 
@@
 
-```{R ex-code_graph}
+To explore more possible variables to extract, the `get_vars` function
+can be used to produce a list of the variables (aka. objects) that are
+created in the script.
+
+```{R ex-get_vars-hid, eval = TRUE, echo = TRUE}
+
+get_vars(script)
 
@@
 
+Especially when the code for different variables are entangled, it can
+be useful to visual the code in order to devise an approach to
+cleaning. As seen above \@ref(fig:prov-graph), `code_graph` will
+produce a visual of the code and the objects that they produce.
+
+```{R ex-code_graph, fig.cap = "Example of the plot produced by the
+code_graph function showing which lines of code produce which
+variables and which variables are used by other lines of code."}
+
+code_graph(script)
+
+```
+
+After examining the output from `get_vars` and `code_graph`, it is
+possible that more than one object needs to be isolated. To do this is
+simple in `keep` by passing the set of desired objects to the *vars*
+argument.
+
+```{R clean-mlti}
+
+clean(script, vars = c("fit_sqrt_A", "fit_anova"))
+
+```
+
+Currently, because of the data provenance that is used, libraries can
+not be isolated directly during the cleaning process. So, the
+`get_libs` function provides a way to detect the libraries for a given
+script. Just supply a file path and `get_libs` will return the
+libraries that are called by that script.
+
 ```{R ex-get_libs}
+
+get_libs(script)
 

### 2020-02-04 joss/paper.Rmd
Adds new refs to paper.bib

@@
 would be improved by refactoring, which is a common practice in
-software engineering [@Martin2009]. From this perspective, tools that
-can lower the time and energy required to refactor analytical scripts
-and otherwise help to "clean" code, but abstracted enough to be easily
-accessible, could have a significant impact on scientific
-reproducibility across all disciplines [@Visser2015].
+software engineering [Martin2009CleanCraftsmanship]. From this
+perspective, tools that can lower the time and energy required to
+refactor analytical scripts and otherwise help to "clean" code, but
+abstracted enough to be easily accessible, could have a significant
+impact on scientific reproducibility across all disciplines
+[@Visser2015].
 
@@
 script. For more information on the mechanics of the `CodeDepends`
-package, see [@Lang2019]. To get an idea of what data provenance is,
-take a look at the `code_graph` function. The plot that it generates
-is a graphical representation of the prospective provenance generated
-for `Rclean` \@ref(fig:prov-graph).
+package, see [@Lang2018PackageComprehension]. To get an idea of what
+data provenance is, take a look at the `code_graph` function. The plot
+that it generates is a graphical representation of the prospective
+provenance generated for `Rclean` \@ref(fig:prov-graph).
 

### 2020-02-05 joss/paper.Rmd
Fix new line in caption for prov figure
Fix new line issue with comment for code_graph example
Fixes citation issues from ref in text

@@
 would be improved by refactoring, which is a common practice in
-software engineering [Martin2009CleanCraftsmanship]. From this
+software engineering [@Martin2009CleanCraftsmanship]. From this
 perspective, tools that can lower the time and energy required to
@@
 
-```{R prov-graph, fig.cap = "Network diagram of the prospective data
-provenance generated for an example script. Arrows indicate
-which lines of code (numbered) produced which objects (named).", echo = FALSE}
+```{R prov-graph, fig.cap = "Network diagram of the prospective data provenance generated for an example script.
+Arrows indicate which lines of code (numbered) produced which objects (named).", echo = FALSE}
 
@@
 
-```{R long-script, echo = FALSE, eval = TRUE}
+```{R long-script, echo = FALSE, eval = FALSE}
 
-readLines(script)
+library(stats)
+x <- 1:100
+x <- log(x)
+x <- x * 2
+x <- lapply(x, rep, times = 4)
+### This is a note that I made for myself.
+### Next time, make sure to use a different analysis.
+### Also, check with someone about how to run some other analysis.
+x <- do.call(cbind, x)
+
+### Now I'm going to create a different variable.
+### This is the best variable the world has ever seen.
+
+x2 <- sample(10:1000, 100)
+x2 <- lapply(x2, rnorm)
+
+### Wait, now I had another thought about x that I want to work through.
+
+x <- x * 2
+colnames(x) <- paste0("X", seq_len(ncol(x)))
+rownames(x) <- LETTERS[seq_len(nrow(x))]
+x <- t(x)
+x[, "A"] <- sqrt(x[, "A"])
+
+for (i in seq_along(colnames(x))) {
+    set.seed(17)
+    x[, i] <- x[, i] + runif(length(x[, i]), -1, 1)
+}
+
+### Ok. Now I can get back to x2.
+### Now I just need to check out a bunch of stuff with it.
+
+lapply(x2, length)[1]
+max(unlist(lapply(x2, length)))
+range(unlist(lapply(x2, length)))
+head(x2[[1]])
+tail(x2[[1]])
+
+## Now, based on that stuff, I need to subset x2.
+
+x2 <- lapply(x2, function(x) x[1:10])
+
+## And turn it into a matrix.
+x2 <- do.call(rbind, x2)
+
+## Now, based on x2, I need to create x3.
+x3 <- x2[, 1:2]
+x3 <- apply(x3, 2, round, digits = 3)
+
+## Oh wait! Another thought about x.
+
+x[, 1] <- x[, 1] * 2 + 10
+x[, 2] <- x[, 1] + x[, 2]
+x[, "A"] <- x[, "A"] * 2
+
+## Now, I want to run an analysis on two variables in x2 and x3.
+
+fit.23 <- lm(x2 ~ x3, data = data.frame(x2[, 1], x3[, 1]))
+summary(fit.23)
+
+## And while I'm at it, I should do an analysis on x.
+
+x <- data.frame(x)
+fit.xx <- lm(A~B, data = x)
+summary(fit.xx)
+shapiro.test(residuals(fit.xx))
+
+## Ah, it looks like I should probably transform A.
+## Let's try that.
+fit_sqrt_A <- lm(I(sqrt(A))~B, data = x)
+summary(fit_sqrt_A)
+shapiro.test(residuals(fit_sqrt_A))
+
+## Looks good!
+
+## After that. I came back and ran another analysis with 
+## x2 and a new variable.
+
+z <- c(rep("A", nrow(x2) / 2), rep("B", nrow(x2) / 2))
+fit_anova <- aov(x2 ~ z, data = data.frame(x2 = x2[, 1], z))
+summary(fit_anova)
 
@@
 
-```{R ex-code_graph, fig.cap = "Example of the plot produced by the
-code_graph function showing which lines of code produce which
-variables and which variables are used by other lines of code."}
+```{R ex-code_graph, fig.cap = "Example of the plot produced by the code_graph function showing which lines of code produce which variables and which variables are used by other lines of code."}
 

### 2020-02-05 joss/paper.Rmd
Adds R pack citations

@@
 following general best practices recommended by the Tidyverse via the
-`styler` package. This code can then be passed to the `keep` function,
-which can either write the code to disk or copy the code to the user's
-clipboard (if no output file path is supplied) and the user can paste
-the code into another location (e.g. a script editor).
+`styler` package [@R-styler]. This code can then be passed to the
+`keep` function, which can either write the code to disk or copy the
+code to the user's clipboard (if no output file path is supplied) and
+the user can paste the code into another location (e.g. a script
+editor).
 
@@
 script. For more information on the mechanics of the `CodeDepends`
-package, see [@Lang2018PackageComprehension]. To get an idea of what
-data provenance is, take a look at the `code_graph` function. The plot
-that it generates is a graphical representation of the prospective
-provenance generated for `Rclean` \@ref(fig:prov-graph).
+package, see [@R-CodeDepends]. To get an idea of what data provenance
+is, take a look at the `code_graph` function. The plot that it
+generates is a graphical representation of the prospective provenance
+generated for `Rclean` \@ref(fig:prov-graph).
 
@@
 The software is currently hosted on Github, and we recommend using the
-`devtools` library to install directly from the repository
-(https://github.com/ROpenSci/Rclean). The package is open-source and
-welcomes contributions. Please visit the repository page to report
-issues, request features or provide other feedback.
+`devtools` library [@R-devtools] to install directly from the
+repository (https://github.com/ROpenSci/Rclean). The package is
+open-source and welcomes contributions. Please visit the repository
+page to report issues, request features or provide other feedback.
 
@@
 tools. One example is the `reprex` package, which provides a simple
-API for sharing reproducible examples. Another possibility is to help
+API for sharing reproducible examples [@R-reprex]. Another possibility is to help
 transition scripts to function, package and workflow creation and
-refactoring via toolboxes like `drake`. `Rclean` could provide a
-reliable way to extract parts of a larger script that would be piped
-to a simplified reproducible example, in the case of `reprex`, or,
-since it can isolate the code from inputs to one or more outputs, be
-used to extract all of the components needed to write one or more
-functions that would be a part of a package or workflow, as is the
-goal of `drake`.
+refactoring via toolboxes like `drake` [@R-drake]. `Rclean` could
+provide a reliable way to extract parts of a larger script that would
+be piped to a simplified reproducible example, in the case of
+`reprex`, or, since it can isolate the code from inputs to one or more
+outputs, be used to extract all of the components needed to write one
+or more functions that would be a part of a package or workflow, as is
+the goal of `drake`.
 
@@
 # References
+
+<!-- Use overleaf papers.bib + knitr::write_bib -->

### 2020-02-05 joss/paper.Rmd
Fix fit_sqrt_A

@@
 So, let's say we've come to our script wanting to extract the code to
-produce one of the results `fit.sqrt.A`, which is an analysis that is
+produce one of the results `fit_sqrt_A`, which is an analysis that is
 relevant to some product. Not only do we want to double check the

### 2020-02-06 joss/paper.Rmd
Read through and spellcheck

@@
 
-More often then not, when someone is writing an R script, the intent
-to produce a set of results, such as a statistical analysis, figure,
-table, etc. This set of results is always a subset of a much larger
-set of possible ways to explore a dataset, as there are many
-statistical approaches and tests, let alone ways to create
-visualizations and other representations of patterns in data. This
-commonly leads to lengthy, complicated scripts from which researchers
-manually subset results, but never refactor, i.e. refine code so that
-it is shorter and focused on a desired product.
-
 The goal of `Rclean` is to provide a set of tools that help someone
-reduce and organize code based on results. The package uses an
+reduce and organize code based on results. More often then not, when
+someone is writing an R script, the intent is to produce a set of
+results, such as a statistical analysis, figure, table, etc. This set
+of results is always a subset of a much larger set of possible ways to
+explore a dataset, as there are many statistical approaches and tests,
+let alone ways to create visualizations and other representations of
+patterns in data. This commonly leads to lengthy, complicated scripts
+from which researchers manually subset results, but likely never to be
+refactored because of the difficulty in disentangling the code needed
+to produce some results and not others. The 'Rclean' package uses an
 automated technique based on data provenance (details below) to
 analyze existing scripts and provide ways to identify and extract code
-to produce a desired output. To keep the process simple and
+to produce a desired output.
+
+## The API
+
+To keep the process simple and
 straight-forward much of this process has been abstracted for the
@@
 3. Get information about the possible results and repeat as needed.
-
-## The API
 
@@
 tools. One example is the `reprex` package, which provides a simple
-API for sharing reproducible examples [@R-reprex]. Another possibility is to help
-transition scripts to function, package and workflow creation and
-refactoring via toolboxes like `drake` [@R-drake]. `Rclean` could
-provide a reliable way to extract parts of a larger script that would
-be piped to a simplified reproducible example, in the case of
-`reprex`, or, since it can isolate the code from inputs to one or more
-outputs, be used to extract all of the components needed to write one
-or more functions that would be a part of a package or workflow, as is
-the goal of `drake`.
+API for sharing reproducible examples [@R-reprex]. Another possibility
+is to help transition scripts to function, package and workflow
+creation and refactoring via toolboxes like `drake`
+[@R-drake]. `Rclean` could provide a reliable way to extract parts of
+a larger script that would be piped to a simplified reproducible
+example, in the case of `reprex`, or, since it can isolate the code
+from inputs to one or more outputs, be used to extract all of the
+components needed to write one or more functions that would be a part
+of a package or workflow, as is the goal of `drake`.
 
@@
 extending its application, particularly in the area of
-reproducibility, such as using code cleaning in the creation of more
-robust capsules [@Pasquier2018]. To get involved, report bugs, suggest
-features, please visit the project page.
+reproducibility. To get involved, report bugs, suggest features,
+please visit the project page.
 

### 2020-02-07 README.rmd
Fixes README figure resolution
Adds ROS logo to README

@@
 
-You can install
-[Rclean](https://cran.r-project.org/web/packages/Rclean/) from *CRAN*:
-
-```{r eval = FALSE}
-install.packages("Rclean")
-```
-
 You can install the most up to date version easily with
@@
 ```{r eval = FALSE} 
-script <- "example/simple_script.R"
+script <- system.file("example", "simple_script.R", package = "Rclean")
 
@@
 
-```{r eval = TRUE}
+```{r eval = TRUE, out.width = "75%", dpi = 300}
 
@@
 By contributing to this project, you agree to abide by its terms.
+
+![ropensci_footer](https://ropensci.org/public_images/ropensci_footer.png)

### 2020-02-12 README.rmd

@@
 <!-- Code status -->
-[![Build Status](https://travis-ci.org/MKLau/Rclean.svg?branch=master)](https://travis-ci.org/MKLau/Rclean) 
-[![Coverage status](https://codecov.io/gh/MKLau/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/MKLau/Rclean?branch=master)
+[![Build Status](https://travis-ci.org/ROpenSci/Rclean.svg?branch=master)](https://travis-ci.org/ROpenSci/Rclean) 
+[![Coverage status](https://codecov.io/gh/ROpenSci/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/ROpenSci/Rclean?branch=master)
 
@@
 
-- [Rclean](https://github.com/ProvTools/Rclean) was created to help
+- [Rclean](https://github.com/MKLau/Rclean) was created to help
     scientists more *easily* write “cleaner” code.

### 2020-02-13 joss/paper.rmd
Removes reference to example in intro, provenance comments paragraph and adds paper.yaml

--- 2020-02-06 joss/paper.Rmd
@@
 designed to ease refactoring for scientists that use R but do not have
-formal training in software engineering. Here, we detail the structure
-of the package's API, describe the general workflow illustrated by an
-example use case and provide some background on how data provenance
-enables the underlying functionality of the package. We then end with
-a discussion of future applications of data provenance in the context
-of "code cleaning" and the potential integration with other software
-engineering tools for the R community.
+formal training in software engineering.
 
@@
 to produce some results and not others. The 'Rclean' package uses an
-automated technique based on data provenance (details below) to
-analyze existing scripts and provide ways to identify and extract code
-to produce a desired output.
-
-## The API
-
-To keep the process simple and
-straight-forward much of this process has been abstracted for the
-user, and the API has been kept to a minimum set of functions that
-enable a user to conduct the following basic workflow:
-
-1. Obtain the "cleaned" code for a result(s).
-2. Transfer the code to a new context (e.g. a new script,
-function, reproducible example, web-app, etc.).
-3. Get information about the possible results and repeat as needed.
-
-The package's main functions are `clean` and `keep`. When provided a
-file path to a script and the name of a result (or a set of results),
-`clean` analyzes the script's code and extracts the lines of code
-required to produce the results. By default, code is formatted
-following general best practices recommended by the Tidyverse via the
-`styler` package [@R-styler]. This code can then be passed to the
-`keep` function, which can either write the code to disk or copy the
-code to the user's clipboard (if no output file path is supplied) and
-the user can paste the code into another location (e.g. a script
-editor).
-
-In the process of cleaning a script, it is likely that a user will not
-know the precise objects they want and might require some help
-analyzing it. There are several functions to help with this
-process. The `get_vars` function will return a list of possible
-results for a given script at a supplied file path. This is obviously
-an important step, and justifiably, the default behavior of the
-`clean` function is to run `get_vars` if no results are supplied. To
-help with limiting and checking the selection of results, the
-`code_graph` function creates a network graph of the relationships
-among the various results and lines of code in the script, which is
-the function used to create the figure demonstrating data provenance
-\@ref(fig:prov-graph). Last, the `get_libs` function can be used to detect
-the packages that a given script depends on, which it will return as
-coded library calls that can be inserted into a cleaned script.
+automated technique based on data provenance to analyze existing
+scripts and provide ways to identify and extract code to produce a
+desired output.
 
@@
 
-Relatedly, it is important to point out that `Rclean` *does not* keep
-comments present in code. This could be seen as a limitation of the
-data provenance, which currently does not assign them a
-relationships. Therefore, although there is often very useful or even
-invaluable information in comments, the `clean` function removes
-them. This is a general issue with automated methods for detecting the
-relationships between comments and the code itself. Comments at the
-end of lines are typically relevant to the line they are on, but this
-is not a requirement and could refer to other lines. Also, comments
-occupying their own lines usually refer to the following lines, but
-this is also not necessarily the case. As `clean` depends on the
-unambiguous determination of relationships in the production of
-results, it cannot operate automatically on comments. However,
-comments in the original code remain untouched and can be used to
-inform the reduced code. Also, as the `clean` function is oriented
-toward isolating code based on a specific result, the resulting code
-tends to naturally support the generation of new comments that are
-higher level (e.g. "The following produces a plot of the mean response
-of each treatment group."), and lower level comments are not necessary
-because the code is simpler and clearer.
-
 In the future, it would also be useful to extend the existing
@@
 has already been done in the direction of implementing retrospective
-provenance for code cleaning in R (see http://end-to-end-provenance.github.io).
-
-# Results
-
-## Example
-
-Data analysis can be messy and complicated, so it's no wonder that the
-code often reflects this. "What did I measure? What analyses are
-relevant to them? Do I need to transform the data? What's the function
-for the analysis I want to run?" This is why having a way to isolate
-code based on variables can be valuable. The following is an example
-of a script that has some complications. As you can see, although the
-script is not extremely long or complicated, it's difficult enough to
-make it frustrating to visualize it in its entirety and pick through
-it.
-
-```{R long-setup, echo = FALSE, eval = TRUE, results = "hide"}
-
-script.long <- system.file(
-    "example", 
-    "long_script.R", 
-    package = "Rclean")
-script <- script.long
-
-```
-
-```{R long-script, echo = FALSE, eval = FALSE}
-
-library(stats)
-x <- 1:100
-x <- log(x)
-x <- x * 2
-x <- lapply(x, rep, times = 4)
-### This is a note that I made for myself.
-### Next time, make sure to use a different analysis.
-### Also, check with someone about how to run some other analysis.
-x <- do.call(cbind, x)
-
-### Now I'm going to create a different variable.
-### This is the best variable the world has ever seen.
-
-x2 <- sample(10:1000, 100)
-x2 <- lapply(x2, rnorm)
-
-### Wait, now I had another thought about x that I want to work through.
-
-x <- x * 2
-colnames(x) <- paste0("X", seq_len(ncol(x)))
-rownames(x) <- LETTERS[seq_len(nrow(x))]
-x <- t(x)
-x[, "A"] <- sqrt(x[, "A"])
-
-for (i in seq_along(colnames(x))) {
-    set.seed(17)
-    x[, i] <- x[, i] + runif(length(x[, i]), -1, 1)
-}
-
-### Ok. Now I can get back to x2.
-### Now I just need to check out a bunch of stuff with it.
-
-lapply(x2, length)[1]
-max(unlist(lapply(x2, length)))
-range(unlist(lapply(x2, length)))
-head(x2[[1]])
-tail(x2[[1]])
-
-## Now, based on that stuff, I need to subset x2.
-
-x2 <- lapply(x2, function(x) x[1:10])
-
-## And turn it into a matrix.
-x2 <- do.call(rbind, x2)
-
-## Now, based on x2, I need to create x3.
-x3 <- x2[, 1:2]
-x3 <- apply(x3, 2, round, digits = 3)
-
-## Oh wait! Another thought about x.
-
-x[, 1] <- x[, 1] * 2 + 10
-x[, 2] <- x[, 1] + x[, 2]
-x[, "A"] <- x[, "A"] * 2
-
-## Now, I want to run an analysis on two variables in x2 and x3.
-
-fit.23 <- lm(x2 ~ x3, data = data.frame(x2[, 1], x3[, 1]))
-summary(fit.23)
-
-## And while I'm at it, I should do an analysis on x.
-
-x <- data.frame(x)
-fit.xx <- lm(A~B, data = x)
-summary(fit.xx)
-shapiro.test(residuals(fit.xx))
-
-## Ah, it looks like I should probably transform A.
-## Let's try that.
-fit_sqrt_A <- lm(I(sqrt(A))~B, data = x)
-summary(fit_sqrt_A)
-shapiro.test(residuals(fit_sqrt_A))
-
-## Looks good!
-
-## After that. I came back and ran another analysis with 
-## x2 and a new variable.
-
-z <- c(rep("A", nrow(x2) / 2), rep("B", nrow(x2) / 2))
-fit_anova <- aov(x2 ~ z, data = data.frame(x2 = x2[, 1], z))
-summary(fit_anova)
-
-```
-
-So, let's say we've come to our script wanting to extract the code to
-produce one of the results `fit_sqrt_A`, which is an analysis that is
-relevant to some product. Not only do we want to double check the
-results, we also want to use the code again for another purpose, such
-as creating a plot of the patterns supported by the test. Manually
-tracing through our code for all the variables used in the test and
-finding all of the lines that were used to prepare them for the
-analysis would be annoying and difficult, especially given the fact
-that we have used "x" as a prefix for multiple unrelated objects in
-the script. Instead, we can easily do this automatically with
-`Rclean`.
-
-```{R long}
-
-clean(script, "fit_sqrt_A")
-
-```
-
-As you can see, `Rclean` has picked through the tangled bits of code
-and found the minimal set of lines relevant to our object of
-interest. This code can now be visually inspected to adapt the
-original code or ported to a new, "refactored" script using `keep`.
-
-```{R ex-keep, eval = FALSE}
-fitSA <- clean(script, "fit_sqrt_A")
-keep(fitSA)
-
-```
-
-This will pass the code to the clipboard for pasting into another
-document. To write directly to a new file, a file path can be
-specified.
-
-```{R ex-keep-write, eval = FALSE}
-fitSA <- clean(script, "fit_sqrt_A")
-keep(fitSA, file = "fit_SA.R")
-
-```
-
-To explore more possible variables to extract, the `get_vars` function
-can be used to produce a list of the variables (aka. objects) that are
-created in the script.
-
-```{R ex-get_vars-hid, eval = TRUE, echo = TRUE}
-
-get_vars(script)
-
-```
-
-Especially when the code for different variables are entangled, it can
-be useful to visual the code in order to devise an approach to
-cleaning. As seen above \@ref(fig:prov-graph), `code_graph` will
-produce a visual of the code and the objects that they produce.
-
-```{R ex-code_graph, fig.cap = "Example of the plot produced by the code_graph function showing which lines of code produce which variables and which variables are used by other lines of code."}
-
-code_graph(script)
-
-```
-
-After examining the output from `get_vars` and `code_graph`, it is
-possible that more than one object needs to be isolated. To do this is
-simple in `keep` by passing the set of desired objects to the *vars*
-argument.
-
-```{R clean-mlti}
-
-clean(script, vars = c("fit_sqrt_A", "fit_anova"))
-
-```
-
-Currently, because of the data provenance that is used, libraries can
-not be isolated directly during the cleaning process. So, the
-`get_libs` function provides a way to detect the libraries for a given
-script. Just supply a file path and `get_libs` will return the
-libraries that are called by that script.
-
-```{R ex-get_libs}
-
-get_libs(script)
-
-```
+provenance for code cleaning in R (see
+http://end-to-end-provenance.github.io).
 
@@
 
-We have created ``Rclean`` to provide a simple, easy to use tool for
-scientists who would like help refactoring code. Using ``Rclean`` the
-code necessary to produce a specified result (e.g., an object stored
-in memory or a table or figure written to disk) can be easily and
-*reliably* isolated even when tangled with code for other
-results. This functionality is enabled by graph analysis of data
-provenance collected from the user's script. This is likely to be a
-broadly useful tool as statistical programming becomes more common
-across the sciences. Tools, such as this, that make it easier to
-produce transparent, accessible code will be an important aid for
-improving scientific reproducibility.
-
-Although the workflow described is impactful, we see promise in
-extending it to interface with other clean code and reproducibility
-tools. One example is the `reprex` package, which provides a simple
-API for sharing reproducible examples [@R-reprex]. Another possibility
-is to help transition scripts to function, package and workflow
-creation and refactoring via toolboxes like `drake`
-[@R-drake]. `Rclean` could provide a reliable way to extract parts of
-a larger script that would be piped to a simplified reproducible
-example, in the case of `reprex`, or, since it can isolate the code
-from inputs to one or more outputs, be used to extract all of the
-components needed to write one or more functions that would be a part
-of a package or workflow, as is the goal of `drake`.
-
-To conclude, we hope that `Rclean` makes writing scientific software
-easier for the R community. We look forward to feedback and help with
-extending its application, particularly in the area of
+We see promise in connecting `Rclean` with other clean code and
+reproducibility tools. One example is the `reprex` package, which
+provides a simple API for sharing reproducible examples
+[@R-reprex]. Another possibility is to help transition scripts to
+function, package and workflow creation and refactoring via toolboxes
+like `drake` [@R-drake]. `Rclean` could provide a reliable way to
+extract parts of a larger script that would be piped to a simplified
+reproducible example, in the case of `reprex`, or, since it can
+isolate the code from inputs to one or more outputs, be used to
+extract all of the components needed to write one or more functions
+that would be a part of a package or workflow, as is the goal of
+`drake`. To conclude, we hope that `Rclean` makes writing scientific
+software easier for the R community. We look forward to feedback and
+help with extending its application, particularly in the area of
 reproducibility. To get involved, report bugs, suggest features,

### 2020-02-13 joss/paper.rmd
Fixes citations

@@
----
-title: 'Rclean: A Tool for Writing Cleaner, More Transparent Code'
-tags:
-  - R
-  - reproducibility
-  - transparency
-  - code cleaning
-  - data provenance
-authors:
-  - name: Matthew K. Lau
-    orcid: 0000-0003-3758-2406
-    affiliation: 1
-  - name: Thomas F. J.-M. Pasquier
-    orcid: 0000-0001-6876-1306
-    affiliation: "2, 3" 
-  - name: Margo Seltzer
-    orcid: 0000-0002-2165-4658
-    affiliation: "4"
-affiliations:
- - name: Harvard Forest, Harvard University 
-   index: 1
- - name: Department of Computer Science, University of Bristol 
-   index: 2
- - name: School of Engineering and Applied Science, Harvard University
-   index: 3
- - name: Department of Computer Science, University of British Columbia
-   index: 4
-date: 
-bibliography: paper.bib
----
-
 # Introduction
@@
 concerns have begun to surface about the reproducibility of scientific
-research in general [@Peng2011 @Baker2016] and the potential issues
-stemming from issues with analytical software [@Pasquier2017
+research in general [@Peng2011, @Baker2016] and the potential issues
+stemming from issues with analytical software [@Pasquier2017,
 @Stodden2018]. Specifically, there is a growing recognition across
@@
 generates is a graphical representation of the prospective provenance
-generated for `Rclean` \@ref(fig:prov-graph).
+generated for `Rclean` \ref{fig:prov-graph}.
 

### 2020-02-13 joss/paper.rmd
Removes multi-cites and brackets

@@
 concerns have begun to surface about the reproducibility of scientific
-research in general [@Peng2011, @Baker2016] and the potential issues
-stemming from issues with analytical software [@Pasquier2017,
-@Stodden2018]. Specifically, there is a growing recognition across
-disciplines that simply making data and software "available" is not
-enough and that there is a need to improve the transparency and
-stability of scientific software [@Pasquier2018].
+research in general @Baker2016 and the potential issues stemming from
+issues with analytical software @Stodden2018. Specifically, there is a
+growing recognition across disciplines that simply making data and
+software "available" is not enough and that there is a need to improve
+the transparency and stability of scientific software @Pasquier2018.
 
@@
 would be improved by refactoring, which is a common practice in
-software engineering [@Martin2009CleanCraftsmanship]. From this
+software engineering @Martin2009CleanCraftsmanship. From this
 perspective, tools that can lower the time and energy required to
@@
 impact on scientific reproducibility across all disciplines
-[@Visser2015].
+@Visser2015.
 
@@
 rigorously determine the the unique computational pathway from inputs
-to results [@Carata2014]. To avoid confusion, note that "data" in this
+to results @Carata2014. To avoid confusion, note that "data" in this
 context is used in a broad sense to include all of the information
@@
 script. For more information on the mechanics of the `CodeDepends`
-package, see [@R-CodeDepends]. To get an idea of what data provenance
+package, see @R-CodeDepends. To get an idea of what data provenance
 is, take a look at the `code_graph` function. The plot that it
@@
 The software is currently hosted on Github, and we recommend using the
-`devtools` library [@R-devtools] to install directly from the
+`devtools` library @R-devtools to install directly from the
 repository (https://github.com/ROpenSci/Rclean). The package is
@@
 provides a simple API for sharing reproducible examples
-[@R-reprex]. Another possibility is to help transition scripts to
+@R-reprex. Another possibility is to help transition scripts to
 function, package and workflow creation and refactoring via toolboxes
-like `drake` [@R-drake]. `Rclean` could provide a reliable way to
+like `drake` @R-drake. `Rclean` could provide a reliable way to
 extract parts of a larger script that would be piped to a simplified

### 2020-02-13 joss/paper.rmd
tests manual brakcets

@@
 concerns have begun to surface about the reproducibility of scientific
-research in general @Baker2016 and the potential issues stemming from
+research in general [@Baker2016] and the potential issues stemming from
 issues with analytical software @Stodden2018. Specifically, there is a

### 2020-02-13 joss/paper.rmd
Manual brackets and yaml

--- 2020-02-13 joss/paper.rmd
@@
 concerns have begun to surface about the reproducibility of scientific
-research in general [@Peng2011, @Baker2016] and the potential issues
-stemming from issues with analytical software [@Pasquier2017,
-@Stodden2018]. Specifically, there is a growing recognition across
-disciplines that simply making data and software "available" is not
-enough and that there is a need to improve the transparency and
-stability of scientific software [@Pasquier2018].
+research in general [@Baker2016] and the potential issues stemming from
+issues with analytical software [@Stodden2018]. Specifically, there is a
+growing recognition across disciplines that simply making data and
+software "available" is not enough and that there is a need to improve
+the transparency and stability of scientific software [@Pasquier2018].
 

### 2020-02-13 joss/paper.rmd
Increases figure resolution

@@
 
-```{R load-script, echo = FALSE, results = "hide"}
+a```{R load-script, echo = FALSE, results = "hide"}
 library(CodeDepends)
@@
 
-```{R prov-graph, fig.cap = "Network diagram of the prospective data provenance generated for an example script.
+```{R prov-graph, dpi = 300, fig.cap = "Network diagram of the prospective data provenance generated for an example script.
 Arrows indicate which lines of code (numbered) produced which objects (named).", echo = FALSE}

### 2020-03-11 ropensci/rclean_technote.Rmd
Creates rclean_technote.Rmd

--- 2020-02-06 joss/paper.Rmd
@@
----
-title: 'Rclean: A Tool for Writing Cleaner, More Transparent Code'
-tags:
-  - R
-  - reproducibility
-  - transparency
-  - code cleaning
-  - data provenance
-authors:
-  - name: Matthew K. Lau
-    orcid: 0000-0003-3758-2406
-    affiliation: 1
-  - name: Thomas F. J.-M. Pasquier
-    orcid: 0000-0001-6876-1306
-    affiliation: "2, 3" 
-  - name: Margo Seltzer
-    orcid: 0000-0002-2165-4658
-    affiliation: "4"
-affiliations:
- - name: Harvard Forest, Harvard University 
-   index: 1
- - name: Department of Computer Science, University of Bristol 
-   index: 2
- - name: School of Engineering and Applied Science, Harvard University
-   index: 3
- - name: Department of Computer Science, University of British Columbia
-   index: 4
-date: 
-bibliography: paper.bib
----
+Rclean: Automated Tools for Cleaning R Code
+===========================================
 
-# Introduction
+> Leave the code cleaner than you found it. 
+-- R.C. Martin in *Clean Code*
 
-The growth of programming in the sciences has been explosive in the
-last decade. This has facilitated the rapid advancement of science
-through the agile development of computational tools. However,
-concerns have begun to surface about the reproducibility of scientific
-research in general [@Peng2011 @Baker2016] and the potential issues
-stemming from issues with analytical software [@Pasquier2017
-@Stodden2018]. Specifically, there is a growing recognition across
-disciplines that simply making data and software "available" is not
-enough and that there is a need to improve the transparency and
-stability of scientific software [@Pasquier2018].
+Data analysis can be messy and complicated, so it's no wonder that the
+code often reflects this. "What did I measure? What analyses are
+relevant to them? Do I need to transform the data? What's the function
+for the analysis I want to run?" In addition, although many
+researchers see the value in learning to write software, the entry
+level is still exceedingly high. The `R` language has become very
+popular among scientists and analysts because of the lower threshold,
+which is good in that it empowers science. The downside is that
+learning to create good software is a skill that takes a considerable
+amount of time to learn, which means that many scientists write code
+that will get the job "done" but lacks transparency and is highly
+unstable (i.e. buggy).
 
-At the core of the growth of scientific computation, the ``R``
-statistical programming language has grown exponentially to become one
-of the top ten programming languages in use today. At it's root R is a
-*statistical* programming language. That is, it was designed for use
-in analytical workflows; and the majority of the R community is
-focused on producing code for idiosyncratic projects that are
-*results* oriented. Also, R's design is intentionally at a level that
-abstracts many aspects of programming that would otherwise act as a
-barrier to entry for many users. This is good in that there are many
-people who use R to their benefit with little to no formal training in
-computer science or software engineering, but these same users can
-also be frequently frustrated by code that is fragile, buggy and
-complicated enough to quickly become obtuse even to the authors. The
-stability, reproducibility and re-use of scientific analyses in R
-would be improved by refactoring, which is a common practice in
-software engineering [@Martin2009CleanCraftsmanship]. From this
-perspective, tools that can lower the time and energy required to
-refactor analytical scripts and otherwise help to "clean" code, but
-abstracted enough to be easily accessible, could have a significant
-impact on scientific reproducibility across all disciplines
-[@Visser2015].
-
-To provide support for easier refactoring in R, we have created
-``Rclean``. The ``Rclean`` package provides tools to automatically
-reduce a script to the parts that are specifically relevant to a
-research product (e.g.  a scientific report, academic talk, research
-article, etc.). Although potentially useful to all R coders, it was
-designed to ease refactoring for scientists that use R but do not have
-formal training in software engineering. Here, we detail the structure
-of the package's API, describe the general workflow illustrated by an
-example use case and provide some background on how data provenance
-enables the underlying functionality of the package. We then end with
-a discussion of future applications of data provenance in the context
-of "code cleaning" and the potential integration with other software
-engineering tools for the R community.
-
-# Methods
-
-The goal of `Rclean` is to provide a set of tools that help someone
-reduce and organize code based on results. More often then not, when
-someone is writing an R script, the intent is to produce a set of
-results, such as a statistical analysis, figure, table, etc. This set
-of results is always a subset of a much larger set of possible ways to
+The goal of `Rclean` is to provide a tool that help someone reduce and
+organize code based on results.  More often then not, when someone is
+writing an R script, the intent is to produce a set of results, such
+as a statistical analysis, figure or table. This set of results is
+nearly always a subset of a much larger set of possible ways to
 explore a dataset, as there are many statistical approaches and tests,
@@
 refactored because of the difficulty in disentangling the code needed
-to produce some results and not others. The 'Rclean' package uses an
-automated technique based on data provenance (details below) to
-analyze existing scripts and provide ways to identify and extract code
-to produce a desired output.
+to produce some results and not others.
 
-## The API
+The `Rclean` package uses an automated technique based on data
+provenance and network algorithms to analyze existing scripts and
+provide ways to identify and extract code to produce a desired output
+without having to manually conduct the search through the code line by
+line. `Rclean` was designed to ease refactoring for scientists that
+use R but do not have formal training in software engineering and
+specifically with the "art" of creating clean code; however, because
+manually culling code is tedious and potentially leads to errors,
+`Rclean` can be a useful tool for everyone at all levels of coding
+ability.
 
-To keep the process simple and
-straight-forward much of this process has been abstracted for the
-user, and the API has been kept to a minimum set of functions that
-enable a user to conduct the following basic workflow:
+# The Provenance Engine Under the Hood
 
-1. Obtain the "cleaned" code for a result(s).
-2. Transfer the code to a new context (e.g. a new script,
-function, reproducible example, web-app, etc.).
-3. Get information about the possible results and repeat as needed.
-
-The package's main functions are `clean` and `keep`. When provided a
-file path to a script and the name of a result (or a set of results),
-`clean` analyzes the script's code and extracts the lines of code
-required to produce the results. By default, code is formatted
-following general best practices recommended by the Tidyverse via the
-`styler` package [@R-styler]. This code can then be passed to the
-`keep` function, which can either write the code to disk or copy the
-code to the user's clipboard (if no output file path is supplied) and
-the user can paste the code into another location (e.g. a script
-editor).
-
-In the process of cleaning a script, it is likely that a user will not
-know the precise objects they want and might require some help
-analyzing it. There are several functions to help with this
-process. The `get_vars` function will return a list of possible
-results for a given script at a supplied file path. This is obviously
-an important step, and justifiably, the default behavior of the
-`clean` function is to run `get_vars` if no results are supplied. To
-help with limiting and checking the selection of results, the
-`code_graph` function creates a network graph of the relationships
-among the various results and lines of code in the script, which is
-the function used to create the figure demonstrating data provenance
-\@ref(fig:prov-graph). Last, the `get_libs` function can be used to detect
-the packages that a given script depends on, which it will return as
-coded library calls that can be inserted into a cleaned script.
-
-## Data Provenance
-
-All of these processes rely on the generation of data provenance.  The
-term provenance means information about the origins of some
-object. Data provenance is a formal representation of the execution of
-a computational process (https://www.w3.org/TR/prov-dm/), to
-rigorously determine the the unique computational pathway from inputs
-to results [@Carata2014]. To avoid confusion, note that "data" in this
-context is used in a broad sense to include all of the information
-generated during computation, not just the data that are collected in
-a research project that are used as input to an analysis. Having the
-formalized, mathematically rigorous representation that data
-provenance provides guarantees that the analyses that `Rclean`
-conducts are theoretically sound. Most importantly, because the
-relationships defined by the provenance can be represented as a graph,
-it is possible to apply network search algorithms to determine the
-minimum and sufficient code needed to generate the chosen result in
-the `clean` function.
+The process that `Rclean` uses relies on the generation of data
+provenance.  The term provenance means information about the origins
+of some object. Data provenance is a formal representation of the
+execution of a computational process (https://www.w3.org/TR/prov-dm/),
+to rigorously determine the the unique computational pathway from
+inputs to results [@Carata2014]. To avoid confusion, note that "data"
+in this context is used in a broad sense to include all of the
+information generated during computation, not just the data that are
+collected in a research project that are used as input to an
+analysis. Having the formalized, mathematically rigorous
+representation that data provenance provides guarantees that the
+analyses that `Rclean` conducts are theoretically sound. Most
+importantly, because the relationships defined by the provenance can
+be represented as a graph, it is possible to apply network search
+algorithms to determine the minimum and sufficient code needed to
+generate the chosen result in the `clean` function.
 
@@
 
-Relatedly, it is important to point out that `Rclean` *does not* keep
-comments present in code. This could be seen as a limitation of the
-data provenance, which currently does not assign them a
-relationships. Therefore, although there is often very useful or even
-invaluable information in comments, the `clean` function removes
-them. This is a general issue with automated methods for detecting the
-relationships between comments and the code itself. Comments at the
-end of lines are typically relevant to the line they are on, but this
-is not a requirement and could refer to other lines. Also, comments
-occupying their own lines usually refer to the following lines, but
-this is also not necessarily the case. As `clean` depends on the
-unambiguous determination of relationships in the production of
-results, it cannot operate automatically on comments. However,
-comments in the original code remain untouched and can be used to
-inform the reduced code. Also, as the `clean` function is oriented
-toward isolating code based on a specific result, the resulting code
-tends to naturally support the generation of new comments that are
-higher level (e.g. "The following produces a plot of the mean response
-of each treatment group."), and lower level comments are not necessary
-because the code is simpler and clearer.
+As you can see, the provenance provides a network representation of
+relationships among functions and objects. This is very powerful
+because we can now apply algorithms analyze the R script with respect
+to our results. The main function of `Rclean`, called `clean`, takes
+the provenance and applies a depth first network search algorithm to
+determine the pathways leading from inputs to outputs, excluding any
+objects or lines of code that do not fall along that pathway and are,
+therefore, not necessary to produce the desired set of results. As
+demonstrated in the next section, through this process, we can produce
+a new script with the minimal code necessary to generate the output we
+want.
 
-In the future, it would also be useful to extend the existing
-framework to support other provenance methods. One such possibility is
-*retrospective provenance*, which tracks a computational process as it
-is executing. Through this active, concurrent monitoring,
-retrospective provenance can gather information that static
-prospective provenance can't. Greater details of the computational
-process would enable other features that could address some
-challenges, such as processing information from comments, parsing
-control statements and replicating random processes. However, using
-retrospective provenance comes at a cost. In order to gather it, the
-script needs to be executed. When scripts are computationally
-intensive or contain bugs that stop execution, then retrospective
-provenance can not be obtained for part or all of the code. Some work
-has already been done in the direction of implementing retrospective
-provenance for code cleaning in R (see http://end-to-end-provenance.github.io).
+# Using `Rclean` to clean your code
 
-# Results
-
-## Example
-
-Data analysis can be messy and complicated, so it's no wonder that the
-code often reflects this. "What did I measure? What analyses are
-relevant to them? Do I need to transform the data? What's the function
-for the analysis I want to run?" This is why having a way to isolate
-code based on variables can be valuable. The following is an example
-of a script that has some complications. As you can see, although the
-script is not extremely long or complicated, it's difficult enough to
-make it frustrating to visualize it in its entirety and pick through
-it.
+The following is an example of a script that has some "complications."
+As you can see, although the script is not extremely long or
+complicated, it's difficult enough to make it frustrating to visualize
+it in its entirety and pick through it.
 
@@
 ```{R long}
-
+library(Rclean)
 clean(script, "fit_sqrt_A")
@@
 
-# Discussion
+# Concluding Remarks and Future Work
 
@@
 *reliably* isolated even when tangled with code for other
-results. This functionality is enabled by graph analysis of data
-provenance collected from the user's script. This is likely to be a
-broadly useful tool as statistical programming becomes more common
-across the sciences. Tools, such as this, that make it easier to
-produce transparent, accessible code will be an important aid for
-improving scientific reproducibility.
+results. Tools, such as this, that make it easier to produce
+transparent, accessible code will be an important aid for improving
+scientific reproducibility.
 
-Although the workflow described is impactful, we see promise in
-extending it to interface with other clean code and reproducibility
-tools. One example is the `reprex` package, which provides a simple
-API for sharing reproducible examples [@R-reprex]. Another possibility
-is to help transition scripts to function, package and workflow
-creation and refactoring via toolboxes like `drake`
-[@R-drake]. `Rclean` could provide a reliable way to extract parts of
-a larger script that would be piped to a simplified reproducible
-example, in the case of `reprex`, or, since it can isolate the code
-from inputs to one or more outputs, be used to extract all of the
-components needed to write one or more functions that would be a part
-of a package or workflow, as is the goal of `drake`.
+The `clean` function provides an effective way to remove code that is
+unwanted; however, many researchers are wary about doing this exact
+thing for at least a few reasons. Perhaps the top reason is that the
+main goal of an analysis is the results and taking time to craft
+transparent, dependable software is not the priority. As such, taking
+time to go back through a script and remove code is time
+wasted. Relatedly, for most researchers the best way to keep track of
+the various analyses that they have explored is to keep them in the
+script, as they do not use a rigorous version control system but
+instead rely on file backups and informal versioning. Although we
+can't give researchers more hours in the day, providing an easier and
+more reliable means to remove unused code will lower the barrier to
+creating better, cleaner code. Combined with the increasing use of
+version control systems and digital notebooks, the practice of
+"saving" analytical ideas in a script will become less common and code
+quality will increase.
+
+Relatedly, it is important to point out that `Rclean` *does not* keep
+comments present in code. This is a limitation of the data provenance,
+which currently does not assign them a relationships. Therefore,
+although there is often very useful or even invaluable information in
+comments, the `clean` function removes them. This is a general issue
+with automated methods for detecting the relationships between
+comments and the code itself. Comments at the end of lines are
+typically relevant to the line they are on, but this is not a
+requirement and could refer to other lines. Also, comments occupying
+their own lines usually refer to the following lines, but this is also
+not necessarily the case. As `clean` depends on the unambiguous
+determination of relationships in the production of results, it cannot
+operate automatically on comments. However, comments in the original
+code remain untouched and can be used to inform the reduced
+code. Also, as the `clean` function is oriented toward isolating code
+based on a specific result, the resulting code tends to naturally
+support the generation of new comments that are higher level
+(e.g. "The following produces a plot of the mean response of each
+treatment group."), and lower level comments are not necessary because
+the code is simpler and clearer. Lastly, as stated above, comments can
+serve an important role in coding, it is worth reflecting on the
+statement in R.C. Martin's book `Clean Code: A Handbook of Agile
+Software Craftsmanship` that "Comments do not compensate for bad
+code."
+
+In the future, it would also be useful to extend the existing
+framework to support other provenance methods. One possibility is
+*retrospective provenance*, which tracks a computational process as it
+is executing. Through this active, concurrent monitoring,
+retrospective provenance can gather information that static
+prospective provenance can't. Greater details of the computational
+process would enable other features that could address some
+challenges, such as processing information from comments, parsing
+control statements and replicating random processes. However, using
+retrospective provenance comes at a cost. In order to gather it, the
+script needs to be executed. When scripts are computationally
+intensive or contain bugs that stop execution, then retrospective
+provenance can not be obtained for part or all of the code. Some work
+has already been done in the direction of implementing retrospective
+provenance for code cleaning in R (see
+http://end-to-end-provenance.github.io).
+
+Although the current implementation of Rclean for minimizing code is
+useful on its own, we see promise in connecting it with other clean
+code and reproducibility tools. One example is the `reprex` package,
+which provides a simple API for sharing reproducible examples
+[@R-reprex]. Another possibility is to help transition scripts to
+function, package and workflow creation and refactoring via toolboxes
+like `drake` [@R-drake]. `Rclean` could provide a reliable way to
+extract parts of a larger script that would be piped to a simplified
+reproducible example, in the case of `reprex`, or, since it can
+isolate the code from inputs to one or more outputs, be used to
+extract all of the components needed to write one or more functions
+that would be a part of a package or workflow, as is the goal of
+`drake`.
 
 To conclude, we hope that `Rclean` makes writing scientific software
-easier for the R community. We look forward to feedback and help with
-extending its application, particularly in the area of
-reproducibility. To get involved, report bugs, suggest features,
-please visit the project page.
-
-# Acknowledgments
-
-This work was improved by discussions with ecologists at Harvard
-Forest and through the helpful review provided by the ROpenSci
-community, particularly Anna Krystalli, Will Landau and Clemens
-Schmid. Much of the work was funded by US National Science Foundation
-grant SSI-1450277 for applications of End-to-End Data Provenance.
+easier for the R community. As an open-source project, we look forward
+to feedback and help with extending it, particularly in the area of
+reproducibility. We invite people to use the package and get involved
+by reporting bugs and suggesting or contributing features. For more
+information please visit the project page on Github.
 

### 2020-03-12 ropensci/rclean_technote.Rmd
Edits technote and adds references

@@
-Rclean: Automated Tools for Cleaning R Code
-===========================================
+---
+title: Rclean and Automatng Code Cleaning in R
+author: M.K. Lau
+bibliography: refs.bib
+---
 
 > Leave the code cleaner than you found it.
+
 -- R.C. Martin in *Clean Code*
@@
 
-As you can see, the provenance provides a network representation of
-relationships among functions and objects. This is very powerful
-because we can now apply algorithms analyze the R script with respect
-to our results. The main function of `Rclean`, called `clean`, takes
-the provenance and applies a depth first network search algorithm to
-determine the pathways leading from inputs to outputs, excluding any
-objects or lines of code that do not fall along that pathway and are,
-therefore, not necessary to produce the desired set of results. As
-demonstrated in the next section, through this process, we can produce
-a new script with the minimal code necessary to generate the output we
-want.
+The provenance provides a network representation of relationships
+among functions and objects. This is very powerful because we can now
+apply algorithms analyze the R script with respect to our results. The
+main function of `Rclean`, called `clean`, takes the provenance and
+applies a depth first network search algorithm to determine the
+pathways leading from inputs to outputs, excluding any objects or
+lines of code that do not fall along that pathway and are, therefore,
+not necessary to produce the desired set of results. As demonstrated
+in the next section, through this process, we can produce a new script
+with the minimal code necessary to generate the output we want.
 
@@
 
-The following is an example of a script that has some "complications."
-As you can see, although the script is not extremely long or
-complicated, it's difficult enough to make it frustrating to visualize
-it in its entirety and pick through it.
+Analytical scripts that have not been refactored are often both long
+and complicated. However, a script doesn't need to be long to be
+complicated. The following example script presents some challenges
+such that even though it's not a long script, picking through it to
+get a result would likely prove to be frustrating.
 
-```{R long-setup, echo = FALSE, eval = TRUE, results = "hide"}
+```{R long-setup, echo = FALSE, eval = TRUE}
 
@@
 
-```{R long-script, echo = FALSE, eval = FALSE}
+```{R long-script, echo = TRUE, eval = FALSE}
 
@@
 produce one of the results `fit_sqrt_A`, which is an analysis that is
-relevant to some product. Not only do we want to double check the
-results, we also want to use the code again for another purpose, such
-as creating a plot of the patterns supported by the test. Manually
-tracing through our code for all the variables used in the test and
-finding all of the lines that were used to prepare them for the
-analysis would be annoying and difficult, especially given the fact
-that we have used "x" as a prefix for multiple unrelated objects in
-the script. Instead, we can easily do this automatically with
-`Rclean`.
+the fitted model object for an analysis. We might want to double check
+the results, and we also might need to use the code again for another
+purpose, such as creating a plot of the patterns supported by the
+test. Manually tracing through our code for all the variables used in
+the test and finding all of the lines that were used to prepare them
+for the analysis would be annoying and difficult, especially given the
+fact that we have used "x" as a prefix for multiple unrelated objects
+in the script. However, `Rclean` can do this easily via the `clean`.
 
@@
 
-Currently, because of the data provenance that is used, libraries can
-not be isolated directly during the cleaning process. So, the
-`get_libs` function provides a way to detect the libraries for a given
-script. Just supply a file path and `get_libs` will return the
-libraries that are called by that script.
+Currently, libraries can not be isolated directly during the cleaning
+process. So, the `get_libs` function provides a way to detect the
+libraries for a given script. We just need to supply a file path and
+`get_libs` will return the libraries that are called by that script.
 
@@
 
-## Software Availability
+## Software Availability and Installation
 
-The software is currently hosted on Github, and we recommend using the
-`devtools` library [@R-devtools] to install directly from the
-repository (https://github.com/ROpenSci/Rclean). The package is
-open-source and welcomes contributions. Please visit the repository
-page to report issues, request features or provide other feedback.
+Thanks to the efforts and helpful feedback from the ROpenSci
+Community, the package has recently passed software review and we have
+also recently published an article in the Journal of Statistical
+Software. The package is hosted through the ROpenSci organization on
+Github, and we recommend using the `devtools` library [@R-devtools] to
+install directly from the repository (https://github.com/ROpenSci/Rclean).
+
+```{R install}
+library(devtools)
+install_github("ROpenSci/Rclean")
+
+```
 
@@
 process would enable other features that could address some
-challenges, such as processing information from comments, parsing
-control statements and replicating random processes. However, using
-retrospective provenance comes at a cost. In order to gather it, the
-script needs to be executed. When scripts are computationally
-intensive or contain bugs that stop execution, then retrospective
-provenance can not be obtained for part or all of the code. Some work
-has already been done in the direction of implementing retrospective
-provenance for code cleaning in R (see
-http://end-to-end-provenance.github.io).
+challenges, such as libraries that are actually used by the code,
+processing comments, parsing control statements and replicating random
+processes. Using retrospective provenance comes at a cost. In order to
+gather it, the script needs to be executed. When scripts are
+computationally intensive or contain bugs that stop execution, then
+retrospective provenance can not be obtained for part or all of the
+code. Some work has already been done in the direction of implementing
+retrospective provenance for code cleaning in R (see
+http://end-to-end-provenance.github.io). Although such costs may
+present challenges, combining prospective and retrospective provenance
+methods could provide a powerful and flexible solution.
 

### 2020-03-12 ropensci/rclean_technote.Rmd
Edits technote adds install info

@@
 ---
-title: Rclean and Automatng Code Cleaning in R
+title: Automatic Code Cleaning in R with `Rclean`
 author: M.K. Lau
@@
 with the minimal code necessary to generate the output we want.
+
+# Installation
+
+Through the helpful feedback from the ROpenSci community, the package
+has recently passed software review and a supporting article was
+recently published in the Journal of Open Source Software [@Lau2020],
+in which you can find more details about the package. The package is
+hosted through the ROpenSci organization on Github, and the package
+can be installed using the `devtools` library [@R-devtools] directly
+from the repository (https://github.com/ROpenSci/Rclean).
+
+```{R install}
+library(devtools)
+install_github("ROpenSci/Rclean")
+
+```
 
@@
 
-## Software Availability and Installation
-
-Thanks to the efforts and helpful feedback from the ROpenSci
-Community, the package has recently passed software review and we have
-also recently published an article in the Journal of Statistical
-Software. The package is hosted through the ROpenSci organization on
-Github, and we recommend using the `devtools` library [@R-devtools] to
-install directly from the repository (https://github.com/ROpenSci/Rclean).
-
-```{R install}
-library(devtools)
-install_github("ROpenSci/Rclean")
-
-```
-
 # Concluding Remarks and Future Work

### 2020-03-12 ropensci/rclean_technote.Rmd
Fixes fig refs

@@
 be useful to visual the code in order to devise an approach to
-cleaning. As seen above \@ref(fig:prov-graph), `code_graph` will
+cleaning. As seen above \ref{fig:prov-graph}, `code_graph` will
 produce a visual of the code and the objects that they produce.

### 2020-03-12 ropensci/rclean_technote.Rmd
Increases figure resolution

@@
 
-Data analysis can be messy and complicated, so it's no wonder that the
-code often reflects this. "What did I measure? What analyses are
-relevant to them? Do I need to transform the data? What's the function
-for the analysis I want to run?" In addition, although many
-researchers see the value in learning to write software, the entry
-level is still exceedingly high. The `R` language has become very
-popular among scientists and analysts because of the lower threshold,
-which is good in that it empowers science. The downside is that
-learning to create good software is a skill that takes a considerable
-amount of time to learn, which means that many scientists write code
-that will get the job "done" but lacks transparency and is highly
-unstable (i.e. buggy).
+Data analysis can be messy and complicated. Because of project
+complexities and time contraints, analytial software often reflects
+these challenges. "What did I measure? What analyses are relevant to
+them? Do I need to transform the data? What's the function for the
+analysis I want to run?" In addition, although many researchers see
+the value in learning to write software, the entry level is still
+exceedingly high. The `R` language has become very popular among
+scientists and analysts because of the lower threshold, which is good
+in that it empowers science. The downside is that learning to create
+good software is a skill that takes a considerable amount of time to
+learn, which means that many scientists write code that will get the
+job "done" but lacks transparency and is highly unstable (i.e. buggy).
 
@@
 
-```{R ex-code_graph, fig.cap = "Example of the plot produced by the code_graph function showing which lines of code produce which variables and which variables are used by other lines of code."}
+```{R ex-code_graph, dpi = 300, fig.cap = "Example of the plot produced by the code_graph function showing which lines of code produce which variables and which variables are used by other lines of code."}
 

### 2020-03-13 ropensci/rclean_technote.Rmd
Typo fix
Edits throughout for final version

@@
 
+# Introduction
+
 > Leave the code cleaner than you found it.
@@
 
-Data analysis can be messy and complicated. Because of project
-complexities and time contraints, analytial software often reflects
+The `R` language has become very popular among scientists and analysts
+because it enables the rapid development of software and empowers
+scientific investigation. However, regardless of the language used,
+data analysis is usually complicated. Because of various project
+complexities and time contraints, analytical software often reflects
 these challenges. "What did I measure? What analyses are relevant to
 them? Do I need to transform the data? What's the function for the
-analysis I want to run?" In addition, although many researchers see
-the value in learning to write software, the entry level is still
-exceedingly high. The `R` language has become very popular among
-scientists and analysts because of the lower threshold, which is good
-in that it empowers science. The downside is that learning to create
-good software is a skill that takes a considerable amount of time to
-learn, which means that many scientists write code that will get the
-job "done" but lacks transparency and is highly unstable (i.e. buggy).
+analysis I want to run?" Although many researchers see the value in
+learning to write software, the time investment for learning a
+programming language alone is still exceedingly high for many, let
+alone also learning software best practices. The downside to the rapid
+spread of data science is that learning to create good software takes
+a back-seat to just writing code that will get the job "done" leading
+to issues with transparency and software that is highly unstable
+(i.e. buggy and not reproducible).
 
-The goal of `Rclean` is to provide a tool that help someone reduce and
-organize code based on results.  More often then not, when someone is
-writing an R script, the intent is to produce a set of results, such
-as a statistical analysis, figure or table. This set of results is
-nearly always a subset of a much larger set of possible ways to
-explore a dataset, as there are many statistical approaches and tests,
-let alone ways to create visualizations and other representations of
-patterns in data. This commonly leads to lengthy, complicated scripts
-from which researchers manually subset results, but likely never to be
-refactored because of the difficulty in disentangling the code needed
-to produce some results and not others.
+The goal of `Rclean` is to provide a automated tool to help scientists
+more easily write better code. Specifically, `Rclean` has been
+designed to faciliate the isolation of the code needed to produce one
+or more results, because more often then not, when someone is writing
+an R script, the ultimate goal is analytical results for inference,
+such as a set of statistical analyses and associated figures and
+tables. As the investigative process is inherently iterative, this set
+of results is nearly always a subset of a much larger set of possible
+ways to explore a dataset. There are many statistical tests and
+visualizations and other representations that can be employed in a
+myriad of ways depending on how the data are processed. This commonly
+leads to lengthy, complicated scripts from which researchers manually
+subset results, but likely never to be refactored because of the
+difficulty in disentangling the code.
 
-The `Rclean` package uses an automated technique based on data
-provenance and network algorithms to analyze existing scripts and
-provide ways to identify and extract code to produce a desired output
-without having to manually conduct the search through the code line by
-line. `Rclean` was designed to ease refactoring for scientists that
-use R but do not have formal training in software engineering and
-specifically with the "art" of creating clean code; however, because
-manually culling code is tedious and potentially leads to errors,
-`Rclean` can be a useful tool for everyone at all levels of coding
-ability.
+The `Rclean` package uses a technique based on data provenance and
+network algorithms to isolate code for a desired result
+*automatically*. The intent is to ease refactoring for scientists that
+use R but do not have formal training in software design and
+specifically with the "art" of creating clean code, which in part is
+the development of an intuitive sense of how code is and/or should be
+organized. However, manually culling code is tedious and potentially
+leads to errors, and we see `Rclean` as a useful tool for everyone at
+all levels of coding ability in `R`. Here, we'll cover details on the
+implementation and design of the package, a general example of how it
+can be used and thoughts on its future development.
 
-# The Provenance Engine Under the Hood
+# How to Use `Rclean` to Write Cleaner Code
 
-The process that `Rclean` uses relies on the generation of data
-provenance.  The term provenance means information about the origins
-of some object. Data provenance is a formal representation of the
-execution of a computational process (https://www.w3.org/TR/prov-dm/),
-to rigorously determine the the unique computational pathway from
-inputs to results [@Carata2014]. To avoid confusion, note that "data"
-in this context is used in a broad sense to include all of the
-information generated during computation, not just the data that are
-collected in a research project that are used as input to an
-analysis. Having the formalized, mathematically rigorous
-representation that data provenance provides guarantees that the
-analyses that `Rclean` conducts are theoretically sound. Most
-importantly, because the relationships defined by the provenance can
-be represented as a graph, it is possible to apply network search
-algorithms to determine the minimum and sufficient code needed to
-generate the chosen result in the `clean` function.
-
-There are multiple approaches to collecting data provenance, but
-`Rclean` uses "prospective" provenance, which analyzes code and uses
-language specific information to predict the relationship among
-processes and data objects. `Rclean` relies on a library called
-`CodeDepends` to gather the prospective provenance for each
-script. For more information on the mechanics of the `CodeDepends`
-package, see [@R-CodeDepends]. To get an idea of what data provenance
-is, take a look at the `code_graph` function. The plot that it
-generates is a graphical representation of the prospective provenance
-generated for `Rclean` \ref{fig:prov-graph}.
-
-```{R load-script, echo = FALSE, results = "hide"}
-library(CodeDepends)
-library(Rclean)
-```
-
-```{R prov-graph, dpi = 300, fig.cap = "Network diagram of the prospective data provenance generated for an example script.
-Arrows indicate which lines of code (numbered) produced which objects (named).", echo = FALSE}
-
-script <- system.file(
-    "example", 
-    "simple_script.R", 
-    package = "Rclean")
-code_graph(script)
-
-```
-
-The provenance provides a network representation of relationships
-among functions and objects. This is very powerful because we can now
-apply algorithms analyze the R script with respect to our results. The
-main function of `Rclean`, called `clean`, takes the provenance and
-applies a depth first network search algorithm to determine the
-pathways leading from inputs to outputs, excluding any objects or
-lines of code that do not fall along that pathway and are, therefore,
-not necessary to produce the desired set of results. As demonstrated
-in the next section, through this process, we can produce a new script
-with the minimal code necessary to generate the output we want.
-
-# Installation
+## Installation
 
@@
 
-# Using `Rclean` to clean your code
+## Isolating Code for a Set of Results
 
@@
 fact that we have used "x" as a prefix for multiple unrelated objects
-in the script. However, `Rclean` can do this easily via the `clean`.
+in the script. However, `Rclean` can do this easily via the `clean`
+function.
 
@@
 be useful to visual the code in order to devise an approach to
-cleaning. As seen above \ref{fig:prov-graph}, `code_graph` will
-produce a visual of the code and the objects that they produce.
+cleaning. The `code_graph` function can also give us a visual of the
+code and the objects that they produce.
 
@@
 
-# Concluding Remarks and Future Work
-
-We have created ``Rclean`` to provide a simple, easy to use tool for
-scientists who would like help refactoring code. Using ``Rclean`` the
-code necessary to produce a specified result (e.g., an object stored
-in memory or a table or figure written to disk) can be easily and
-*reliably* isolated even when tangled with code for other
-results. Tools, such as this, that make it easier to produce
-transparent, accessible code will be an important aid for improving
-scientific reproducibility.
+# The Provenance Engine Under the Hood
 
@@
 
-Relatedly, it is important to point out that `Rclean` *does not* keep
-comments present in code. This is a limitation of the data provenance,
-which currently does not assign them a relationships. Therefore,
-although there is often very useful or even invaluable information in
-comments, the `clean` function removes them. This is a general issue
-with automated methods for detecting the relationships between
-comments and the code itself. Comments at the end of lines are
-typically relevant to the line they are on, but this is not a
-requirement and could refer to other lines. Also, comments occupying
-their own lines usually refer to the following lines, but this is also
-not necessarily the case. As `clean` depends on the unambiguous
-determination of relationships in the production of results, it cannot
-operate automatically on comments. However, comments in the original
-code remain untouched and can be used to inform the reduced
+The process that `Rclean` uses relies on the generation of data
+provenance.  The term provenance means information about the origins
+of some object. Data provenance is a formal representation of the
+execution of a computational process (https://www.w3.org/TR/prov-dm/),
+to rigorously determine the the unique computational pathway from
+inputs to results [@Carata2014]. To avoid confusion, note that "data"
+in this context is used in a broad sense to include all of the
+information generated during computation, not just the data that are
+collected in a research project that are used as input to an
+analysis. Having the formalized, mathematically rigorous
+representation that data provenance provides guarantees that the
+analyses that `Rclean` conducts are theoretically sound. Most
+importantly, because the relationships defined by the provenance can
+be represented as a graph, it is possible to apply network search
+algorithms to determine the minimum and sufficient code needed to
+generate the chosen result in the `clean` function.
+
+There are multiple approaches to collecting data provenance, but
+`Rclean` uses "prospective" provenance, which analyzes code and uses
+language specific information to predict the relationship among
+processes and data objects. `Rclean` relies on a library called
+`CodeDepends` to gather the prospective provenance for each
+script. For more information on the mechanics of the `CodeDepends`
+package, see [@R-CodeDepends]. To get an idea of what data provenance
+is, we can use `code_graph` function to get a graphical representation
+of the prospective provenance generated for `Rclean`
+\ref{fig:prov-graph}.
+
+```{R load-script, echo = FALSE, results = "hide"}
+library(CodeDepends)
+library(Rclean)
+```
+
+```{R prov-graph, dpi = 300, fig.cap = "Network diagram of the prospective data provenance generated for an example script.
+Arrows indicate which lines of code (numbered) produced which objects (named).", echo = FALSE}
+
+script <- system.file(
+    "example", 
+    "simple_script.R", 
+    package = "Rclean")
+code_graph(script)
+
+```
+
+All of this work with the provenance is to get the network
+representation of relationships among functions and objects. The
+provenance network is very powerful because we can now apply
+algorithms analyze the R script with respect to our results. This is
+what empowers the `clean` function, which takes the provenance and
+applies a a network search algorithm to determine the pathways leading
+from inputs to outputs. In the process any objects or lines of code
+that do not fall along that pathway are by definition not necessary to
+produce the desired set of results and can therefore be removed. As
+demonstrated in the example, this property of the provenance network
+is what facilitates the robust isolation of the minimal code necessary
+to generate the output we want.
+
+One important topic to discuss is that `Rclean` *does not* keep
+comments present in code. This is the result of a limitation of the
+data provenance collection, which currently does not assign them a
+relationship in the provenance network. This is a general issue with
+detecting the relationships between comments and code. For example,
+comments at the end of lines are typically relevant to the line they
+are on, but this is not a requirement and could refer to other
+lines. Also, comments occupying their own lines usually refer to the
+following lines, but this is also not necessarily the case either, as
+there is no "linguistic" requirement for this. Although `Rclean`
+cannot operate automatically on comments; however, comments in the
+original code remain untouched and can be used to inform the reduced
 code. Also, as the `clean` function is oriented toward isolating code
@@
 treatment group."), and lower level comments are not necessary because
-the code is simpler and clearer. Lastly, as stated above, comments can
+the code is simpler and clearer. This process of comments is an
+important part of writing better code. Lastly, although comments can
 serve an important role in coding, it is worth reflecting on the
 statement in R.C. Martin's book `Clean Code: A Handbook of Agile
-Software Craftsmanship` that "Comments do not compensate for bad
-code."
+Software Craftsmanship` where he writes that, "Comments do not
+compensate for bad code."
 
-In the future, it would also be useful to extend the existing
-framework to support other provenance methods. One possibility is
-*retrospective provenance*, which tracks a computational process as it
-is executing. Through this active, concurrent monitoring,
-retrospective provenance can gather information that static
-prospective provenance can't. Greater details of the computational
-process would enable other features that could address some
-challenges, such as libraries that are actually used by the code,
-processing comments, parsing control statements and replicating random
-processes. Using retrospective provenance comes at a cost. In order to
-gather it, the script needs to be executed. When scripts are
-computationally intensive or contain bugs that stop execution, then
-retrospective provenance can not be obtained for part or all of the
-code. Some work has already been done in the direction of implementing
-retrospective provenance for code cleaning in R (see
-http://end-to-end-provenance.github.io). Although such costs may
-present challenges, combining prospective and retrospective provenance
-methods could provide a powerful and flexible solution.
+# Concluding Remarks and Future Work
+
+``Rclean`` provides a simple, easy to use tool for scientists who
+would like help refactoring code. Using ``Rclean``, the code necessary
+to produce a specified result (e.g., an object stored in memory or a
+table or figure written to disk) can be easily and *reliably* isolated
+even when tangled with code for other results. Tools, such as this,
+that make it easier to produce transparent, accessible code will be an
+important aid for improving scientific reproducibility
+[@Pasquier2017].
 
 Although the current implementation of Rclean for minimizing code is
-useful on its own, we see promise in connecting it with other clean
-code and reproducibility tools. One example is the `reprex` package,
-which provides a simple API for sharing reproducible examples
+useful on its own, we see promise in connecting it with other
+reproducibility tools. One example is the `reprex` package, which
+provides a simple API for sharing reproducible examples
 [@R-reprex]. Another possibility is to help transition scripts to
@@
 
-To conclude, we hope that `Rclean` makes writing scientific software
-easier for the R community. As an open-source project, we look forward
-to feedback and help with extending it, particularly in the area of
-reproducibility. We invite people to use the package and get involved
-by reporting bugs and suggesting or contributing features. For more
-information please visit the project page on Github.
+In the future, it would also be useful to extend the existing
+framework to support other provenance methods. One possibility is
+*retrospective provenance*, which tracks a computational process as it
+is executing. Through this active, concurrent monitoring,
+retrospective provenance can gather information that static
+prospective provenance can't. Greater details of the computational
+process would enable other features that could address some
+challenges, such as libraries that are actually used by the code,
+processing comments (as discussed above), parsing control statements
+and replicating random processes. Using retrospective provenance comes
+at a cost, however. In order to gather it, the script needs to be
+executed. When scripts are computationally intensive or contain bugs
+that stop execution, then retrospective provenance can not be obtained
+for part or all of the code. Some work has already been done in the
+direction of implementing retrospective provenance for code cleaning
+in R (see http://end-to-end-provenance.github.io). Although such costs
+may present challenges, combining prospective and retrospective
+provenance methods could provide a powerful and flexible solution.
+
+We hope that `Rclean` makes writing scientific software easier for the
+R community. We look forward to the future progress of the package and
+other "code cleaning" tools. As an open-source project, we are very
+receptive to feedback and help with extending it. We invite people to
+use the package and get involved by reporting bugs and suggesting or
+(hopefully) contributing features. For more information please visit
+the project page on Github.
 

### 2020-03-13 ropensci/rclean_technote.Rmd
Spellcheck

@@
 data analysis is usually complicated. Because of various project
-complexities and time contraints, analytical software often reflects
+complexities and time constraints, analytical software often reflects
 these challenges. "What did I measure? What analyses are relevant to
@@
 more easily write better code. Specifically, `Rclean` has been
-designed to faciliate the isolation of the code needed to produce one
+designed to facilitate the isolation of the code needed to produce one
 or more results, because more often then not, when someone is writing
